
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP4 Meeting Minutes\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP4 Weekly Scrum: Validation and Verification\\
Date \& time & 2013-11-08, 10:30h--10:45h\\
Location & Telco and Goto-Meeting\\
Called up by & Marc Behrens\\
Participants &
Benjamin Beichler,
%Marc Behrens,
%Cecile Braunstein,
%Cyril Cornu,
%Sylvain Baro,
%Fausto Cochetti,
%Peyman Farhangi,
%Laurent Ferrier,
%Jens Gerlach,
%Frank Golatowski,
%Ainhoa Gracia,
%Baseliyos Jacob,
%Michael Jastram,
%Klaus-R\"udiger Hase,
Bernd Hekele,
%Jonas Helming,
%Hardi Hungar,
Roberto Kretschmer,
%Renaud de Landtsheer,
%Peter Mahlmann,
Alexander Nitsch,
Marielle Petit-Doche,
%Stan Pinte,
Merlin Pokam,
%Christophe Ponsard,
%Stefan Rieger,
%Uwe Steinke,
%Pierre Francois Jauquet,
%Jo\~ao Santos,
%Izaskun de la Torre
Jan Welte
%Jan Welvaarts
%Silvano dal Zilio
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item Backlog 1st Level V\&V
\item D4.2.1 V\&V Report
\item First Workshop on Safety Assessment
\end{itemize}

\section{Discussion}

\begin{itemize}
\item Backlog 1st Level V\&V\\
12th sprint completed. (Last sprint in planning.) Since there is still some work on the items in progress the items will be managed in sprint the 12 backlog. 

Before starting with 2nd level V\&V the we plan to invite to a Level 1 retrospective meeting.

The Backlog is visible in the validation repository:
\url{https://github.com/openETCS/validation/issues?milestone=11&page=1&state=open}\\

\item D4.2.1 V\&V Report\\
D4.2.1 document structure is available. The results of V\&V 1 level shall be incorporated in this document. The progress of this document is on the agenda for the upcoming WP4 meetings.

\item First Workshop on Safety Assessment\\
The workshop is planned (but not yet confirmed) to take place at AEbt in N\"urnberg. Agenda is currently in preparation. url{https://github.com/openETCS/validation/wiki/First-Workshop-on-Safety-Assessment}

\end{itemize}


\section{Notes}

\end{document}




