
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}



% Page layout (geometry)
\title{Meeting Minute openETCS WP4: V&\V}
\author{Hekele, Bernd}
\date{2013-04-19}

\begin{document}
\section*{\large{Meeting Minute openETCS WP4: Verification \& Validation 2013-04-19}}

\emph{Called up by: \ Marc Behrens}\\
\emph{Minutes by: \ \  Bernd Hekele}


\subsection*{Participants:} WP4, 
% Sylvain Baro,
Benjamin Beichler,
Marc Behrens, 
Cyril Cornu, 
%Michael Ditze,
Jens Gerlach, 
Frank Golatowski, 
Klaus-Ruediger Hase, 
Bernd Hekele,
%Jonas Helming,
Baseliyos Jacob,
%Michael Jastram, 
%Rico Kaseroni, 
Roberto Kretschmer,
%Peter Mahlmann, 
Marielle Petit-Doche, 
%Stan Pinte, 
%Merlin Pokam, 
%Stefan Rieger,
%Uwe Steinke,
%Joao Santos, 
Jan Welte\\

\subsection*{Meeting Time: from 10:00h \ to: \ 10:30h}

\subsection*{Type of conference: Telco}

\line(1,0){440}
\section*{\underline{Agenda}}
\begin{enumerate}
\item First draft of the "Tool-Artifacts-Matrix"
\begin{itemize}
\item Concept and usage of the matrix
\item Questions concerning the matrix
\item The Matrix is planned to be filled out and reviewed in parallel until the 26th April.
\end{itemize}
\item At the 24th of April the SSRS Kick-off in Paris takes place
\item What to do with the first findings of the verification? 
\begin{itemize}
\item How to verify the issues have not yet been discussed at ERTMS Users group level?
\item Who should report the issues?
\item How should the issues been reported?
\end{itemize}
\item Pre- qualification of the V\&V model 
\begin{itemize}
\item Which model to take from the model evaluation for the V\&V process qualification?
\item Preparing the first V\&V phase coming up
\item Open discussion on the V\&V concept
\end{itemize}
\end{enumerate}
\line(1,0){440}
\section*{\underline{Discussion}}
\begin{enumerate}
\item First draft of the "Tool-Artifacts-Matrix"
has been distributed via E-Mail today. For further review and update Github is planned to be used. The WP4 infomation and artifakts matrix is available here:\\
\url{https://github.com/openETCS/validation/tree/master/Artifacts}.\\
You will find more useful information about the process in the following Wiki:\\
\url{https://github.com/openETCS/model-evaluation/wiki/Open-Question-for-Modeling-Benchmark}

\item At the 24th of April the SSRS Kick-off in Paris takes place:
\item A short walk through the agenda will be presented.
For improving the performance of the upcoming activities the use of an own repository is highly recommended. The issue will be discussed on PMB.\\
The repository is available here:
\url{https://github.com/openETCS/SSRS.git}

The following candidates for SSRS architecturew have been discussed:\\
Graphical Architecture Modelling Tools
\begin{itemize}
\item EA (Entgerprise Architect) - commercial
\item Artisan Studio    - commercial
\item Visio      - commercial
\item Scade      - commercial
\item Papyrus/Eclipse (Topcased) - opensource
\item Rodin-Editor (B-Event)  - opensource
\item CPN-Tools     - GPL (opensource forseen)
\end{itemize}

Key features for qualification are:
\begin{itemize}
\item  needs multi-user capability
\item  needs version control
\end{itemize}

The upcoming activity is taking effort. A first rough preliminary estimation is:
 
\begin{itemize}
\item estimate 15 requirements per person day
\item ca. 6000 requirements in subset-026
\item ==> 400 person days effort
\end{itemize}

\item What to do with the first findings of the verification? Following questions should be addressed:
In principle, the DB representative in the ERTMS user group will act as an interface. Within openETCS, DB will set up a fra meworkto easily collect findings. Options discussed were own e-mail account for findings or Issue's linked with the new repository SSRS. Baseliyos (DB) will prepare the process and distribute/set-up the relevant information.

\end{enumerate}

\line(1,0){440}
\section*{\underline{Notes}}

\end{document}
