
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP4 Meeting Minutes\end{center}}
%{\begin{center}\huge\bf Project Management Board (PMB)\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP4 Weekly Scrum: Validation and Verification\\
Date \& time & 2013-04-26, 10:00h--10:30h\\
Location & Telco and Goto-Meeting\\
Called up by & Marc Behrens\\
Participants & WP4,
Benjamin Beichler,
Marc Behrens,
Cecile Braunstein,
%Stephane Callet,
Cyril Cornu, 
%Gilles Dalmas,
Jens Gerlach, 
Frank Golatowski, 
Klaus-R\"udiger Hase,
Bernd Hekele,
%Jonas Helming,
Baseliyos Jacob,
Michael Jastram, 
%Bego\~na Laibarra,
Peter Mahlmann, 
Jaime Paniagua,
%Marielle Petit-Doche, 
%Stan Pinte,
Stefan Rieger,
Uwe Steinke,
Jo\~ao Santos,
Jan Welte\\
%Giovanni Zanelli\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item V\&V and Safety relevant results as outcome from the 24th of April the SSRS Kick-off in Paris
\item Result of the tools workshops in Munich
\end{itemize}

\section{Discussion}
\begin{itemize}
\item V\&V and Safety relevant results as outcome from the 24th of April the SSRS Kick-off in Paris:
SSRS experts group and SRSS Review Team\\

The minutes to the SRSS Kick-Off meeting are in preparation (Baseliyos). They will be provided on Github for review (29.04.13). 

As an outcome of the workshop the competences are planned to be concentrated in 2 teams:
\begin{itemize}
\item The SRSS Expert Team with the competences from railway suppliers and research 
\item The SRSS review team with the competence of railway operators.
\end {itemize}
Experts for the teams still have to be nominated. It is foreseen to have the expert team working on a single site, e.g., in Munich at DB. Kickoff for the Review Team Kickoff is scheduled for May 15th.

For planning of the expert team, the following doodle is activated:\\
\url{http://doodle.com/k4emwuvart6uukbv}

\item Result of the tools workshops in Munich
Which Methodology and Tool can be taken for Verification?\\
The trialing of tools based on the presentation of the tools workshop is ongoing. 
Further interesting candidate:\\
Papyrus: \url{www.eclipse.org/papyrus}\\

A Papyrus training is in preparation.

Which are the important criteria for first preliminary process qualification?\\
This is part of the upcoming activities in WP4.
\end{itemize}

%\end{itemize}

\line(1,0){440}
\section{\underline{Notes}}

\end{document}
