
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP4 Meeting Minutes\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP4 Weekly Scrum: Validation and Verification\\
Date \& time & 2014-02-21, 09:30h--09:45h\\
Location & Telco and Goto-Meeting\\
Called up by & Marc Behrens\\
Participants &
Benjamin Beichler,
Marc Behrens,
%Cecile Braunstein,
%Sylvain Baro,
%Peyman Farhangi,
%Jens Gerlach,
%Frank Golatowski,
%Ainhoa Gracia,
%Klaus-R\"udiger Hase,
Bernd Hekele,
%Jonas Helming,
%Hardi Hungar,
%Baseliyos Jacob,
Michael Jastram,
%Roberto Kretschmer,
Peter Mahlmann,
Alexander Nitsch,
%Vincent Nuhaan,
Marielle Petit-Doche,
%Stan Pinte,
%Merlin Pokam,
%Christophe Ponsard,
Stefan Rieger,
Uwe Steinke,
%Pierre Francois Jauquet,
%Jo\~ao Santos,
Izaskun de la Torre
Jan Welte
%Jan Welvaarts,
%Silvano dal Zilio,
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item V\&V D4.2 Report (1st Level)
\item V\&V Internal Assessment workshop in N\"urnberg.

\end{itemize}

\section{Discussion}

\begin{itemize}
\item V\&V D4.2 Report (1st Level)\\
Thr project plkans for a revision phase to start for the next 2 weeks. 
 
\item V\&V Internal Assessment workshop in N\"urnberg.\\
The internal assessment workshop has been during this week. 
The reviewers (All4Tec and AEbt) concentrated on the process docuements and the quality assurance plan. During the meeting several issues were highlighted which needs completion before continuation of the internal assessment can be  performed.

To continue the work on the QA-Plan the QA backlog will be updated with findings from the meeting. A close follow-up of items in the backlog is planned to be part of the weekly QA session. (Thursday's 13:00 - 14:00) Active contribution by partners of WP1, WP2, WP3 and WP4 is needed to complete the task.

The next step of the internal assessment is planned to take place at June 10th (as a part of the Munich meeting).

A go/nogo decision  is scheduled for May 9th (PMB).

The meeting minutes and slides will be made available  in the V\&V project.

\end{itemize}


\section{Notes}

\end{document}
