
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP1 Meeting Minutes: Management\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP1 Weekly Scrum: Management\\
Date \& time & 2013-05-03, 14:30h--15:00h\\
Location & Telco and Goto-Meeting\\
Called up by & Klaus-R\"udiger Hase\\
Participants & WP1,
%Benjamin Beichler,
%Marc Behrens,
%Cecile Braunstein,
%Stephane Callet,
Cyril Cornu, 
%Gilles Dalmas,
%Jens Gerlach, 
%Frank Golatowski, 
Klaus-R\"udiger Hase,
Bernd Hekele,
%Jonas Helming,
Baseliyos Jacob,
Michael Jastram, 
Bego\~na Laibarra,
%Peter Mahlmann, 
%Jaime Paniagua,
%Marielle Petit-Doche, 
%Stan Pinte,
%Stefan Rieger,
%Uwe Steinke,
%Jo\~ao Santos,
%Jan Welte,
Giovanni Zanelli\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item Review Process
\item QA-Plan
\end{itemize}

\section{Discussion}
\begin{itemize}
\item Review Process\\SQS has provided a new review process. This review process is currently in the state of a prototype. It is in use for the review of the document as such and for quality related documents. After confirmation, we plan to take this process in use. Till then the current agreements - especially the review process in use with requirement documents - can be used for ongoing activities.
The new process resp. quality document has to respect the review results which have been achieved beforehand.
It is foreseen to have a (live or goto-) meeting in order to finalize the review.

\item QA-Plan
An updated version of the QA plan (still some sort of sceleton) is announced for Wednesday, May 8th.
Based on this document a meeting is planned to assign open tasks to experts.
\end{itemize}

\line(1,0){440}
\section{\underline{Notes}}

\end{document}
