\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP6 Meeting Minutes\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP6 Weekly Scrum: Dissemination\\
Date \& time & 2013-12-13, 10:15h--10:30h\\
Location & Telco and Goto-Meeting\\
Called up by & Stefan Rieger\\
Participants &
Arnaud,
%Sylvain Baro,
%Benjamin Beichler,
%Marc Behrens,
%Cecile Braunstein,
%Fausto Cochetti,
%Cyril Cornu,
Klaus R\"udiger Hase,
%Frank Golatowski,
%Hardi Hungar,
%Baseliyos Jacob
Michael Jastram,
Peter Mahlmann,
Alexander Nitsch,
Marielle Petit-Doche,
%Merlin Pokam,
%Christophe Ponsard,
Stefan Rieger,
Uwe Steinke,
%Izaskun de la Torre,
%Silvano dal Zilio,
Jan Welte
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{Agenda}
\begin{itemize}

\item Exploitation Plan
\item Standardisation Commitee
\item AAET Conference 2014
\item Mid-Term Workshop

\end{itemize}

\section{Discussion}

\begin{itemize}

\item Exploitation Plan\\
The initial exploitation plan is still under construction: \url{https://github.com/openETCS/dissemination-management/blob/master/D6.2_Initial_Exploitation_Plan_and_Standardization_Strategy/D6.2_Initial_Exploitation_Plan_and_Standardization_Strategy.pdf}\\

Contributions are still collected. Due date is end of December 2013. In the same document contributions of openETCS to standardization are collected. Please, update relevant sections.


\item AAET Conference 2014\\
We are driving a contribution to the AAET conference in 2014:
\url{https://github.com/openETCS/dissemination-management/blob/master/ProjectPublications/AAET_2014_Open_Proofs/AAET_2014_Open_Proof_Structure.docx}\\
Contributions are collected in this repository.

\item ITEA Summit\\
The openETCS midterm workshop is planned to take part in the middle of the year. We propose to align the workshop with the Innotrans. Details will be discussed in the WP6 January slot.
\end{itemize}

%\line(1,0){440}
\section{Notes}

\end{document}
