
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}

% Page layout (geometry)
\title{Meeting Minute openETCS WP6: Dissemination}
\author{Hekele, Bernd}
\date{2013-03-22}

\begin{document}%\setwidth {1.8}
\section*{\large{Meeting Minute openETCS WP6: Dissemination 2013-03-22}}

\emph{Called up by: \ Dr. Klaus Ruediger Hase.}\\
\emph{Minutes by: \ \  Stefan Rieger.}

\subsection*{Participants:} WP6, 
Stefan Rieger, 
Marc Behrens, 
Michael Ditze,
% Jens Gerlach, 
% Frank Golatowski, 
Baseliyos Jacob,
Klaus-Ruediger Hase, 
Bernd Hekele,
% Jonas Helmig,
% Michael Jastram, 
Peter Mahlmann, 
% Marielle Petit-Doche, 
Jan Welte\\

\subsection*{Meeting Time: from 09:00h \ to: \ 09:30h}

\subsection*{Type of conference: Telco}

\line(1,0){440}
\section*{\underline{Agenda}}
\begin{enumerate}
\item  D6.1 Dissemination Report (due at the end of the month) 
\item Special session at IEEE INDIN (deadline extension) 
\end{enumerate}
\line(1,0){440}
\section*{\underline{Discussion}}

\begin{enumerate}

\item Special session at IEEE INDIN (deadline extension) \\
Deadline for contribution extended. 

\item  D6.1 Dissemination Report (due at the end of the month)\\
Some contributions still pending. Stefan will send a mail contacting persons with outstanding topics.\\
Deadline for the template with new layout: April 2nd. Peter will deliver updated template.\\
Events/contributions mentioned in the dissemination plan need to have a clear alignment with the openETCS project. If association is not clear the part will be taken out of the plan.

\end{enumerate}

\line(1,0){440}
\section*{\underline{Notes}}

\end{document}
