
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}

% Page layout (geometry)
\title{Meeting Minute openETCS WP6: Dissemination}
\author{Hekele, Bernd}
\date{2013-03-20}

\begin{document}%\setwidth {1.8}
\section*{\large{Meeting Minute openETCS WP6: Dissemination 2013-03-15}}

\emph{Called up by: \ Dr. Klaus Ruediger Hase.}\\
\emph{Minutes by: \ \  Stefan Rieger.}

\subsection*{Participants:} WP6, 
Stefan Rieger, 
% Marc Behrens, 
% Jens Gerlach, 
% Frank Golatowski, 
% Klaus-Ruediger Hase, 
Bernd Hekele,
% Jonas Helmig,
% Michael Jastram, 
Peter Mahlmann, 
Marielle Petit-Doche, 
Jan Welte\\

%Baseliyos Jacob, Joao Santos, Uwe Steinke, Roberto, Kretschmer

\subsection*{Meeting Time: from 09:00h \ to: \ 09:30h}

\subsection*{Type of conference: Telco}

\line(1,0){440}
\section*{\underline{Agenda}}
\begin{enumerate}
\item Special Session at IEEE INDIN 2013
\item Collection of openETCS Terminology
\item D6.1 Dissemination Plan
\end{enumerate}
\line(1,0){440}
\section*{\underline{Discussion}}

\begin{enumerate}

\item Special Session at IEEE INDIN 2013\\
Today is the submission deadline but we are working towards another
deadline extension. You will be informed as soon as there are any news.

\item Collection of openETCS Terminology\\
DB and Jan Welte will setup a system/process for collecting openETCS
terminology. This will most likely be Github-based. More details will
follow.

\item D6.1 Dissemination Plan\\
We discussed the current state of the dissemination plan and decided to add
concrete responsibilities to the individual parts.\\
\\
TODO:\\
Please check the current version of the dissemination plan on Github\\

% https://github.com/openETCS/Dissemination/tree/master/D6.1_Dissemination_Plan_and_Report\\

with regard to missing contributions that are marked in red. For every
element, the responsibilities are given in the document. Please commit or
contribute via Github, or, if this is not possible for you, send me an
email with your contribution. Please provide your contributions until next
Thursday (21/3) for us to have a preliminary version to discuss on Friday,\\
Thank you in advance for your help!\\

\end{enumerate}

\line(1,0){440}
\section*{\underline{Notes}}

\end{document}
