
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP6 Meeting Minutes\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP7 Weekly Scrum: Dissemination\\
Date \& time & 2013-06-07, 10:00h--10:15h\\
Location & Telco and Goto-Meeting\\
Called up by & Stefan Rieger\\
Participants &
%Sylvain Baro,
%Benjamin Beichler,
Marc Behrens,
Cecile Braunstein,
Fausto Cochetti,
Frank Golatowski,
Hardi Hungar,
Peter Mahlmann,
%Marielle Petit-Doche,
Merlin Pokam,
Christophe Ponsard,
%Uwe Steinke,
Stefan Rieger,
Peter Mahlmann,
Klaus R\"udiger Hase,
Baseliyos Jacob,
Izaskun de la Torre,
Silvano dal Zilio,
Jan Welte
\\

Minutes by & Stefan Rieger\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{Agenda}
\begin{itemize}
\item ITEA Review Meeting
\item publications of references with the Zotero tool
\end{itemize}

\section{Discussion}

\begin{itemize}

\item in today's WP6 phone conference we discussed the preparation for the ITEA review meeting. We need your help with the following to-dos: 

* Please send me all of your publications that reference the openETCS project (as PDF files). They need to be provided to ITEA. 

* Please provide us some input regarding your exploitation plans (e.g., short text or simple slide). If we do not get input we are forced to fall back to the information from the FPP. 

\item The second topic was a brief introduction to the management of publications of references with the Zotero tool. I created a Wiki page that describes how to setup the software and your account: 

\url{https://github.com/openETCS/Dissemination/wiki/Management-of-Publications-and-References-with-Zotero }

It's really easy to use and we kindly ask you to contribute by providing your publications and references via Zotero. All partners will benefit from this database. 


\end{itemize}

%\line(1,0){440}
\section{Notes}

\end{document}
