
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP7 Meeting Minutes\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP7 Weekly Scrum: Toolchain\\
Date \& time & 2013-09-13, 11:00h--11:15h\\
Location & Telco and Goto-Meeting\\
Called up by & Michael Jastram\\
Participants &
Benjamin Beichler
Marc Behrens,
Cecile Braunstein,
Cyril Cornu,
%Peyman Farhangi,
Frank Golatowski,
%Klaus R\"udiger Hase,
Bernd Hekele,
%Jonas Helming,
%Hardi Hungar,
%Baseliyos Jacob,
Michael Jastram,
%Roberto Kretschmer,
%Peter Mahlmann,
%Alexander Nitsch,
Renaud de Landtsheer,
Marielle Petit-Doche,
Merlin Pokam,
%Christophe Ponsard,
%Alexander Stante,
Stefan Rieger,
Uwe Steinke,
%Izaskun de la Torre,
Jan Welte\\
%Silvano dal Zilio


Minutes by & Bend Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{Agenda}
\begin{itemize}
\item D7.1 Review
\item T7.2 Secondary Tools Chain Status and Steps
\end{itemize}

\section{Discussion}

\begin{itemize}
\item D7.1 Review\\
Document has been updated after Review. Status is now approaching "Closing" state. No major technical options are open. The decisions proposed in the document will be finalized in Braunschweig. Open issues are related to resource allocations for covering the modelling efforts. These issues will be taken care of outside D7.1, e.g., in the PCC scheduled in Braunschweig.\\

\item T7.2 Secondary Tools Chain Status and Steps\\
Work on secondary ttols chain is now proceeding. A draft document for this artefact is available. The process for benchmaking is open and needs definition.
\url{https://github.com/openETCS/model-evaluation/wiki/Secondary-Tools-Analyses}
\end{itemize}

%\line(1,0){440}
\section{Notes}

\end{document}
