
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}



% Page layout (geometry)
\title{Meeting Minute openETCS WP7: Toolchain}
\author{Hekele, Bernd}
\date{2013-03-20}

\begin{document}
\section*{\large{Meeting Minute openETCS WP7: Toolchain \ \ \ \ 2013-03-15}}

\emph{Called up by: \ Dr. Klaus Ruediger Hase.}\\
\emph{Minutes by: \ \  Bernd Hekele.}

\subsection*{Participants:} WP7, 
Michael Jastram, 
Marc Behrens, 
%Cecile Braunstein,
Cyril Cornu, 
%Frank Golatowski, 
Klaus-Ruediger Hase, 
Bernd Hekele,
Jonas Helming,
Rico Kaseroni, 
Peter Mahlmann, 
%Marielle Petit-Doche, 
Ralf Pinger\\
%Stan Pinte, 
%Stefan Rieger, 
%Jan Welvaarts\\

%Jens Gerlach, 
%Merlin Pokam, 
%Jan Welte,
%Baseliyos Jacob, Joao Santos, Uwe Steinke, Roberto, Kretschmer

\subsection*{Meeting Time: from 11:00h \ to: \ 11:30h}

\subsection*{Type of conference: Telco}

\line(1,0){440}
\section*{\underline{Agenda}}
\begin{enumerate}
\item Tools Workshop April
\end{enumerate}
\line(1,0){440}
\section*{\underline{Discussion}}

\begin{enumerate}

\item Tools Workshop in April
Preparation for tools workshop started. Proposed Agenda is in review. Meeting is planned to be handled as an "open" meeting - participation from outside the project is welcome. Meeting is made visible via google calendar. DSetails, especially regarding the process for tools selection is still in work.

\end{enumerate}

\line(1,0){440}
\section*{\underline{Notes}}

\end{document}
