
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}



% Page layout (geometry)
\title{Meeting Minute openETCS WP7: Toolchain}
\author{Hekele, Bernd}
\date{2013-04-05}

\begin{document}
\section*{\large{Meeting Minute openETCS WP7: Toolchain \ \ \ \ 2013-04-05}}

\emph{Called up by: \ Dr. Klaus Ruediger Hase.}\\
\emph{Minutes by: \ \  Bernd Hekele.}

\subsection*{Participants:} WP7, 
Michael Jastram, 
Marc Behrens, 
Benjamin Beichler,
Cecile Braunstein,
Cyril Cornu,
%Silvano Dal Zilio,
%Michael Ditze, 
Frank Golatowski, 
Baseliyos Jacob,
Klaus-Ruediger Hase, 
Bernd Hekele,
Jonas Helming,
%Rico Kaseroni, 
Roberto Kretschmer,
%Peter Mahlmann, 
Marielle Petit-Doche, 
%Ralf Pinger,
Stan Pinte, 
%Merlin Pokam,
Stefan Rieger, 
%Joao Santos,
Uwe Steinke\\
%Jan Welvaarts

%Jens Gerlach, 
%Merlin Pokam, 
%Jan Welte,
%Baseliyos Jacob, Joao Santos, Uwe Steinke, Roberto, Kretschmer

\subsection*{Meeting Time: from 11:00h \ to: \ 11:30h}

\subsection*{Type of conference: Telco}

\line(1,0){440}
\section*{\underline{Agenda}}
\begin{enumerate}
\item WP2 Deliverables
\item List of Criteria
\item WP7 Workshop

\end{enumerate}
\line(1,0){440}
\section*{\underline{Discussion}}

\begin{enumerate}

\item WP2 Deliverables:
Some WP2 deliverables needed in WP7 now have delay. Reason is the intensive work in the Security Workshop in Charleroi an the impact of results on the content of the requirement documents in work.\\
Impact on WP7 deliverables to be clarified.
\item List of Criteria:\\
Marielle will produce a list of criteria for a certifiable tool chain and set up a telco on Tuesday to discuss it.
\item WP7 Workshop:\\
A WP7 team meeting will start on 15th of April 11:00 before the workshop.
The organization of the workshop is on track.

\end{enumerate}

\line(1,0){440}
\section*{\underline{Notes}}

\end{document}
