
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
%Organised by &Klaus-R\"udiger Hase\\
Organised by &Bernd Hekele\\
Minutes by & Bernd Hekele\\
When & January, 9th, 2015, 10:00 - 12:00\\
Location & Telco and Goto-Meeting\\
%9:30-10:00 and 
%\hline
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
10:15 - 10:30 & Nicolas van Landeghem & WP5: Demonstration \\\hline  
%10:30 - 11:00 & Jan Welte & WP4: Verification \& Validation \\\hline  
10:30 - 11:00 & Marc Behrens & WP4: Verification \& Validation \\\hline  
%10:45 - 11:00 & Fausto Cochetti & WP3: Modelling \\\hline  
%10:45 - 11:00 & Peter Mahlmann & WP3: Modelling \\\hline  
10:45 - 11:00 & Bernd Hekele & WP3: Modelling \\\hline  
11:00 - 11:45 &  & WP7: Toolchain \\\hline
%11:15 - 11:30 & Baseliyos Jacob & WP2: API Requirements \\\hline  
11:45 - 12:00 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
%11:15 - 11:45 & Bernd Hekele & PMB: Project Management Board \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} \\\hline
% Name                  6   5   4   3   7   P
%Alexander Nitsch     &   &   &   &   &   &   \\\hline  
%Alexander Stante     &   &   &   &   & x & x \\\hline 
Baseliyos Jacob      & x & x & x & x & x & x \\\hline 
%Bernd Gonska         &   &   & x &   &   &   \\\hline
Bernd Hekele         & x & x & x & x & x & x \\\hline
Benjamin Beichler    & x & x & x & x &   &   \\\hline
Cecile Braunstein    &   &   & x & x & x & x \\\hline
%Christian Giraud     &   &   &   &   &   &   \\\hline
%Christian Stahl      &   &   &   & x &   &   \\\hline
%David Mentre         &   &   &   &   &   &   \\\hline
%Fausto Cochetti      &   & x & x & x & x &   \\\hline
%Hardi Hungar         &   &   & x &   & x &   \\\hline
%Huu-Nghia Nguyen     & x &   & x & x & x &   \\\hline
%Ion I. Uribe         &   &   & x &   &   &   \\\hline
Izaskun de la Torre  & x & x & x & x & x &   \\\hline
%Jan Welte            & x & x & x & x & x & x \\\hline
%Jaime Paniagua       &   &   &   & x &   &   \\\hline
%Jakob Gaertner       &   &   &   & x & x &   \\\hline
%Jan Welvaarts        &   & x & x & x &   &   \\\hline
Jens Gerlach         &   &   & x & x &   &   \\\hline
%Jonas Helming        &   &   &   &   &   &   \\\hline
%Jos Holtzer          & x &   &   &   &   &   \\\hline
%Karsten Falk         &   &   & x & x & x & x \\\hline
Klaus-R\"udiger Hase & x & x & x & x & x & x \\\hline
%Laurent Ferier       &   &   &   & x & x & x \\\hline
%Lukasz Fronc         &   &   &   &   & x & x \\\hline
Marc Behrens         &   &   & x & x & x & x \\\hline
Marielle Petit-Doche &   &   & x & x & x & x \\\hline
%Mathilde Arnaud      &   &   &   &   &   &   \\\hline
%Matthieu Perin       &   &   &   & x & x &   \\\hline
%Michael Jastram      &   & x & x & x & x & x \\\hline
Nicolas van Landeghem& x & x & x &   &   &   \\\hline
Peter Mahlmann       & x & x & x & x & x & x \\\hline
%Peyman Farhangi      &   & x & x & x & x & x \\\hline
Pierre-Yves Le Morvan& x & x & x & x &   &   \\\hline
%Silvano dal Zilio    &   &   & x & x & x &  \\\hline
Stefan Karg          & x & x & x & x & x &   \\\hline
Stefan Rieger        & x & x & x & x & x &   \\\hline
Uwe Steinke          & x & x & x & x & x &   \\\hline
%Veronique Gontier    &   & x & x & x & x &   \\\hline
%Vincent Nuhaan       &   &   &   & x &   &   \\\hline
% Name                  6   5   4   3   7   P  \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{WP6: Dissemination}
\begin{itemize}
\item Activities\\
The link to the Itea Co-Summit event is visible in the Wiki:
\url{https://github.com/openETCS/Dissemination/wiki/ITEA-ARTEMIS-Co-Summit-2015}.\\
 Please, use the doodle for showing your participation.
\url{http://doodle.com/4wwcndmadvg8vtu3#table}. Participants for the Itea summit need to register at Itea website.

In preparation to the Co-Summit event a rehearsal for the actual Itea review meeting is planned. Location will be in Berlin as well. The ERSA feedback for the participation is outstanding.

\item D6.4 Review of Deliverable Exploitation Plan\\
The exploitation plan is ready for review. Izaskun confirmed to pick this activity. Due date is January 16th.

\end{itemize}

\subsection{WP5: Demonstration}
\begin{itemize}
\item Activities\\
The separation of interfaces (CORBA based) is completed. The deliverable is ready for use in openETCS.
For partners willing to use it ERSA is proposing a training session (gotomeeting). Participation is expected by partners who also participated in the ERSA testing tool workshop.

ERSA already has data for the Utrecht-Amsterdam track in stock. To enable use within openETCS a permit by NS is needed. (AI Baseliyos to contact NS for confirmation).

WP4 activities are started for providing scenarios for Utrecht Amsterdam to be used with the ERSA tool.

D5.1 review comments have been received and will be incorporated.

The use of TC-Sim in openETCS needs clarification (AI Bernd).
 
\end{itemize}

\subsection{WP4: Validation \& Verification}
\begin{itemize}
\item Activities\\
Handover of the first iteration release by WP3 is done. WP4 is now planning the activities in more detail.

\end{itemize}

\subsection{WP3: Modelling}


\begin{itemize}
\item WP3 Activities\\
Use cases (scenarios) have been defined in the WP3 backlog. The items are listed according to the priority. Cases 1 to 4 are expected for presentation at the itea review in March.

\begin{itemize}
\item Issue \#66: Use Case 1\\
Start of Mission and connection to the RBC  US-Operational Scenarios on Utrecht Amsterdam

\item Issue \#67: Use Case 2\\
Train is running after receiving a Movement Authority (MA) US-Operational Scenarios on Utrecht Amsterdam

\item Issue \#68: Use Case 3\\
ETCS Brake intervention (revokation of MA or not allowed speed) US-Operational Scenarios on Utrecht Amsterdam

\item Issue \#69: Use Case 4\\
Train is reading track information - Train is sending information to the track. US-Operational Scenarios on Utrecht Amsterdam
\end{itemize}

Other scenarios are also been published but will be treated with reduced priority.
 
\item Scade Training\\
The Scade training is scheduled now for 12th of January - 16th of January.
The date has been confirmed by Esterel. Invitations are sent to the participants.

\end{itemize}

\subsection{WP7: Toolchain}

\begin{itemize}
\item WP7 Leadership\\
Currently, WP7 leader position is not staffed. Projectoffice could not find the funding of Michaels position. So far, it was not possible to find a substitute either. Klaus-R\"udiger will jump in for the time being. 

For  checking on the consequences and looking for an alternative solution project office will call for a meeting with WP7 representatives. (AI KRH). Prposed date: January 19th.

The regular WP7 meetings (e.g., scrum) will be continued.

\end{itemize}

\subsection{PMB: Project Management Board}
\begin{itemize}
\item ITEA/Artemis Co-summit (March 10th - 11th)\\
will be combined with the first rehearsal of the ITEA review meeting (March 12th, 8-13h)

\item ITEA review meeting in Paris\\
will be combined with the final rehearsal, a workshop and a PCC meeting. Details can be found in the management wiki \url{https://github.com/openETCS/management/wiki/ITEA-Review-2015}.\\
Please indicate your participation by filling this doodle: \url{http://doodle.com/45krxsz6v6rew8vq}.\\
Current planning:\\
\begin{itemize}
\item March 24th:\\
8-13h rehearsal of the review meeting\\
14-17h PCC meeting\\
\item March 25th:\\
8-13h review meeting\\
14-17h combined WP3 \& WP4 workshop \\
\end{itemize}
\item Advisory Board Meeting\\
will take place on March 26th in Brussels

\item GitHub repository and copyright notices\\
Copyright notices are mandatory for all deliverables. The issue is solved for documents by the template. But also for code the copyright has to be explicitly documented for all functions (e.g., the copyright has to be part of the .H header). 

\item Product backlog grooming\\
Took place and is documented in the openETCS backlog.


\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/\jobname}. Please, use the issue tracker for findings with the minutes.

\end{itemize}

\end{document}
