
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\usepackage{booktabs}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}

\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum Meetings\\
Minutes by & Peter Mahlmann (DB Netz AG)\\
When & September 4th, 2015, 9:45 AM -- 11:45 AM\\
Location & Telco and GoToMeeting\newline \url{https://global.gotomeeting.com/meeting/join/493963173}\\
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting Agenda}

\begin{tabular}{lll}
\toprule
\textbf{Slot} &  \textbf{Chair} & \textbf{Work P ackage} \\
\midrule 
9:45 AM -- 10:15 AM & Peter Mahlmann & Product Backlog Grooming  \\
10:15 AM -- 10:30 AM & Matthieu Poirot & WP5 openETCS Demonstrator \\  
10:30 AM -- 10:45 AM & Marc Behrens & WP4 Validation \& Verification \\
10:45 AM -- 11:00 AM & Bernd Hekele & WP3 Modeling \\
11:00 AM -- 11:15 AM & Michael Jastram  & WP7 openETCS Tool Chain \\
11:15 AM -- 11:45 AM & Klaus-R\"udiger Hase & Project Management Board \\
\bottomrule
\end{tabular}

\section{List of Attendees}

\begin{table}[htbp]
    \begin{tabular}{rrr}
    \toprule
    \textbf{Name} & \textbf{Join Time} & \textbf{Leave Time} \\
    \midrule
    Alexander Pinnau (ICS) & 10:30 AM & 11:09 AM \\
    Baseliyos Jacob & 9:53 AM & 12:07 PM \\
    Behrens, Marc & 9:46 AM & 10:59 AM \\
    FAUDOU raphael & 11:17 AM & 12:07 PM \\
    Ingo Weigelt & 9:44 AM & 12:07 AM \\
    Jan Welte (TU-BS) & 9:47 AM & 12:07 PM \\
    Johannes Kastner (ICS) & 10:42 AM & 11:09 AM \\
    Marc Pantel & 11:13 AM & 11:56 AM \\
    Marielle Petit-Doche & 10:26 AM & 12:07 PM \\
    Matthieu POIROT -ERSA & 9:58 AM & 12:03 PM \\
    Michael Jastram & 9:44 AM & 12:07 PM \\
    Nasir Mohamed (AEbt) & 10:01 AM & 12:07 PM \\
    openETCS  Office (KRH) & 9:51 AM & 12:07 PM \\
    Peter Mahlmann (DB) & 9:43 AM & 12:07 PM \\
    Stefan Karg (LEA Railergy) & 9:55 AM & 12:07 PM \\
    Stefan Rieger & 10:34 AM & 11:59 AM \\
    Thorsten Schulz (Uni Ro) & 10:34 AM & 11:18 AM \\
    \bottomrule
    \end{tabular}%
\end{table}%



\section{Minutes}

\subsection{Product Backlog Grooming}
\begin{itemize}
\item The product backlog is available to the public via 
\url{https://github.com/openETCS/product-backlog}. 
\item For the results of grooming session we refer to the waffle.io scrum board \url{https://waffle.io/openETCS/product-backlog} (free registration for waffle.io needed).
\end{itemize}

\subsection{WP6: Dissemination}
\begin{itemize}
\item The WP6 meeting was canceled, the WP6 slot has been used for product backlog grooming.
\end{itemize}

\subsection{WP5 openETCS Demonstrator}
\begin{itemize}
\item The meeting scheduled for discussion about the generic openETCS API between ERSA and MERCE could not take place due to time conflicts of the involved parties. Email will be used for coordination instead.
\item The ERSA API will be used as the openETCS generic API.
\item A first draft of the API software wrapper respectively glue code, needed to connect WP3 OBU model and ERSA demonstrator should be available within the next two weeks.
\end{itemize}

\subsection{WP4 Validation \& Verification}
\begin{itemize}
\item The description of work for the internal assessment has been completed.
\item All \emph{plan} documents (e.g. QA plan, V\&V plan, etc.) will be freezed for validation by end of September. The results are expected to be available by October 15th. For software documentation (e.g. the architecture and design description) the final deadline for the internal assessment will be November 15th. Changes made after November 15th will not be considered in the internal assessment.
\item A detailed review of the checkBGConsistency OBU component and its documentation in the ADD has been done (c.f. \url{https://github.com/openETCS/validation/issues/301}).
\end{itemize}

\subsection{WP3 Modeling}
\begin{itemize}
\item Most of the modeling activities this week were focused on the development of a demonstrator needed for next week.
\item Concerning the overall modelling activities the focus currently lies on user stories 7,8, and 9.
\item Information filter component: bugs and especially the work arounds for these bugs that have been created in the model (e.g. short cuts) turned out to be a major problem in the V\&V. Action will be taken on this from the side of WP3.
\item From side of WP4 it is noted that many behavioral bugs in the model occur due to the fact that the update of components/modules in case of a level/mode change is not handled or in a globally defined way.
\end{itemize}

\subsection{WP7 openETCS Tool Chain}
\begin{itemize}
\item New RMF (Requirements Modeling Framework) release is imminent and will be included in the openETCS tool chain.
\item Partner ENSEEIHT is still trying to subcontract Samares Engineering to take action on traceability.
\item Master branch error free proposal will be updated next week.
\end{itemize}

\subsection{Project Management Board}
\begin{itemize}
\item Concerning the pending subcontract to Samares Engineering (c.f. WP7) no reaction has been received from the french cluster leader for several month despite of repeated requests. Thus, It has been decided to bypass the french cluster leader.
\item The focus of WP3 creating a simulation environment (to allow demonstration and visualization) and model development (i.e. implementing additional functionality) has been discussed.
\end{itemize}


\section{General Remarks}

\begin{itemize}
\item Please find these minutes online at \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/\jobname.pdf}. Please, use the github issue tracker for findings and corrections within the minutes.
\end{itemize}

\end{document}
