
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
Organised by & Bernd Hekele\\
Minutes by & Bernd Hekele\\
When & May 23rd, 2014, 9:30 - 12:00\\
Location & Telco and Goto-Meeting\\
%9:30-10:00 and 
%\hline
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
09:30 - 10:00 & Bernd Hekele & WP3: Modelling (team activities)\\\hline
%10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
10:15 - 10:30 & Nicolas van Landeghem & WP5: Demonstration \\\hline  
10:30 - 10:45 & Marc Behrens & WP4: Verification \& Validation \\\hline  
10:45 - 11:00 & Bernd Hekele & WP3: Modelling \\\hline  
11:00 - 11:15 & Michael Jastram & WP7: Toolchain \\\hline
%11:15 - 11:30 & Baseliyos Jacob & WP2: API Requirements \\\hline  
11:15 - 11:30 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
11:15 - 12:00 & Klaus-R\"udiger Hase & ITEA Review Preparation \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant} &  \textbf{WP3} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} & \textbf{ITEA} \\\hline
% Name                  3    6   5   4   3   7   P   I
%Alessandro Cimatti    &   &   &   &   &   &   &   &   \\\hline 
Alexander Nitsch      & x &   &   & x & x & x & x & x \\\hline  
Alexander Stante      &   &   &   & x & x & x &   &   \\\hline 
%Baseliyos Jacob       &   &   &   &   &   &   &   &   \\\hline 
%Benjamin Beichler     &   &   &   &   &   &   &   &   \\\hline 
Bernd Hekele          & x &   & x & x & x & x & x & x \\\hline
Cecile Braunstein     &   &   &   & x & x & x &   &   \\\hline
%Christian Giraud      &   &   &   &   &   &   &   &   \\\hline
Christian Stahl       & x &   & x & x & x &   &   &   \\\hline
%David Mentre          &   &   &   &   &   &   &   &   \\\hline
%Fausto Cochetti       &   &   &   &   &   &   &   &   \\\hline
%Giovanni Trotta       &   &   &   &   &   &   &   &   \\\hline
Giovanni Zanelli      &   &   &   &   &   & x & x & x \\\hline
Hardi Hungar          &   &   &   & x &   &   &   &   \\\hline
%Huu-Nghia Nguyen      &   &   &   &   &   &   &   &   \\\hline
%Izaskun de la Torre   &   &   &   &   &   &   &   &   \\\hline
Jan Welte             & x &   & x & x & x &   &   &   \\\hline
%Jan Welvaarts         &   &   &   &   &   &   &   &   \\\hline
Jens Gerlach          &   &   &   & x &   &   &   &   \\\hline
%Jonas Helming         &   &   &   &   &   &   &   &   \\\hline
Klaus-R\"udiger Hase  & x &   & x & x & x & x & x & x \\\hline
Laurent Ferier        &   &   &   &   &   &   & x & x \\\hline
%Lukasz Fronc          &   &   &   &   &   &   &   &   \\\hline
Marc Behrens          &   &   &   & x & x & x & x & x \\\hline
%Marielle Petit-Doche  &   &   &   &   &   &   &   &   \\\hline
%Mathilde Arnaud       &   &   &   &   &   &   &   &   \\\hline
Matthieu Perin        &   &   &   &   &   & x &   &   \\\hline
Michael Jastram       &   &   &   &   &   & x & x & x \\\hline
Nicolas van Landeghem & x &   & x & x &   &   &   &   \\\hline
Peter Mahlmann        & x &   & x & x & x & x & x & x \\\hline
Peyman Farhangi       & x &   & x & x & x & x & x & x \\\hline
Silvano dal Zilio     &   &   &   &   &   &   &   &   \\\hline
Stefan Rieger         &   &   &   &   &   &   &   &   \\\hline
Uwe Steinke           & x &   & x & x &   & x &   &   \\\hline
Vincent Nuhaan        & x &   & x & x &   &   &   &   \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{WP6: Dissemination}

No meeting this date.

\subsection{WP5: Demonstration}
\begin{itemize}
\item Update on Activities\\
A planning meeting with ERSA and DB was held. The meeting was used for technical discussions on the ERSA contribution to the API. Also, concepts for the integration of modelling results into the ERSA application were touched.
\end{itemize}


\subsection{WP4: Validation \& Verification}
\begin{itemize}
\item upcoming events\\
The agenda for the Braunschweig test training is now in available. The meeting is scheduled June 4th and 5th. You find details to the meetin in this wiki: Here is the agenda: \url{https://github.com/openETCS/validation/wiki/Agenda-for-Test-Training}.

\item Internal Assessment\\
The follow up to the internal assessment meeting is scheduled for 12.June. It is planned to take place after the Itea Review meeting.

\end{itemize}

\subsection{WP3: Modelling}

\begin{itemize}
\item Upcoming Events\\
The next \textbf{WP3 modelling workshop}, now under management by Alstom, is  scheduled to take place on May 26th - May 28th. Agenda and further reading can be found here: \url{https://github.com/openETCS/modeling/tree/master/meetings/Team-Meeting_Brussels-2014-05-26}

\item each partner: impediments, progress\\
Uwe has updated the Scade model on location information. The model can be discussed at the WP3 workshop. Vincent has updated the xls for section 5 of the SRS.

\item a.o.b.\\

\end{itemize}

\subsection{WP7: Toolchain}

The backlog and the resource plan have been updated.

In consequence to insufficient contribution to the WP in the past the toolchain wants to improve management. The backlog is now managed on a smaller granularity. Target: provide easy tasks which can be picked by persons even if they are not experts.


\subsection{WP2: Requirements}

No meeting this week.

\subsection{PMB: Project Management Board}
\begin{itemize}
\item PCC Meeting scheduled
\item Proposal for an openETCS Product Backlog
\item Preparation of the ITEA Review Meeting

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/Minute_20140523.pdf}. Please, use the issue tracker for findings with the minutes.

Starting with 23rd of May the minutes will be provided in one document for the whole meeting series of a day.

\end{itemize}

\end{document}
