
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\usepackage{booktabs}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}

\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum Meetings\\
Minutes by & Peter Mahlmann (DB Netz AG)\\
When & October 16th, 2015, 9:45 AM -- 11:45 AM\\
Location & Telco and GoToMeeting\newline \url{https://global.gotomeeting.com/meeting/join/493963173}\\
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting Agenda}

\begin{tabular}{lll}
\toprule
\textbf{Slot} &  \textbf{Chair} & \textbf{Work Package} \\
\midrule 
9:45 AM -- 10:15 AM & Peter Mahlmann & Product Backlog Grooming  \\
10:15 AM -- 10:30 AM & Matthieu Poirot & WP5 openETCS Demonstrator \\  
10:30 AM -- 10:45 AM & Marc Behrens & WP4 Validation \& Verification \\
10:45 AM -- 11:00 AM & Bernd Hekele & WP3 Modeling \\
11:00 AM -- 11:15 AM & Michael Jastram & WP7 openETCS Tool Chain \\
11:15 AM -- 11:45 AM & Klaus-R\"udiger Hase & Project Management Board \\
\bottomrule
\end{tabular}

\section{List of Attendees}

\begin{table}[htbp]
    \begin{tabular}{rrr}
    \toprule
    \textbf{Name} & \textbf{Join Time} & \textbf{Leave Time} \\
    \midrule
    BaseliyosJacob & 10:32 AM & 11:14 AM  \\
    Behrens, Marc & 9:44 AM & 11:40 AM  \\
    Bernd Hekele (DB) & 9:46 AM & 11:42 AM  \\
    COCHETTI Fausto & 9:47 AM & 11:10 AM  \\
    Sylvano Dalzilio (LAAS) & 10:52 AM & 11:25 AM  \\
    FAUDOU Raphael & 9:53 AM & 10:52 AM \\
    Ghiglia, Jonathan R (GE) & 10:09 AM & 10:40 AM \\
    GIRAUD Christian & 9:10 AM & 9:37 AM  \\
    Jens Gerlach & 10:28 AM & 10:44 AM \\
    Johannes Kastner (ICS) & 10:12 AM & 11:10 AM  \\
    Lampatzer, Rainer (ICS)& 10:52 AM & 11:20 AM \\
    Marielle Petit-Doche & 10:55 AM & 11:24 AM  \\
    Matthieu Poirot (ERSA) & 9:43 AM & 11:24 AM  \\
    Michael Jastram & 9:45 AM & 11:42 AM  \\
    Peter Mahlmann (DB) & 9:44 AM & 11:24 AM  \\
    Klaus-R\"udiger HAse (DB) & 9:44 AM & 11:42 AM  \\
    Thorsten Schulz (Uni Ro) & 10:23 AM & 11:41 AM  \\
    Uwe Steinke (Siemens) & 9:42 AM & 11:26 AM  \\

     \bottomrule
    \end{tabular}%
  \label{tab:addlabel}%
\end{table}%




\section{Minutes}

\subsection{Product Backlog Grooming}
\begin{itemize}
\item The product backlog is available via 
\url{https://github.com/openETCS/product-backlog}. 
\item For the results of the grooming session we refer to the corresponding waffle.io scrum board available via \url{https://waffle.io/openETCS/product-backlog} (free GitHub account needed).
\end{itemize}

\subsection{WP6: Dissemination}
\begin{itemize}
\item The WP6 meeting was canceled, the slot of this meeting has been used for product backlog grooming instead.
\end{itemize}

\subsection{WP5 openETCS Demonstrator}
\begin{itemize}
\item M5.3.2 Basic demonstrator including sources and documentation has been delivered, cf. \url{https://github.com/openETCS/demonstrator/tree/master/Sources/M5.3.2%20-%20Basic%20Demonstrator%20Release%201}.
\item The non-vital demonstrator based on GE hardware has been demonstrated at the Test4Rail conference. Here, the audience feedback was extremely positive.
\end{itemize}

\subsection{WP4 Validation \& Verification}
\begin{itemize}
\item A brief update on the openETCS activites at the Test4Rail conference was given.
\item The openETCS SysML models needed for the hazard and risk analysis have been delivered by DB. Accordingly, All4tec will start with the analysis using safety architect.
\item FhG gave a brief update on the current state of the Bitwalker component. The component is considered to be ready for integration now.
\item The progress on \emph{Use Case 9} has been disucssed. Here, some errors on coding level have been identified.
\end{itemize}

\subsection{WP3 Modeling}
\begin{itemize}
\item The interface of the EVC model will be freezed from now on to allow WP5 the integration into the demonstrator.
\item Issues with the MARequest component have been identified and are beeing fixed. These issues relate to \emph{Use Case 9}, cf. WP4 section.
\item Updates on the TrackAtlas component by LEA are expected to be delivered within the next days.
\item Regression tests are ongoing after a major model update.
\item A possible technical meeting between DB and Alstom for the integration of components developed by Alstom has been discussed. A possible date for this meeting is the last week of October. To reduce travel expenses for some partners the meeting may be held as an online meeting.
\end{itemize}

\subsection{WP7 openETCS Tool Chain}
\begin{itemize}
\item Concerning the migration path to an open source tool chain a first draft is expected for next week.
\item Concerning the SysML to B user story Acceleo will be integrated into the tool chain, so that MERCE can continue to work on this.
\item The WP7 homepage will be redesigned (\url{http://openetcs.org/tool/}).
\end{itemize}

\subsection{Project Management Board}
\begin{itemize}
\item The organization of the exploitation workshop on November 23/24 has been briefly discussed. DB will contact the WP leaders to discuss further details within the next weeks.
\end{itemize}

\section{General Remarks}

\begin{itemize}
\item Please find these minutes online at \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/\jobname.pdf}. Please, use the github issue tracker for findings and corrections within the minutes.
\end{itemize}

\end{document}
