
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
%Organised by &Klaus-R\"udiger Hase\\
Organised by &Bernd Hekele\\
Minutes by & Bernd Hekele\\
When & January, 30th, 2015, 09:45 - 11:05\\
Location & Telco and Goto-Meeting\\
%9:30-10:00 and 
%\hline
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
9:45 - 10:00 & Peter Mahlmann & openETCS Backlog Grooming  \\\hline
10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
10:15 - 10:30 & Nicolas van Landeghem & WP5: Demonstration \\\hline  
%10:30 - 11:00 & Jan Welte & WP4: Verification \& Validation \\\hline  
10:30 - 11:00 & Marc Behrens & WP4: Verification \& Validation \\\hline  
%10:45 - 11:00 & Fausto Cochetti & WP3: Modelling \\\hline  
%10:45 - 11:00 & Peter Mahlmann & WP3: Modelling \\\hline  
10:45 - 11:00 & Bernd Hekele & WP3: Modelling \\\hline  
11:00 - 11:15 & Alexander Stante  & WP7: Toolchain \\\hline
%11:15 - 11:30 & Baseliyos Jacob & WP2: API Requirements \\\hline  
11:15 - 11:30 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
%11:15 - 11:45 & Bernd Hekele & PMB: Project Management Board \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant}  & \textbf{G} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} \\\hline
% Name               G   6   5   4   3   7   P
%Alexander Nitsch    &   &   &   &   &   &   &   \\\hline  
%Alexander Stante     &  &   &   &   &   & x & x \\\hline 
Baseliyos Jacob       & x & x & x & x & x & x & x \\\hline 
%Bernd Gonska         & &   &   & x &   &   &   \\\hline
Bernd Hekele         & x & x & x & x & x & x & x \\\hline
Benjamin Beichler    & x & x & x & x & x &   &   \\\hline
Cecile Braunstein    & x &   &   & x & x & x & x \\\hline
%Christian Giraud     &   &   &   &   &   &   &   \\\hline
Christian Stahl      &   &   &   &   & x &   &   \\\hline
%David Mentre         &  &   &   &   &   &   &   \\\hline
%Fausto Cochetti      &  &   & x & x & x & x &   \\\hline
Hardi Hungar         &  &   &   & x &   & x &   \\\hline
%Huu-Nghia Nguyen     &  & x &   & x & x & x &   \\\hline
%Ion I. Uribe         &  &   &   & x &   &   &   \\\hline
Izaskun de la Torre  &  & x & x & x & x & x &   \\\hline
%Jan Welte            &  & x & x & x & x & x & x \\\hline
%Jaime Paniagua       &  &   &   &   & x &   &   \\\hline
%Jakob Gaertner       &  &   &   &   & x & x &   \\\hline
%Jan Welvaarts        &  &   & x & x & x &   &   \\\hline
Jan Welte            & x & x & x & x & x &   &   \\\hline
%Jens Gerlach         &   &   &   & x & x &   &   \\\hline
%Jonas Helming        &   &   &   &   &   &   &   \\\hline
%Jos Holtzer          &   & x &   &   &   &   &   \\\hline
%Karsten Falk         &   &   &   & x & x & x & x \\\hline
%Klaus-R\"udiger Hase & x & x & x & x & x & x & x \\\hline
%Laurent Ferier       &   &   &   &   & x & x & x \\\hline
%Lukasz Fronc         &   &   &   &   &   & x & x \\\hline
Marc Behrens         & x & x & x & x & x & x & x \\\hline
Marielle Petit-Doche &   &   &   & x & x & x & x \\\hline
%Mathilde Arnaud      &   &   &   &   &   &   &   \\\hline
Matthieu Perin       &   &   &   & x & x & x &   \\\hline
%Michael Jastram      &   &   & x & x & x & x & x \\\hline
%Nicolas van Landeghem &   & x & x & x &   &   &   \\\hline
Peter Mahlmann       & x & x & x & x & x & x & x \\\hline
%Peyman Farhangi      &   &   & x & x & x & x & x \\\hline
Pierre-Yves Le Morvan &   & x & x & x & x &   &   \\\hline
%Silvano dal Zilio    &   &   &   & x & x & x &  \\\hline
Stefan Karg          &   & x & x & x & x & x &   \\\hline
Stefan Rieger        &   & x & x & x & x & x &   \\\hline
Uwe Steinke          &   & x & x & x & x & x &   \\\hline
Valerio D'Angelo     &   & x & x & x & x & x &   \\\hline
%Veronique Gontier    &   &   & x & x & x & x &   \\\hline
%Vincent Nuhaan       &   &   &   &   & x &   &   \\\hline
% Name               G   6   5   4   3   7   P  \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{openETCS Grooming}
\begin{itemize}
\item Backlog Grooming Session\\
happened. The online backlog has been updated.
\end{itemize}

\subsection{WP6: Dissemination}
\begin{itemize}
\item Activities\\
The link to the Itea Co-Summit event is visible in the Wiki:
\url{https://github.com/openETCS/Dissemination/wiki/ITEA-ARTEMIS-Co-Summit-2015}.\\

\item D6.4 Review of Deliverable Exploitation Plan\\
The exploitation plan is ready for review. Izaskun confirmed to pick this activity. Due date is January 16th.

\end{itemize}

\subsection{WP5: Demonstration}
\begin{itemize}
\item Activities\\
Technical issues have been reported for the (CORBA based) platform.  Problems are under investigation.

WP4 activities are started for providing scenarios for Utrecht Amsterdam to be used with the ERSA tool.

WP5 needs the definition of the API for being able to progress with the interfaces to the WP3 results. A session is requested to clarify the status and decisions and to agree on the next an implementation strategy.
\end{itemize}

\subsection{WP4: Validation \& Verification}
\begin{itemize}
\item Activities\\
Systerel plans to demonstrate formal verification at parts of the openETCS Scade models. Work at the WP4 deliverables is progressing. 

First iteration release grooming at WP4 took place. Works has been distributed to WP4 partners. 

\end{itemize}

\subsection{WP3: Modelling}


\begin{itemize}
\item WP3 Activities\\
Modelling work is progressing.
Integration of the models will start next week in Braunschweig, Berlin and Munich. The team 1 will have a team meeting in Berlin as well.

\end{itemize}

\subsection{WP7: Toolchain}

\begin{itemize}
\item WP7 Leadership\\
Alexander Stante will jumpo in for the WP7 leadership until Michael is back in the openETCS team. Only small resources are available at the partners for 2015.

\end{itemize}

\subsection{PMB: Project Management Board}
\begin{itemize}
\item ITEA/Artemis Co-summit (March 10th - 11th)\\
will be combined with the first rehearsal of the ITEA review meeting (March 12th, 8-13h)

\item ITEA review meeting in Paris\\
will be combined with the final rehearsal, a workshop and a PCC meeting. Details can be found in the management wiki \url{https://github.com/openETCS/management/wiki/ITEA-Review-2015}.\\
Please indicate your participation by filling this doodle: \url{http://doodle.com/45krxsz6v6rew8vq}.\\
Current planning:\\

\begin{itemize}
\item March 24th:\\
8-13h rehearsal of the review meeting\\
14-17h PCC meeting\\
\item March 25th:\\
8-13h review meeting\\
14-17h combined WP3 \& WP4 workshop \\
\end{itemize}
\item Advisory Board Meeting\\
will take place on March 26th in Brussels

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/\jobname}. Please, use the issue tracker for findings with the minutes.

\end{itemize}

\end{document}
