
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
%Organised by &Klaus-R\"udiger Hase\\
Organised by & Peter Mahlmann\\
%Organised by & Baseliyos Jacob\\
Minutes by & Peter Mahlmann\\
When & August, 14th, 2015, 09:45 - 11:45\\
Location & Telco and Goto-Meeting\\
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
9:45 - 10:00 & Peter Mahlmann & openETCS Backlog Grooming  \\\hline
%9:45 - 10:00 & Baseliyos Jacob & openETCS Backlog Grooming  \\\hline
%10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
10:15 - 10:30 & Matthieu Poirot & WP5: Demonstration \\\hline  
%10:00 - 10:00 & Matthieu POIROT & WP5: Demonstration \\\hline
10:15 - 10:30 & Marc Behrens & WP4: Verification \& Validation \\\hline 
10:30 - 10:45 & Bernd Hekele & Modelling \\\hline
11:00 - 11:15 & Michael Jastram  & WP7: Toolchain \\\hline
11:15 - 11:45 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant}  & \textbf{G} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} \\\hline
% Name                  G   6   5   4   3   7   P
Abdelnasir Mohamed    &  &   & x & x  & x &x  &x  \\\hline 
%Alexander Probst      &  x &   & x  & x  & x & x &x  \\\hline  
Alexander Pinnau      &   &   &   & x & x &  &  \\\hline  
%Alexander Stante     &   &   & x  & x  & x & x &x  \\\hline 
Baseliyos Jacob       & x & x & x & x & x & x &  \\\hline 
%Bernd Gonska         & &   &   & x &   &   &   \\\hline
Bernd Hekele          & x & x & x & x & x & x & x \\\hline
%Benjamin Beichler     &   &   &   & x & x &  &   \\\hline
%Christian Giraud     &   &   &   &   &   &   &   \\\hline
%Christian Stahl      &   &   &  &  & x & x  &   \\\hline
Dario Mercuri         &   &   & x & x & x &  &   \\\hline
David Mentre          & x & x & x & x & x & x & x \\\hline
%Didier Weckmann      & x &   & x & x & x & x &  \\\hline
%Fausto Cochetti      &  x &   &  x & x & x & x & x \\\hline
%Frederique Vallee      & x  &   &  x & x & x & x &  \\\hline
%Hardi Hungar         &  &   &   & x &   & x &   \\\hline
Ingo Weigelt          & x & x & x & x & x & x &   \\\hline
%Ion I. Uribe         &  &   &   & x &   &   &   \\\hline
%Izaskun de la Torre  &  &   &   &   &   & x & x \\\hline
%Jakob Gaertner       &   &   &  & x & x &x   &   \\\hline
%Jan Welvaarts        &  &   & x & x & x &   &   \\\hline
Jan Welte             & x & x & x & x & x & x &   \\\hline
Jens Gerlach          &   &   &   & x &  &  &   \\\hline
%Karsten Falk         &   &   &   & x & x & x & x \\\hline
Klaus-R\"udiger Hase & x & x & x & x & x & x & x \\\hline
%Kolja Muchow  & x &   & x & x & x & x & x \\\hline
%Laurent Ferier       &   &   &   &   & x & x & x \\\hline
%Lukasz Fronc         &   &   &   &   &   & x & x \\\hline
Marc Behrens         & x & x & x & x & x & x & x  \\\hline
%Marielle Petit-Doche & x  &   & x & x & x & x &  \\\hline
%Mathilde Arnaud      &   &   &   &   &   &   &   \\\hline
%Matthieu Perin       &   &   &   & x & x & x &   \\\hline
Matthieu Poirot       & x & x & x & x & x & x & x  \\\hline
Michael Jastram       & x & x & x & x & x & x & x  \\\hline
Peter Mahlmann        & x & x & x & x & x & x & x \\\hline
%Peyman Farhangi      & x  &   & x & x & x & x & x  \\\hline
%Pierre-Yves Le Morvan &   &   & x & x & x &   &   \\\hline
%Silvano dal Zilio    &   &   &   &  &  & x &  \\\hline
Stefan Karg          & x  & x & x  & x & x & x & x \\\hline
%Stefan Rieger        &   &  & x & x & x & x &x  \\\hline
Thorsten Schulz      &   &   &  &  & x & x & x \\\hline
%Uwe Schulze          &   &   &   & x & x & x &   \\\hline
Uwe Steinke          & x & x & x & x & x & x & x \\\hline
%Valerio D'Angelo     & x &   & x & x  & x & x & x \\\hline
%Veronique Gontier    &   &   & x & x & x & x & x \\\hline
%Vincent Nuhaan       &   &   &   &   & x &   &   \\\hline
% Name                  G   6   5   4   3   7   P \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{openETCS Grooming}
\begin{itemize}
\item Product backlog grooming\\
The product backlog is available to the public via 
\url{https://github.com/openETCS/product-backlog}. For the results of grooming session we refer to the waffle.io scrum board \url{https://waffle.io/openETCS/product-backlog} (free registration for waffle.io needed).

\end{itemize}

\subsection{WP6: Dissemination}

The WP6 meeting was canceled.
 
\subsection{WP5: openETCS Demonstrator}

\begin{itemize}
\item GE demonstrator documentation has been uploaded to WP5 repository.
\item Hardware will be shipped from DE to DLR today.
\item A meeting between MERCE and ERSA is planned for the end of the month.
\end{itemize}

\subsection{WP4: Validation \& Verification}
\begin{itemize}
\item TUBS is currently working on SCADE traceability, for details see \url{https://github.com/openETCS/validation/wiki/Traceability-in-SCADE-Suite-Models}.\
\item It is requested that top-level components have the requirements they cover annotated in the SCADE comments at least.
\item The current state of the automatic error reports has been presented.
\end{itemize}

\subsection{WP3: Modelling}

\begin{itemize}
\item This week a meeting between ERSA and DB for further coordination took place at the site of ERSA France.
\item Lifecycle of data has been briefly discussed and will be topic for the next iteration.
\item The information filter module is currently in review by DB.
\item A new release with additional functionality is scheduled for today. The overall state is that the WP3 team is close to a release covering user story 7.
\item Documentation (D3.6.3/ADD, SysML models) is currently ongoing and coordinated by DB. All partners should deliver their input by August 18th.
\item Up to date SCADE code documentation (automatically generated) is needed by WP4.
\end{itemize}

\subsection{WP7: openETCS Tool Chain}

\begin{itemize}
\item The test plan has been presented by SQS. A recording of the gotomeeting session will be uploaded to the openETCS YouTube channel.
\item The roadmap how to transfer the openETCS resutls to a fully open tool chain has been discussed. A corresponding user story has been created in the product backlog.
\end{itemize}

\subsection{PMB: Project Management Board}

\begin{itemize}
\item All project partners should focus their effort and resources to the highest priority items in the product backlog.
\item For the german cluster the report to the project management agency in the DLR is due by tomorrow. A copy of the individual reports has to be sent to DB (electronically is sufficient).
\item The input to the ITEA PPR 2015 S1 is due by next Friday.
\end{itemize}

\section{Notes}


\begin{itemize}
\item You can find these minutes online at \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/\jobname}. Please, use the issue tracker for findings and corrections within the minutes.
\end{itemize}

\end{document}
