
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
Minutes by & Peter Mahlmann\\
When & August, 21th, 2015, 09:45 - 11:45\\
Location & Telco and Goto-Meeting\\
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
9:45 - 10:15 & Peter Mahlmann & openETCS Backlog Grooming  \\\hline
%9:45 - 10:00 & Baseliyos Jacob & openETCS Backlog Grooming  \\\hline
%10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
10:15 - 10:30 & Matthieu Poirot & WP5: Demonstration \\\hline  
10:30 - 10:45 & Marc Behrens & WP4: Verification \& Validation \\\hline 
10:45 - 11:00 & Bernd Hekele & Modelling \\\hline
11:00 - 11:15 & Michael Jastram  & WP7: Toolchain \\\hline
11:15 - 11:45 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c|c|c|c|c||c|c|}
\hline
\textbf{Participant}  & \textbf{G} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} \\\hline
% Name                  G   6   5   4   3   7   P
Abdelnasir Mohamed    &   &   & x & x & x & x & x \\\hline 
Alexander Pinnau      &   &   &   & x & x &   &   \\\hline  
%Alexander Stante     &   &   & x  & x  & x & x &x  \\\hline 
Baseliyos Jacob       & x &   & x & x & x & x & x \\\hline 
Bernd Hekele          &   &   & x & x & x & x & x \\\hline
Janathan Ghiglia      &   &   &   &   &   &   &   \\\hline
%Benjamin Beichler     &   &   &   & x & x &  &   \\\hline
%Christian Giraud     &   &   &   &   &   &   &   \\\hline
%Christian Stahl      &   &   &  &  & x & x  &   \\\hline
%Dario Mercuri         &   &   & x & x & x &  &   \\\hline
David Mentre          &   &   &   & x & x & x & x \\\hline
%Didier Weckmann      & x &   & x & x & x & x &  \\\hline
%Fausto Cochetti      &  x &   &  x & x & x & x & x \\\hline
%Frederique Vallee      & x  &   &  x & x & x & x &  \\\hline
%Hardi Hungar         &  &   &   & x &   & x &   \\\hline
%Ion I. Uribe         &  &   &   & x &   &   &   \\\hline
%Izaskun de la Torre  &  &   &   &   &   & x & x \\\hline
%Jakob Gaertner       &   &   &  & x & x &x   &   \\\hline
%Jan Welvaarts        &  &   & x & x & x &   &   \\\hline
Jan Welte             & x &   & x & x & x & x &   \\\hline
Jens Gerlach          &   &   &   & x &  &  &   \\\hline
%Karsten Falk         &   &   &   & x & x & x & x \\\hline
%Klaus-R\"udiger Hase & x & x & x & x & x & x & x \\\hline
%Kolja Muchow  & x &   & x & x & x & x & x \\\hline
%Laurent Ferier       &   &   &   &   & x & x & x \\\hline
%Lukasz Fronc         &   &   &   &   &   & x & x \\\hline
Marc Behrens          &   &   & x & x & x & x & x  \\\hline
%Marielle Petit-Doche & x  &   & x & x & x & x &  \\\hline
%Mathilde Arnaud      &   &   &   &   &   &   &   \\\hline
%Matthieu Perin       &   &   &   & x & x & x &   \\\hline
Matthieu Poirot       & x &   & x & x & x & x & x  \\\hline
Michael Jastram       & x &   & x & x & x & x & x  \\\hline
Peter Mahlmann        & x &   & x & x & x & x & x \\\hline
%Peyman Farhangi      & x  &   & x & x & x & x & x  \\\hline
%Silvano dal Zilio    &   &   &   &  &  & x &  \\\hline
Stefan Karg           & x &   & x  & x & x & x & x \\\hline
%Stefan Rieger        &   &  & x & x & x & x &x  \\\hline
Thorsten Schulz       &   &   &   &  & x & x & x \\\hline
%Uwe Schulze          &   &   &   & x & x & x &   \\\hline
Uwe Steinke           & x &   & x & x & x & x & x \\\hline
Ingo Weigelt          &   &   &   &   &   & x & x  \\\hline
%Veronique Gontier    &   &   & x & x & x & x & x \\\hline
%Vincent Nuhaan       &   &   &   &   & x &   &   \\\hline
% Name                  G   6   5   4   3   7   P \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{openETCS Grooming}
\begin{itemize}
\item Product backlog grooming\\
The product backlog is available to the public via 
\url{https://github.com/openETCS/product-backlog}. For the results of grooming session we refer to the waffle.io scrum board \url{https://waffle.io/openETCS/product-backlog} (free registration for waffle.io needed).
\end{itemize}

\subsection{WP6: Dissemination}

The WP6 meeting was canceled.
 
\subsection{WP5: openETCS Demonstrator}

\begin{itemize}
\item Work on the OBU demonstrator is ongoing.
\item DLR is working on integration of GE hardware.
\item Documentation on how to integrate the GE platform is about to be published on github (awaiting approval from GE management).
\item A meeting between ERSA and DB took place on Wednesday to fix WP5 priorities.
\end{itemize}

\subsection{WP4: Validation \& Verification}
\begin{itemize}
\item GE hardware arrived at DLR labs in Brunswick. A telco between GE and DLR about integration is scheduled for this afternoon.
\item On Tuesday a gotomeeting session on lifecycle linking of documents took place. The results are available at \url{https://github.com/openETCS/internal-assessment/blob/master/Mapping_openETCS_Deliverables_To_requierd_EN50128-2011_Docs.pdf}.
\item D2.3 will be updated to cover scrum development and the lifecycle linking of documents. 
\item A Bitwalker update compatible with baseline 2 messages is about to be released (baseline 3 messages are working already).
\item For the end of next week a two day workshop for integrating the DLR laboratories TIU and the WP3 OBU model is scheduled.
\end{itemize}

\subsection{WP3: Modelling}

\begin{itemize}
\item Level management component is working fine again, a new release of the OBU model fixing 10 issues has been put on github.
\item Problems with driver messages have been solved.
\item WP3 will have a look at the WP7 proposal to work with branches on github.
\item Maintenance of information filter module will be handed from Fraunhofer over to TWT.
\item University of Rostock will deliver their contribution to the ADD (D3.5.3) documentation by the beginning of next week.
\end{itemize}

\subsection{WP7: openETCS Tool Chain}

\begin{itemize}
\item A first process proposal for the master-branch-error-free issue has been described and needs review and discussion (c.f. \url{https://github.com/openETCS/toolchain/issues/498}).
\item CNRS LAAS will take action on the development of a roadmap concept how to convert SCADE Suite artefacts to an open tool chain.
\end{itemize}

\subsection{PMB: Project Management Board}

\begin{itemize}
\item Input to the ITEA project progress report 2015 S1 is due today.
\item An openETCS event to present the project results to interested parties is planned to be held after the final ITEA review in Munich, i.e. at December 17th. Details will follow.
\end{itemize}

\section{Notes}


\begin{itemize}
\item You can find these minutes online at \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/\jobname}. Please, use the issue tracker for findings and corrections within the minutes.
\end{itemize}

\end{document}
