
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\usepackage{booktabs}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}

\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum Meetings\\
Minutes by & Peter Mahlmann (DB Netz AG)\\
When & December 4th, 2015, 9:45 AM -- 11:45 AM\\
Location & Telco and GoToMeeting\newline \url{https://global.gotomeeting.com/meeting/join/493963173}\\
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting Agenda}

\begin{tabular}{lll}
\toprule
\textbf{Slot} &  \textbf{Chair} & \textbf{Work Package} \\
\midrule 
9:45 AM -- 10:15 AM & Peter Mahlmann & Product Backlog Grooming  \\
10:15 AM -- 10:30 AM & Matthieu Poirot & WP5 openETCS Demonstrator \\  
10:30 AM -- 10:45 AM & Marc Behrens & WP4 Validation \& Verification \\
10:45 AM -- 11:00 AM & Bernd Hekele & WP3 Modeling \\
11:00 AM -- 11:15 AM & Michael Jastram & WP7 openETCS Tool Chain \\
11:15 AM -- 11:45 AM & Klaus-R\"udiger Hase & Project Management Board \\
\bottomrule
\end{tabular}

\section{List of Attendees}

\begin{table}[htbp]
    \begin{tabular}{rrr}
    \toprule
    \textbf{Name} & \textbf{Join Time} & \textbf{Leave Time} \\
    \midrule
    Baseliyos Jacob & 10:16 AM & 11:13 AM \\
    Bernd Hekele (DB) & 9:56 AM & 11:13 AM \\
    Silvano Dalzilio & 10:54 AM & 11:08 AM \\
    Hardi Hungar (DLR) & 10:21 AM & 10:46 AM \\
    Ingo Weigelt & 11:07 AM & 11:13 AM \\
    Jens Gerlach & 10:35 AM & 10:42 AM \\
    Jens Gerlach & 10:29 AM & 10:35 AM \\
    Johannes Kastner (ICS) & 10:13 AM & 11:13 AM \\
    Marielle Petit-Doche & 10:23 AM & 11:13 AM \\
    Michael Jastram & 10:50 AM & 11:13 AM \\
    Peter Mahlmann (DB)& 10:11 AM & 11:13 AM \\
    Peyman Farhangi (DB)& 10:19 AM & 11:13 AM \\
    Raphael Faudou (Samares) & 10:17 AM & 11:13 AM \\
    Stefan Karg (LEA) & 10:14 AM & 11:13 AM \\
    Thorsten Schulz (Uni Ro) & 10:42 AM & 11:13 AM \\
    Uwe Steinke (Siemens) & 10:20 AM & 11:13 AM \\
     \bottomrule
    \end{tabular}%
  \label{tab:addlabel}%
\end{table}%




\section{Minutes}

\subsection{Product Backlog Grooming}
\begin{itemize}
\item Meeting has been canceled due to review preparation.
\end{itemize}

\subsection{WP6: Dissemination}
\begin{itemize}
\item Meeting has been canceled due to review preparation.
\end{itemize}

\subsection{WP5 openETCS Demonstrator}
\begin{itemize}
\item DLR is continuing the work on the demonstrator with GE/Alstom hardware.
\end{itemize}

\subsection{WP4 Validation \& Verification}
\begin{itemize}
\item The state of due deliverables has been discussed. This applies to D4.3.1, D4.3.2, D4.3.3, D4.4, and D4.5. It has been agreed that draft versions of these deliverables will be provided to the ITEA reviewers by Wednesday, December 9th.
\end{itemize}

\subsection{WP3 Modeling}
\begin{itemize}
\item In preparation of the ITEA review the fourth and final release of the openETCS OBU model has been made.
\item Deliverables D3.5.4, D3.6.4, D3.7, and D3.8 have been completed and uploaded to the ITEA website in time for the upcoming review meeting.
\item The option of having an onsite meeting in Munich with DB, ERSA, ICS, LEA has been discussed.
\end{itemize}

\subsection{WP7 openETCS Tool Chain}
\begin{itemize}
\item The WP7 presentation for the final ITEA review has been completed and is ready for upload to the ITEA website.
\item The openETCS tool chain homepage will be updated and a final release of the tool chain is in preparation.
\item The demonstration of the tool chain at the ITEA review has been discussed. Partners were asked to provide input in issue 512 (\url{https://github.com/openETCS/toolchain/issues/512})
\end{itemize}

\subsection{Project Management Board}
\begin{itemize}
\item Partners have been asked for contributions to the openETCS Unconference on December 17th, cf. \url{https://github.com/openETCS/17Dec15UnConference}.
\end{itemize}


\section{General Remarks}

\begin{itemize}
\item Please find these minutes online at \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/\jobname.pdf}. Please, use the github issue tracker for findings and corrections within the minutes.
\end{itemize}

\end{document}
