
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
%Organised by &Klaus-R\"udiger Hase\\
Organised by &Bernd Hekele\\
Minutes by & Bernd Hekele\\
When & November, 14th, 2014, 10:00 - 11:15\\
Location & Telco and Goto-Meeting\\
%9:30-10:00 and 
%\hline
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
10:15 - 10:30 & Nicolas van Landeghem & WP5: Demonstration \\\hline  
10:30 - 11:00 & Jan Welte & WP4: Verification \& Validation \\\hline  
%10:30 - 11:00 & Marc Behrens & WP4: Verification \& Validation \\\hline  
10:45 - 11:00 & Fausto Cochetti & WP3: Modelling \\\hline  
%10:45 - 11:00 & Peter Mahlmann & WP3: Modelling \\\hline  
11:00 - 11:10 & Michael Jastram & WP7: Toolchain \\\hline
%11:15 - 11:30 & Baseliyos Jacob & WP2: API Requirements \\\hline  
11:10 - 11:15 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
%11:15 - 11:45 & Bernd Hekele & PMB: Project Management Board \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} \\\hline
% Name                  6   5   4   3   7   P
%Alexander Nitsch     &   & x & x & x & x & x \\\hline  
%Alexander Stante     &   &   &   &   & x &   \\\hline 
%Baseliyos Jacob      &   &   & x & x & x &   \\\hline 
%Bernd Gonska         &   &   & x &   &   &   \\\hline
Bernd Hekele         & x & x & x & x & x & x \\\hline
Benjamin Beichler    &   &   & x & x & x &   \\\hline
%Cecile Braunstein    &   &   & x & x & x &   \\\hline
%Christian Giraud     &   &   &   &   &   &   \\\hline
Christian Stahl      &   &   & x & x &   &   \\\hline
%David Mentre         &   &   &   &   &   &   \\\hline
Fausto Cochetti      &   &   & x & x & x &   \\\hline
Hardi Hungar         &   &   & x &   & x &   \\\hline
%Huu-Nghia Nguyen     & x &   & x & x & x &   \\\hline
%Ion I. Uribe         &   &   & x &   &   &   \\\hline
Izaskun de la Torre  & x & x & x & x & x &   \\\hline
Jan Welte            & x & x & x & x & x & x \\\hline
Jaime Paniagua       &   &   &   & x & x &   \\\hline
%Jakob Gaertner       &   &   &   & x & x &   \\\hline
Jan Welvaarts        &   &   &   & x &   &   \\\hline
Jens Gerlach         & x & x & x & x &   &   \\\hline
%Jonas Helming        &   &   &   &   &   &   \\\hline
%Jos Holtzer          & x &   &   &   &   &   \\\hline
%Karsten Falk         &   &   & x & x & x & x \\\hline
Klaus-R\"udiger Hase & x & x & x & x & x & x \\\hline
%Laurent Ferier       &   &   &   & x & x & x \\\hline
%Lukasz Fronc         &   &   &   &   & x & x \\\hline
%Marc Behrens         &   &   & x & x & x & x \\\hline
Marielle Petit-Doche &   &   & x & x & x & x \\\hline
%Mathilde Arnaud      &   &   &   &   &   &   \\\hline
Matthieu Perin       &   &   &   & x & x & x \\\hline
Michael Jastram      &   &   &   & x & x & x \\\hline
Nicolas van Landeghem&   & x & x &   &   &   \\\hline
%Peter Mahlmann       &   & x & x & x & x & x \\\hline
%Peyman Farhangi      &   & x & x & x & x & x \\\hline
Pierre-Yves Le Morvan&   & x & x & x &   & x \\\hline
%Silvano dal Zilio    &   &   & x & x & x &  \\\hline
Stefan Rieger        & x & x & x & x & x & x \\\hline
Uwe Steinke          &   & x & x & x & x & x \\\hline
Veronique Gontier    &   & x & x & x & x & x \\\hline
Vincent Nuhaan       &   &   &   & x &   &   \\\hline
% Name                  6   5   4   3   7   P  \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{WP6: Dissemination}
\begin{itemize}
\item Dissemination Plan Update\\
The next update of the dissemination plan is due. Deadline for contributions is December 20th. You can find the plan here:
\url{https://github.com/openETCS/dissemination-management/tree/master/D6.4_Updated_Exploitation_Plan_and_Standardisation_Report}.

\end{itemize}

\subsection{WP5: Demonstration}
\begin{itemize}
\item Activities\\
ERSA is investigating the use of CORBA for the demonstrator with the target to separate EVC Software, Base-Software and Test-Environment.
ERSA is also looking into an implementation of a test environment targeting to implement the Scade test stimuli.

\end{itemize}

\subsection{WP4: Validation \& Verification}
\begin{itemize}
\item Activities
The second grooming session on WP4 user stories took place. Results are visible in the WP4 backlog:
\url{https://waffle.io/openETCS/validation}. The feedback on the chosen priority of the user stories is expected.
\end{itemize}

\subsection{WP3: Modelling}
\begin{itemize}

\item WP3 Activities\\
The workshop-results of the first convergence workshop(Munich, November 3rd to November 7th) have been discussed.
As a result and as part of the work writing of the ADD document (Architecture and Design Document) is being driven with priority.
The work is organised in working groups.

\item Scade Training\\
A doodle \url{http://doodle.com/6t38wcpkbrpi6yb5} is in use for collecting inputs for the upcoming scade training. In addition to a session on Scade Design (3 days) we are planning for a session on Scade verification. 
\end{itemize}

\subsection{WP7: Toolchain}

\begin{itemize}
\item Activities
Small contributions due to holidays. The actual sprint will be extended.
\end{itemize}

\subsection{PMB: Project Management Board}
\begin{itemize}

\item Scrum Of Scrum Proposal\\
Grooming of the openETCS master backlog is scheduled for next Friday (as an special event in the PMB meeting)
\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/Minute_20141114.pdf}. Please, use the issue tracker for findings with the minutes.

\end{itemize}

\end{document}
