
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
%Organised by &Klaus-R\"udiger Hase\\
Organised by &Bernd Hekele\\
Minutes by & Bernd Hekele\\
When & September, 19th, 2014, 10:15 - 11:45\\
Location & Telco and Goto-Meeting\\
%9:30-10:00 and 
%\hline
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
10:15 - 10:30 & Nicolas van Landeghem & WP5: Demonstration \\\hline  
10:30 - 11:00 & Marc Behrens & WP4: Verification \& Validation \\\hline  
10:45 - 11:00 & Fausto Cochetti & WP3: Modelling \\\hline  
%10:45 - 11:00 & Peter Mahlmann & WP3: Modelling \\\hline  
11:00 - 11:15 & Michael Jastram & WP7: Toolchain \\\hline
%11:15 - 11:30 & Baseliyos Jacob & WP2: API Requirements \\\hline  
%11:15 - 11:45 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
11:15 - 11:45 & Bernd Hekele & PMB: Project Management Board \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} \\\hline
% Name                  6   5   4   3   7   P
Alexander Nitsch     & x & x & x & x & x & x \\\hline  
%Alexander Stante     &   &   &   &   & x &   \\\hline 
Baseliyos Jacob      & x &   & x & x & x &   \\\hline 
%Bernd Gonska         &   &   & x &   &   &   \\\hline
Bernd Hekele         & x & x & x & x & x & x \\\hline
%Benjamin Beichler    &   &   & x & x & x &   \\\hline
Cecile Braunstein    &   &   & x & x & x &   \\\hline
%Christian Giraud     &   &   &   &   &   &   \\\hline
%Christian Stahl      &   &   &   & x &   &   \\\hline
%David Mentre         &   &   &   &   &   &   \\\hline
Fausto Cochetti      &   &   &   & x & x &   \\\hline
%Hardi Hungar         &   &   &   &   & x &   \\\hline
%Huu-Nghia Nguyen     & x &   & x & x & x &   \\\hline
%Ion I. Uribe         &   &   & x &   &   &   \\\hline
Izaskun de la Torre  & x & x & x & x & x &   \\\hline
Jan Welte            &   &   &   & x & x & x \\\hline
Jaime Paniagua       &   &   & x &   &   &   \\\hline
%Jakob Gaertner       &   &   &   & x & x &   \\\hline
Jan Welvaarts        &   & x & x & x &   &   \\\hline
%Jens Gerlach         & x & x & x & x &   &   \\\hline
%Jonas Helming        &   &   &   &   &   &   \\\hline
%Jos Holtzer          & x &   &   &   &   &   \\\hline
%Karsten Falk         &   &   & x & x &   &   \\\hline
%Klaus-R\"udiger Hase &  & x & x & x & x & x \\\hline
%Laurent Ferier       &   &   &   & x & x & x \\\hline
%Lukasz Fronc         &   &   &   &   & x & x \\\hline
Marc Behrens         &   & x & x & x & x & x \\\hline
%Marielle Petit-Doche & x &   & x & x & x & x \\\hline
%Mathilde Arnaud      &   &   &   &   &   &   \\\hline
Matthieu Perin       &   &   & x & x & x & x \\\hline
Michael Jastram      & x & x & x & x & x & x \\\hline
Nicolas van Landeghem&   & x & x & x &   &   \\\hline
%Peter Mahlmann       &   & x & x & x & x & x \\\hline
Peyman Farhangi      &   &   &   & x &   &   \\\hline
Pierre-Yves Le Morvan&   & x & x & x &   & x \\\hline
%Silvano dal Zilio    &   &   & x & x & x &  \\\hline
Stefan Rieger        & x & x & x & x & x & x \\\hline
Uwe Steinke          & x & x & x & x & x & x \\\hline
Veronique Gontier    &   & x & x & x & x & x \\\hline
%Vincent Nuhaan       &   &   &   & x &   &   \\\hline
% Name                  6   5   4   3   7   P  \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{WP6: Dissemination}
\begin{itemize}
\item openETCS@Innotrans\\
The openETCS@Innotrans event is well prepared. No open issues. 

\item openETCS Publications\\
Please, report your openETCS publications for the upcoming report.
Work on the dissemination plan is proceeding. Alexander has put the update on the dissemination repository:
\url{https://github.com/openETCS/Dissemination/tree/master/D6.3_Updated_Dissemination_Plan_and_Report}.\\
Target is to complete this update on schedule.

\end{itemize}

\subsection{WP5: Demonstration}
\begin{itemize}
\item 5.1: Review participation still not sufficient\\
The coverage of reviews of WP5 contributions by partners is still not sufficient. Please, make your contribution.
\item Demonstrator Training\\
ERSA is preparing a 2 day training session for the demonstrator. Please, make use of this doodle for confirming your participation \url{http://doodle.com/64mma694b4u4ra7c}.\\
The training is planned to take place at Strassbourg October 7th and 8th.
\item API Document Review\\
ERSA started with the review of the new API document.

\end{itemize}

\subsection{WP4: Validation \& Verification}
\begin{itemize}

\item Activities\\
Activities have been started in order to define the procedure for closing a design step \url{https://github.com/openETCS/validation/wiki/How-to-close-a-design-step} \\ and on Synchronization on the openETCS Coding Rules (part of D4.2.2).
\end{itemize}

\subsection{WP3: Modelling}
\begin{itemize}

\item WP3 workshop\\
The minutes and action plan resulting from the Brussels workshop are currently under review. The results can be found here \url{https://github.com/openETCS/SRS-Analysis/tree/master/Meetings/Team-meeting_Brussels_2014-09-09}.

Alstom France partners have participated in a Scade training.

The next workshop is planned to take place end of October.

First activities to work on the architecture are being started.

\end{itemize}

\subsection{WP7: Toolchain}

\begin{itemize}
\item Planning of the WP7 team meeting is progressing. 
\item The Tuesday team meeting is being reactivated.
\item First WP7 product backlog is available in the WP7 wiki.
\end{itemize}

\subsection{PMB: Project Management Board}
\begin{itemize}

\item No issues this meeting.

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/Minute_20140919.pdf}. Please, use the issue tracker for findings with the minutes.

\end{itemize}

\end{document}
