
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\usepackage{booktabs}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}

\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum Meetings\\
Minutes by & Peter Mahlmann (DB Netz AG)\\
When & September 11th, 2015, 9:45 AM -- 11:45 AM\\
Location & Telco and GoToMeeting\newline \url{https://global.gotomeeting.com/meeting/join/493963173}\\
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting Agenda}

\begin{tabular}{lll}
\toprule
\textbf{Slot} &  \textbf{Chair} & \textbf{Work Package} \\
\midrule 
9:45 AM -- 10:15 AM & Peter Mahlmann & Product Backlog Grooming  \\
10:15 AM -- 10:30 AM & Matthieu Poirot & WP5 openETCS Demonstrator \\  
10:30 AM -- 10:45 AM & Marc Behrens & WP4 Validation \& Verification \\
10:45 AM -- 11:00 AM & Bernd Hekele & WP3 Modeling \\
11:00 AM -- 11:15 AM & Michael Jastram  & WP7 openETCS Tool Chain \\
11:15 AM -- 11:45 AM & Klaus-R\"udiger Hase & Project Management Board \\
\bottomrule
\end{tabular}

\section{List of Attendees}

\begin{table}[htbp]
    \begin{tabular}{rrr}
    \toprule
    \textbf{Name} & \textbf{Join Time} & \textbf{Leave Time} \\
    \midrule
    Ingo Weigelt & 10:09 AM & 11:05 AM \\
    Jan Welte & 10:30 AM & 11:05 AM \\
    Johannes Kastner (ICS) & 9:57 AM & 11:04 AM \\
    Marc Behrens & 10:10 AM & 11:04 AM \\
    Mercuri, Dario (GE Transportation) & 9:39 AM & 10:32 AM \\
    Klaus-R\"udiger Hase (DB) & 9:50 AM & 11:12 AM \\
    Peter Mahlmann (DB) & 9:35 AM & 11:12 AM \\
    Stefan Karg (LEA Railergy) & 10:02 AM & 11:04 AM \\
    Uwe Steinke (Siemens) & 9:45 AM & 11:05 AM \\
    \bottomrule
    \end{tabular}%
  \label{tab:addlabel}%
\end{table}%




\section{Minutes}

\subsection{Product Backlog Grooming}
\begin{itemize}
\item The product backlog is available via 
\url{https://github.com/openETCS/product-backlog}. 
\item For the results of the grooming session we refer to the waffle.io scrum board available via \url{https://waffle.io/openETCS/product-backlog} (free GitHub account needed).
\end{itemize}

\subsection{WP6: Dissemination}
\begin{itemize}
\item The WP6 meeting was canceled, the WP6 slot has been used for product backlog grooming.
\end{itemize}

\subsection{WP5 openETCS Demonstrator}
\begin{itemize}
\item The integration of GE hardware is stalling due to holidays and missing software. In particular compiler settings for code generation are needed from GE. 
\item ERSA is still working the wrapper respectively glue code  to make the openETCS OBU model work with the ERSA environment.
\end{itemize}

\subsection{WP4 Validation \& Verification}
\begin{itemize}
\item A telco on V\&V results took place this week. The very good exchange between developers and the V\&V team on the findings is mentioned. First actions on the the findings of the V\&V team have been taken already in case of the CheckBGConsistency component.
\item AEbt and All4tec are going to write the internal assessment report. As a first step, the report will report on the CENELEC conformance of the planning documents.
\item The team of DB subcontractor ICS has been asked to join the test plan meetings on Thursdays to align V\&V activities between the various partners.
\end{itemize}

\subsection{WP3 Modeling}
\begin{itemize}
\item The focus of the WP3 team between creating a simulation environment (to allow demonstration and visualization) model development (i.e. implementing additional functionality), and documentation has been discussed.
\end{itemize}

\subsection{WP7 openETCS Tool Chain}
\begin{itemize}
\item The WP7 meeting was canceld due to GoToMeeting issues.
\end{itemize}

\subsection{Project Management Board}
\begin{itemize}
\item No PMB meeting was required this week.
\end{itemize}


\section{General Remarks}

\begin{itemize}
\item Please find these minutes online at \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/\jobname.pdf}. Please, use the github issue tracker for findings and corrections within the minutes.
\item Participation in todays meeting was relatively low due to technical issues with GoToMeeting, i.e. several partners were not able to join the meeting due to server issues.
\end{itemize}

\end{document}
