
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
Organised by & Bernd Hekele\\
Minutes by & Bernd Hekele\\
When & June 6th, 2014, 9:30 - 12:00\\
Location & Telco and Goto-Meeting\\
%9:30-10:00 and 
%\hline
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
%09:30 - 10:00 & Bernd Hekele & WP3: Modelling (team activities)\\\hline
%10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
10:15 - 10:30 & Nicolas van Landeghem & WP5: Demonstration \\\hline  
10:30 - 10:45 & Marc Behrens & WP4: Verification \& Validation \\\hline  
10:45 - 11:00 & Fausto Cocchetti & WP3: Modelling \\\hline  
11:00 - 11:15 & Michael Jastram & WP7: Toolchain \\\hline
%11:15 - 11:30 & Baseliyos Jacob & WP2: API Requirements \\\hline  
11:15 - 11:30 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
11:15 - 12:00 & Klaus-R\"udiger Hase & ITEA Review Preparation \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant} &  \textbf{WP3} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} & \textbf{ITEA} \\\hline
% Name                  3    6   5   4   3   7   P   I
%Alessandro Cimatti    &   &   &   &   &   &   &   &   \\\hline 
%Alexander Nitsch      & x &   &   & x & x & x & x & x \\\hline  
Alexander Stante      &   &   &   &   &   & x &   &   \\\hline 
Baseliyos Jacob       &   &   & x & x & x & x & x & x \\\hline 
%Benjamin Beichler     &   &   &   &   &   &   &   &   \\\hline 
Bernd Hekele          &   &   & x & x & x & x & x & x \\\hline
Cecile Braunstein     &   &   &   & x & x & x &   &   \\\hline
%Christian Giraud      &   &   &   &   &   &   &   &   \\\hline
%Christian Stahl       & x &   & x & x & x &   &   &   \\\hline
%David Mentre          &   &   &   &   &   &   &   &   \\\hline
Fausto Cochetti       &   &   &   & x & x & x &   &   \\\hline
%Giovanni Trotta       &   &   &   &   &   &   &   &   \\\hline
%Giovanni Zanelli      &   &   &   &   &   & x & x & x \\\hline
Hardi Hungar          &   &   &   & x &   &   &   &   \\\hline
%Huu-Nghia Nguyen      &   &   &   &   &   &   &   &   \\\hline
Izaskun de la Torre   &   &   &   &   & x & x &   &   \\\hline
Jan Welte             &   &   & x & x & x & x & x & x \\\hline
Jan Welvaarts         &   &   &   &   & x &   &   &   \\\hline
%Jens Gerlach          &   &   &   & x &   &   &   &   \\\hline
%Jonas Helming         &   &   &   &   &   &   &   &   \\\hline
Klaus-R\"udiger Hase  &   &   & x & x & x & x & x & x \\\hline
Laurent Ferier        &   &   &   &   & x & x & x & x \\\hline
%Lukasz Fronc          &   &   &   &   &   &   &   &   \\\hline
Marc Behrens          &   &   & x & x & x & x & x & x \\\hline
Marielle Petit-Doche  &   &   &   & x & x & x & x & x \\\hline
%Mathilde Arnaud       &   &   &   &   &   &   &   &   \\\hline
%Matthieu Perin        &   &   &   &   &   & x &   &   \\\hline
Michael Jastram       &   &   &   &   & x & x & x & x \\\hline
Nicolas van Landeghem &   &   & x & x &   &   &   &   \\\hline
Peter Mahlmann        &   &   & x & x & x & x & x & x \\\hline
%Peyman Farhangi       &   &   & x & x & x & x & x & x \\\hline
%Silvano dal Zilio     &   &   &   &   &   &   &   &   \\\hline
Stefan Rieger         &   &   & x & x & x & x & x & x \\\hline
Uwe Steinke           &   &   & x & x & x & x & x & x \\\hline
%Vincent Nuhaan        &   &   & x & x &   &   &   &   
% Name                  3    6   5   4   3   7   P  \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{WP6: Dissemination}

No meeting this week.

\subsection{WP5: Demonstration}
\begin{itemize}
\item Update on Activities\\
The bi-weekly synch meeting ERSA and DB was held the first time. 

The functional specification has been updated. The review is plaaned under this issue: \url{https://github.com/openETCS/demonstrator/issues/8}. Review period is 2 weeks.

An update of the ERSA demonstrator following the openETCS architecture has been released. 

\end{itemize}


\subsection{WP4: Validation \& Verification}
\begin{itemize}
\item actual event\\
The Braunschweig test training has been conducted this week. Results are available on Github.

\item Internal Assessment\\
The follow up to the internal assessment meeting is scheduled for 12.June, 13:30 - 15:00 in Munich. It is planned to take place after the Itea Review meeting.

\end{itemize}

\subsection{WP3: Modelling}

\begin{itemize}
\item Upcoming Events\\
The results of the Brussel Modelling workshop are available here: \url{https://github.com/openETCS/modeling/tree/master/meetings/Team-Meeting_Brussels-2014-05-26}. The meeting minutes have been distributed for review.

The next \textbf{WP3 modelling workshop} is  scheduled to take place on June  24th - 25th. in Munich.  

For working on the API a team has started with participation of ERSA, Alstom and MERCE. A weekly meeting is planned to be conducted on the topic. The activity is maanaged in the following folder:\url{https://github.com/openETCS/modeling/tree/master/API}. Minutes os the first meeting are currently under review.

\item each partner: impediments, progress\\

\item a.o.b.\\

\end{itemize}

\subsection{WP7: Toolchain}

The backlog and the resource plan have been updated.

\subsection{WP2: Requirements}

No meeting this week.

\subsection{PMB: Project Management Board}
\begin{itemize}
\item PCC Meeting agenda has been updated: \url{https://github.com/openETCS/governance/wiki/%7C-M:-2014.06.11-openETCS-7th-PCC-AGENDA}
\item Proposal for an openETCS Product Backlog
\item Preparation of the ITEA Review Meeting\\
The presentations are uploaded to ITEA.

\end{itemize}

\section{Notes}
\begin{itemize}
\item Scrum agenda to be changed again\\
The agenda to the Friday meetings will be updated.

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/Minute_20140606.pdf}. Please, use the issue tracker for findings with the minutes.

Starting with 23rd of May the minutes will be provided in one document for the whole meeting series of a day.

\end{itemize}

\end{document}
