
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
Organised by &Klaus-R\"udiger Hase\\
Minutes by & Bernd Hekele\\
When & September, 5th, 2014, 10:15 - 11:45\\
Location & Telco and Goto-Meeting\\
%9:30-10:00 and 
%\hline
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
%10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
10:15 - 10:30 & Nicolas van Landeghem & WP5: Demonstration \\\hline  
10:30 - 11:00 & Marc Behrens & WP4: Verification \& Validation \\\hline  
10:45 - 11:00 & Fausto Cochetti & WP3: Modelling \\\hline  
%10:45 - 11:00 & Peter Mahlmann & WP3: Modelling \\\hline  
11:00 - 11:15 & Michael Jastram & WP7: Toolchain \\\hline
%11:15 - 11:30 & Baseliyos Jacob & WP2: API Requirements \\\hline  
11:15 - 11:45 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
%11:15 - 11:45 & Bernd Hekele & PMB: Project Management Board \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} \\\hline
% Name                  6   5   4   3   7   P
%Alexander Nitsch     & x & x & x & x & x & x \\\hline  
%Alexander Stante     &   &   &   &   & x &   \\\hline 
%Baseliyos Jacob      &   &   &   &  &  & x \\\hline 
%Bernd Gonska         &   &   & x &   &   &   \\\hline
Bernd Hekele         &   & x & x & x & x & x \\\hline
%Benjamin Beichler    &  &   & x & x & x &  \\\hline
%Cecile Braunstein    &   &   & x & x & x &   \\\hline
%Christian Giraud     &   &   &   &   &   &   \\\hline
%Christian Stahl      &   &   &   & x &   &   \\\hline
%David Mentre         &   &   &   &   &   &   \\\hline
Fausto Cochetti      &   &   & x & x & x &   \\\hline
Hardi Hungar         &   &   & x &   &   &   \\\hline
%Jos Holtzer         & x &   &   &   &   &   \\\hline
%Huu-Nghia Nguyen     & x &   & x & x & x &   \\\hline
Ion I. Uribe         &   &   & x &   &   &   \\\hline
%Izaskun de la Torre  &   &   &   & x & x &   \\\hline
%Jan Welte            &   &  & x & x & x & x \\\hline
Jakob Gaertner       &   &   & x & x & x &   \\\hline
Jan Welvaarts        &  &  &   & x  &   &   \\\hline
Jaime Paniagua       &  & x & x & x & x &    \\\hline
%Jens Gerlach         & x & x & x & x &   &   \\\hline
%Jonas Helming        &   &   &   &   &   &   \\\hline
Karsten Falk         &  &   & x & x & x &   \\\hline
Klaus-R\"udiger Hase &  & x & x & x & x & x \\\hline
%Laurent Ferier       &   &   &   & x & x & x \\\hline
%Lukasz Fronc         &   &   &   &   & x & x \\\hline
Marc Behrens         &   & x & x & x & x & x \\\hline
Marielle Petit-Doche &   & x & x & x & x & x \\\hline
%Mathilde Arnaud      &   &   &   &   &   &   \\\hline
Matthieu Perin       &   &   & x & x & x & x \\\hline
Michael Jastram      &   &   &   &   & x & x \\\hline
Nicolas van Landeghem&   & x &   &   &   &   \\\hline
Peter Mahlmann       &   & x & x & x & x & x \\\hline
Peyman Farhangi      &   &   &   & x & x & x \\\hline
%Pierre-Yves Le Morvan&   &  & x & x & x & x \\\hline
%Silvano dal Zilio    &   &   & x & x & x &  \\\hline
%Stefan Rieger        & x & x & x & x & x & x \\\hline
Uwe Steinke          &   & x & x & x & x & x \\\hline
Veronique Gontier    &   & x & x & x & x & x \\\hline
Vincent Nuhaan       &   &   &   & x &   &   \\\hline
% Name                  6   5   4   3   7   P  \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{WP5: Demonstration}
\begin{itemize}
\item Test Workshop\\
WP5 is planning to organize a test workshop. Currently discussed is the meeting to be held in the beginning of October. The workshop is planned for gioving an introduction in the ERSA demonstrator and its handling. A ddodle query is forseen for collecting the requirements.

\end{itemize}

\subsection{WP4: Validation \& Verification}
\begin{itemize}
\item SQS has provided a test-model forthe Roll-Away-Protection function: \url{https://github.com/openETCS/validation/tree/master/VnVUserStories/VnVUserStorySQS/05-Work/Roll%20Away%20Protection%20Model/PAP-001-rtt-model-template-sysmlSQS}.
\item The follow-up meeting of the internal assessment with AEbt has been scheduled for September 16th in Braunschweig, Germany. Goal of the workshop is to discuss CENELEC compliance of the openETCS process. Participants are asked to use the following doodle for planning: \url{http://doodle.com/32avv8ff5igy7mr9}.\\
The last week Wednesday the Telco On Testing took place finishing sprint 13 by checking the status of all issues and transferring all ongoing activities in sprint 14.

\end{itemize}

\subsection{WP3: Modelling}
\begin{itemize}
\item The agenda for the Brussels WP3 meeting has been discussed.\\
The updated version will be made available in the SRS-Analysis repository: \url{https://github.com/openETCS/SRS-Analysis/blob/master/Meetings/Team-meeting_Brussels_2014-09-09/Open-ETCS-WP3-09-10-sept.pptx}
\end{itemize}

\subsection{WP7: Toolchain}

\begin{itemize}
\item Sprint 18 has been extended and will end on September 19.
\item The test plan has been reviewed and a revised version will be available soon.
\item The problems concerning the target platform and integration of Scade libraries will be solved within the next weeks.
\end{itemize}

\subsection{PMB: Project Management Board}
\begin{itemize}
\item Scrum Of Scrum
Peter has provided and distributed a first version of the backlog (based on xls). \\
\item Deliverables\\
The openETCS ITEA progress report is currently under review.

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/Minute_20140905.pdf}. Please, use the issue tracker for findings with the minutes.

\end{itemize}

\end{document}
