
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
%Organised by &Klaus-R\"udiger Hase\\
Organised by &Bernd Hekele\\
Minutes by & Bernd Hekele\\
When & October, 17th, 2014, 10:15 - 11:45\\
Location & Telco and Goto-Meeting\\
%9:30-10:00 and 
%\hline
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
%10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
10:15 - 10:30 & Nicolas van Landeghem & WP5: Demonstration \\\hline  
10:30 - 11:00 & Marc Behrens & WP4: Verification \& Validation \\\hline  
10:45 - 11:00 & Fausto Cochetti & WP3: Modelling \\\hline  
%10:45 - 11:00 & Peter Mahlmann & WP3: Modelling \\\hline  
11:00 - 11:15 & Michael Jastram & WP7: Toolchain \\\hline
%11:15 - 11:30 & Baseliyos Jacob & WP2: API Requirements \\\hline  
11:15 - 11:45 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
%11:15 - 11:45 & Bernd Hekele & PMB: Project Management Board \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} \\\hline
% Name                  6   5   4   3   7   P
Alexander Nitsch     &   & x & x & x & x & x \\\hline  
%Alexander Stante     &   &   &   &   & x &   \\\hline 
%Baseliyos Jacob      &   &   & x & x & x &   \\\hline 
%Bernd Gonska         &   &   & x &   &   &   \\\hline
Bernd Hekele         &   & x & x & x & x & x \\\hline
%Benjamin Beichler    &   &   & x & x & x &   \\\hline
Cecile Braunstein    &   &   & x & x & x &   \\\hline
%Christian Giraud     &   &   &   &   &   &   \\\hline
Christian Stahl      &   &   & x & x &   &   \\\hline
%David Mentre         &   &   &   &   &   &   \\\hline
Fausto Cochetti      &   &   & x & x & x &   \\\hline
%Hardi Hungar         &   &   &   &   & x &   \\\hline
%Huu-Nghia Nguyen     & x &   & x & x & x &   \\\hline
%Ion I. Uribe         &   &   & x &   &   &   \\\hline
Izaskun de la Torre  &   &   & x & x & x &   \\\hline
%Jan Welte            &   &   &   & x & x & x \\\hline
Jaime Paniagua       &   &   &   & x &   &   \\\hline
%Jakob Gaertner       &   &   &   & x & x &   \\\hline
Jan Welvaarts        &   & x & x & x &   &   \\\hline
%Jens Gerlach         & x & x & x & x &   &   \\\hline
%Jonas Helming        &   &   &   &   &   &   \\\hline
%Jos Holtzer          & x &   &   &   &   &   \\\hline
Karsten Falk         &   &   & x & x & x & x \\\hline
Klaus-R\"udiger Hase &  & x &   &   &   & x \\\hline
%Laurent Ferier       &   &   &   & x & x & x \\\hline
%Lukasz Fronc         &   &   &   &   & x & x \\\hline
Marc Behrens         &   &   & x & x & x & x \\\hline
Marielle Petit-Doche &   &   & x & x & x & x \\\hline
%Mathilde Arnaud      &   &   &   &   &   &   \\\hline
Matthieu Perin       &   &   & x & x & x & x \\\hline
Michael Jastram      &   & x & x & x & x & x \\\hline
Nicolas van Landeghem&   & x &   &   &   &   \\\hline
%Peter Mahlmann       &   & x & x & x & x & x \\\hline
Peyman Farhangi      &   & x & x & x & x & x \\\hline
Pierre-Yves Le Morvan&   & x & x & x &   & x \\\hline
%Silvano dal Zilio    &   &   & x & x & x &  \\\hline
Stefan Rieger        &   &   & x & x & x & x \\\hline
Uwe Steinke          &   & x & x & x & x & x \\\hline
%Veronique Gontier    &   & x & x & x & x & x \\\hline
%Vincent Nuhaan       &   &   &   & x &   &   \\\hline
% Name                  6   5   4   3   7   P  \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{WP6: Dissemination}
\begin{itemize}
\item No meeting held this week.

\end{itemize}

\subsection{WP5: Demonstration}
\begin{itemize}
\item Activities\\
ERSA reviewed the WP3 Architecture.

The WP5 Grooming session is in preparation. Please, use this doodle if you want to join the event:
\url{http://doodle.com/2xwy7ugbdgym739n#table}.

\end{itemize}

\subsection{WP4: Validation \& Verification}
\begin{itemize}

\item Activities\\
The scenario for the verification of the train positioning documents has been presented. The scenario will be used for the closing session (Braunschweig, 28th and 29th of October.)

The WP4 Grooming session is in preparation. Please, use this doodle if you want to join the event:
\url{http://doodle.com/3hzy3rhnkdai82t8}.

\end{itemize}

\subsection{WP3: Modelling}
\begin{itemize}

\item WP3 Activities\\
The WP3 archtiecture convergence workshop is scheduled for 3rd of November to 11 of November. The workshop is planned to take place in Munich.

The Alstom Database paper has been made available for review. \url{https://github.com/openETCS/SRS-Analysis/issues/47}.

The WP3 Grooming session is in preparation. Please, use this doodle if you want to join the event:
\url{http://doodle.com/5mgp6qh8wgie8pbs}

\end{itemize}

\subsection{WP7: Toolchain}

\begin{itemize}
\item WP7 team meeting held in Munich. Results of the meeting are documented in the wiki:\url{https://github.com/openETCS/toolchain/wiki/WP7-Workshop-Fall-2014}. 
\item openETCS Eclipse Basis.\\
We propose to switch to the openETCS Luna version as soon as possible. A tool release will be prepared.

\end{itemize}

\subsection{PMB: Project Management Board}
\begin{itemize}

\item ITEA board member meeting in Munich.\\
 Klaus-R\"udiger reported on the visit of the ITEA CEO, Prof. Haggenm\"uller and Dr. Stegemann,  at DB V\"olckerstr on Oct 15. It was agreed to  follow-up on some action items:\\
\begin{itemize}
\item French Cluster Leadership to become active (extension of the project)
\item Review of Objectives and Results expected by WP3 leadership
\item Report required to explain the concept of what to be expected (API, Formal Approach, OBU Software, Simulator Software, proof of concept)
\item Final Project  review to be planned for December 2015.
\item ITEA expects to see the TC-Sim loaded with openETCS software.
\end{itemize}

\item Scrum Of Scrum Proposal\\
Karsten presented the ScrumOfScrum process proposal \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/Attachments/4-3_DLR_WP7_scrum_of_scrum_munich_141015.pdf}. The same proposal was discussed at the WP7 workshop. Some details need clarification before implementing the proposal. Peter will follow-up on it.

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/Minute_20141017.pdf}. Please, use the issue tracker for findings with the minutes.

\end{itemize}

\end{document}
