
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
%Organised by &Klaus-R\"udiger Hase\\
Organised by &Bernd Hekele\\
Minutes by & Bernd Hekele\\
When & December, 12th, 2014, 10:00 - 12:00\\
Location & Telco and Goto-Meeting\\
%9:30-10:00 and 
%\hline
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
10:15 - 10:30 & Nicolas van Landeghem & WP5: Demonstration \\\hline  
10:30 - 11:00 & Jan Welte & WP4: Verification \& Validation \\\hline  
%10:30 - 11:00 & Marc Behrens & WP4: Verification \& Validation \\\hline  
10:45 - 11:00 & Fausto Cochetti & WP3: Modelling \\\hline  
%10:45 - 11:00 & Peter Mahlmann & WP3: Modelling \\\hline  
%10:45 - 11:00 & Bernd Hekele & WP3: Modelling \\\hline  
11:00 - 11:15 & Michael Jastram & WP7: Toolchain \\\hline
%11:15 - 11:30 & Baseliyos Jacob & WP2: API Requirements \\\hline  
11:15 - 12:00 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
%11:15 - 11:45 & Bernd Hekele & PMB: Project Management Board \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} \\\hline
% Name                  6   5   4   3   7   P
%Alexander Nitsch     &   &   &   &   &   &   \\\hline  
%Alexander Stante     &   &   &   &   & x & x \\\hline 
Baseliyos Jacob      &   &   & x & x & x & x \\\hline 
%Bernd Gonska         &   &   & x &   &   &   \\\hline
Bernd Hekele         & x & x & x & x & x & x \\\hline
Benjamin Beichler    &   &   & x & x &   &   \\\hline
Cecile Braunstein    &   & x & x & x & x &   \\\hline
%Christian Giraud     &   &   &   &   &   &   \\\hline
Christian Stahl      &   &   &   & x &   &   \\\hline
%David Mentre         &   &   &   &   &   &   \\\hline
Fausto Cochetti      &   & x & x & x & x &   \\\hline
%Hardi Hungar         &   &   & x &   & x &   \\\hline
%Huu-Nghia Nguyen     & x &   & x & x & x &   \\\hline
%Ion I. Uribe         &   &   & x &   &   &   \\\hline
Izaskun de la Torre  & x & x & x & x & x &   \\\hline
Jan Welte            & x & x & x & x & x & x \\\hline
Jaime Paniagua       &   &   &   & x &   &   \\\hline
%Jakob Gaertner       &   &   &   & x & x &   \\\hline
Jan Welvaarts        &   & x & x & x &   &   \\\hline
Jens Gerlach         &   & x & x & x &   &   \\\hline
%Jonas Helming        &   &   &   &   &   &   \\\hline
%Jos Holtzer          & x &   &   &   &   &   \\\hline
%Karsten Falk         &   &   & x & x & x & x \\\hline
Klaus-R\"udiger Hase &   & x & x & x & x & x \\\hline
%Laurent Ferier       &   &   &   & x & x & x \\\hline
%Lukasz Fronc         &   &   &   &   & x & x \\\hline
%Marc Behrens         &   &   & x & x & x & x \\\hline
%Marielle Petit-Doche &   &   & x & x & x & x \\\hline
%Mathilde Arnaud      &   &   &   &   &   &   \\\hline
%Matthieu Perin       &   &   &   & x & x &   \\\hline
Michael Jastram      &   & x & x & x & x & x \\\hline
Nicolas van Landeghem& x & x &   &   &   &   \\\hline
Peter Mahlmann       & x & x & x & x & x & x \\\hline
%Peyman Farhangi      &   & x & x & x & x & x \\\hline
Pierre-Yves Le Morvan&   & x & x & x &   &   \\\hline
%Silvano dal Zilio    &   &   & x & x & x &  \\\hline
Stefan Karg          & x & x & x & x & x &   \\\hline
Stefan Rieger        & x & x & x & x & x &   \\\hline
Uwe Steinke          & x & x & x & x & x & x \\\hline
Veronique Gontier    &   & x & x & x & x &   \\\hline
Vincent Nuhaan       &   &   &   & x &   &   \\\hline
% Name                  6   5   4   3   7   P  \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{WP6: Dissemination}
\begin{itemize}
\item Activities\\
The link to the Itea Co-Summit event is visible in the Wiki:
\url{https://github.com/openETCS/Dissemination/wiki/ITEA-ARTEMIS-Co-Summit-2015}. Please, use the doodle for planning your participation.
\url{http://doodle.com/4wwcndmadvg8vtu3#table}. Participants for the Itea summit need to register at Itea webside.

In preparation to the Co-Summit event a rehearsal for the actual Itea review meeting is planned. Location will be in Berlin as well.
Feedback frokm ERSA for the participation is outstanding.

\end{itemize}

\subsection{WP5: Demonstration}
\begin{itemize}
\item Activities\\
The seperation of interfaces (CORBA based) is progressing.  ERSA already has data for the Utrecht-Amsterdam track in stock. To enable use within openETCS a permit by NS is needed. 

\end{itemize}

\subsection{WP4: Validation \& Verification}
\begin{itemize}
\item Activities\\
The synch-meeting WP3-WP4 has happened. Use-Cases for the next release (target begin March) have been discussed and the work-split has been agreed on. WP4 plans to extend the use cases to scenarios. 
\end{itemize}

\subsection{WP3: Modelling}
\begin{itemize}

\item WP3 Activities\\
Team 1 workshop took place in Alstom premeises in Paris. Work with Scade started. An update of the architecture is also planned. 

\item Scade Training\\
The Scade training is scheduled now for 12th of January - 16th of January.
The date has been confirmed by Esterel. Invitations are sent to the participants.

\end{itemize}

\subsection{WP7: Toolchain}

\begin{itemize}
\item Activities\\
Sprint activities are progressing. Work with the product backlog is well accepted. To improve the tools-chain work a guideline on the use of the Scade tools is requested.

\end{itemize}

\subsection{PMB: Project Management Board}
\begin{itemize}

\item Activities\\
The technical review document (TR1.1) is still open. Contributions from Alstom and DLR are pending.

\item Scrum Of Scrum Proposal\\
Backlog grooming has been continued. You will find the actual state in the product backlog repository.

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/\jobname}. Please, use the issue tracker for findings with the minutes.

\end{itemize}

\end{document}
