
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\usepackage{booktabs}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}

\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum Meetings\\
Minutes by & Peter Mahlmann (DB Netz AG)\\
When & October 2nd, 2015, 9:45 AM -- 11:45 AM\\
Location & Telco and GoToMeeting\newline \url{https://global.gotomeeting.com/meeting/join/493963173}\\
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting Agenda}

\begin{tabular}{lll}
\toprule
\textbf{Slot} &  \textbf{Chair} & \textbf{Work Package} \\
\midrule 
9:45 AM -- 10:15 AM & Peter Mahlmann & Product Backlog Grooming  \\
10:15 AM -- 10:30 AM & Matthieu Poirot & WP5 openETCS Demonstrator \\  
10:30 AM -- 10:45 AM & Marc Behrens & WP4 Validation \& Verification \\
10:45 AM -- 11:00 AM & Bernd Hekele & WP3 Modeling \\
11:00 AM -- 11:15 AM & Michael Jastram & WP7 openETCS Tool Chain \\
11:15 AM -- 11:45 AM & Klaus-R\"udiger Hase & Project Management Board \\
\bottomrule
\end{tabular}

\section{List of Attendees}

\begin{table}[htbp]
    \begin{tabular}{rrr}
    \toprule
    \textbf{Name} & \textbf{Join Time} & \textbf{Leave Time} \\
    \midrule
     Alexander Pinnau (ICS) & 10:28 AM & 11:40 AM \\
     Baseliyos Jacob (DB) & 9:56 AM & 10:03 AM \\
     Behrens, Marc (DLR)& 9:45 AM & 11:39 AM \\
     Silvano Dalzilio (CNRS LAAS)& 10:27 AM & 11:40 AM \\
     FAUDOU Raphael (Samares Engineering)& 9:45 AM & 11:09 AM \\
     Ingo Weigelt (Formal Mind)& 9:51 AM & 11:40 AM \\
     Jan Welte (TU-BS) & 9:55 AM & 10:56 AM \\
     Marielle Petit-Doche (Systerel)& 10:23 AM & 11:40 AM \\
     Matthieu Poirot (ERSA) & 9:45 AM & 11:40 AM \\
     Mercuri, Dario (GE) & 10:03 AM & 10:21 AM \\
     Michael Jastram (Formal Mind)& 10:53 AM & 11:40 AM \\
     Michael Jastram (Formal Mind)& 9:45 AM & 9:52 AM \\
     Nasir Mohamed (AEbt) & 9:50 AM & 11:40 AM \\
     Klaus-R\"udiger Hase (DB)& 10:10 AM & 11:40 AM \\
     Peter Mahlmann (DB) & 9:45 AM & 11:40 AM \\
     Thorsten Schulz (Uni Ro) & 10:31 AM & 11:40 AM \\
     Uwe Steinke (Siemens) & 9:45 AM & 11:40 AM \\
     \bottomrule
    \end{tabular}%
  \label{tab:addlabel}%
\end{table}%




\section{Minutes}

\subsection{Product Backlog Grooming}
\begin{itemize}
\item The product backlog is available via 
\url{https://github.com/openETCS/product-backlog}. 
\item For the results of the grooming session we refer to the corresponding waffle.io scrum board available via \url{https://waffle.io/openETCS/product-backlog} (free GitHub account needed).
\end{itemize}

\subsection{WP6: Dissemination}
\begin{itemize}
\item The WP6 meeting was canceled, the slot of this meeting has been used for product backlog grooming instead.
\end{itemize}

\subsection{WP5 openETCS Demonstrator}
\begin{itemize}
\item ERSA is still working on the generic API. The release of a draft, originally  scheduled for today, has been postponed to next Friday, i.e. October 9th.
\item The integration of GE hardware in the DLR labs is progressing:
	\begin{itemize}
	\item EVC code can be compiled to tun with the GE software libraries. These libraries are however not royalty free.
	\item Results are expected for mid of October.
	\item The possibility to show GE hardware integration at the final ITEA review as a WP5 demonstrator has been discussed and will be further investigated.
	\end{itemize}
\item The state of WP5 deliverables has been discussed:
	\begin{itemize}
	\item M5.2: Data for testing is available, however integration is still pending.
	\item M5.4 and D5.2: Will be completed in time for the final ITEA review.
	\item M5.5 and D5.3: Unclear for the moment. Will be discussed between ERSA, DLR and GE.
	\end{itemize}
\end{itemize}

\subsection{WP4 Validation \& Verification}
\begin{itemize}
\item With respect to the assessment the mapping of deliverables to required CENELEC EN50128 has been discussed.
\item Concerning D4.5 the task description has been completed. The structure for the document will be available by Wednesday.
\item The agile assessment process has been documented in the assessment plan by DLR.
\item The V\&V plan will be updated by end of October.
\item A major focus of WP4 activities currently is the traceability between SRS, SysML and SCADE Suite. Here, the focus lies on the SRS and SCADE Suite part due to the WP3 process and constraints.
\end{itemize}

\subsection{WP3 Modeling}
\begin{itemize}
\item This week the data flow between the componentes for level and mode management, information filtering and the track atlas has been discussed in several meetings between DB, LEA, TWT, and Systerel.
\item For next week a two day WP3 workshop is planned at the site of LEA in Augsburg.
\item It is noted that a stable interface of the WP3 model is needed by October 15th to allow ERSA the integration into the "road show" demonstrator.
\item Another focus of work this week was the SysML model and the ADD document. Here, especially the documentation and/or SysML models of Track Atlas, level and mode management, ETCS procedures, and the DMI are still missing.
\end{itemize}

\subsection{WP7 openETCS Tool Chain}
\begin{itemize}
\item The migration of the modeling results to an open source tool chain has been discussed with LAAS, who will drive this topic. For details see \url{https://github.com/openETCS/toolchain/issues/500}. The WP7 Thursday meeting will be used for further investigation on this.
\end{itemize}

\subsection{Project Management Board}
\begin{itemize}
\item Possible demonstrators of the various WPs at the foinal review have been discussed. WP leaders are asked to further investigate on possible demonstrations.
\item It has been noted that the TCSIM integration is no more feasible within the ITEA project. A PC based mobile demonstrator is in development instead.
\item For the final ITEA revie it will be tried to run the openETCS OBU model on GE hardware in combination with a simulated DMI. The timescale for this is tight however.
\item The removal of the ERTMS formal specs repository from the openETCS GitHub site has been discussed. This has to be clarified by ERTMS solutions.
\end{itemize}


\section{General Remarks}

\begin{itemize}
\item Please find these minutes online at \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/\jobname.pdf}. Please, use the github issue tracker for findings and corrections within the minutes.
\end{itemize}

\end{document}
