
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
Organised by & Bernd Hekele\\
Minutes by & Bernd Hekele\\
When & June 30th, 2014, 9:30 - 12:00\\
Location & Telco and Goto-Meeting\\
%9:30-10:00 and 
%\hline
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
10:15 - 10:30 & Nicolas van Landeghem & WP5: Demonstration \\\hline  
10:30 - 10:45 & Marc Behrens & WP4: Verification \& Validation \\\hline  
10:45 - 11:00 & Fausto Cocchetti & WP3: Modelling \\\hline  
11:00 - 11:15 & Michael Jastram & WP7: Toolchain \\\hline
%11:15 - 11:30 & Baseliyos Jacob & WP2: API Requirements \\\hline  
11:15 - 11:30 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} \\\hline
% Name                  6   5   4   3   7   P
%Alessandro Cimatti   &   &   &   &   &   &  \\\hline 
Alexander Nitsch     & x & x & x & x & x & x \\\hline  
%Alexander Stante     &   &   &   &   & x &   \\\hline 
%Baseliyos Jacob      &   & x & x & x & x & x \\\hline 
%Benjamin Beichler    &   &   &   &   &   &   \\\hline 
Bernd Hekele         & x & x & x & x & x & x \\\hline
Cecile Braunstein    &   &   & x & x & x &   \\\hline
%Christian Giraud     &   &   &   &   &   &   \\\hline
%Christian Stahl      &   & x & x & x &   &   \\\hline
%David Mentre         &   &   &   &   &   &   \\\hline
Fausto Cochetti      &   &   & x & x & x &   \\\hline
Hardi Hungar         &   &   & x &   &   &   \\\hline
%Huu-Nghia Nguyen     &   &   &   &   &   &   \\\hline
%Izaskun de la Torre  &   &   &   & x & x &   \\\hline
Jan Welte            &   &   & x & x & x & x \\\hline
%Jan Welvaarts        &   &   &   & x &   &   \\\hline
%Jens Gerlach         &   &   & x &   &   &   \\\hline
%Jonas Helming        &   &   &   &   &   &   \\\hline
%Klaus-R\"udiger Hase &   & x & x & x & x & x \\\hline
%Laurent Ferier       &   &   &   & x & x & x \\\hline
%Lukasz Fronc         &   &   &   &   &   &   \\\hline
%Marc Behrens         &   & x & x & x & x & x \\\hline
Marielle Petit-Doche & x & x & x & x & x & x \\\hline
%Mathilde Arnaud      &   &   &   &   &   &   \\\hline
%Matthieu Perin       &   &   &   &   & x &   \\\hline
Michael Jastram      &   &   &   & x & x & x \\\hline
Nicolas van Landeghem&   & x &   &   &   &   \\\hline
Peter Mahlmann       &   & x & x & x & x & x \\\hline
%Peyman Farhangi      &   & x & x & x & x & x \\\hline
Silvano dal Zilio    &   &   & x & x & x & x \\\hline
Stefan Rieger        & x & x & x & x & x & x \\\hline
%Uwe Steinke          &   & x & x & x & x & x \\\hline
Veronique Gontier    &   &   &   & x & x & x \\\hline
Vincent Nuhaan       &   & x & x &   &   &   \\\hline
% Name                  6   5   4   3   7   P  \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{WP6: Dissemination}

The preparation for the Innotrans is ongoing. \url{
https://github.com/openETCS/Dissemination/wiki/INNOTRANS-2014-Planning}. We still are looking for topics to present in a short slot (15 min.). Please, indicate you plan for participating with this doodle: \url{http://doodle.com/xhkuppzrtupunsue}.

Activities on the dissemination plan are also proceeding.

\subsection{WP5: Demonstration}
\begin{itemize}
\item Update on Activities\\

D5.1: The review of the functional specification is ongoing. So far no comments have been posted \url{https://github.com/openETCS/demonstrator/issues/8}.

Further documents are now in work (Test Specification).

\end{itemize}


\subsection{WP4: Validation \& Verification}
\begin{itemize}
\item actual event\\
Currently in focus: How to take into account track profile given by a train expert and how to simulate it with RT-tester.

The  update of VnV user stories in the Sec. 8.2 of the VnV Plan (V02) is ongoing. 

The revision for the deliverables D4.2.1, D4.2.2 and D4.2.3 is in its final stages.. 

\end{itemize}

\subsection{WP3: Modelling}

\begin{itemize}
\item Activities\\
The follow-up meeting for modelling took place in Munich. Focus was on activities leading to the architecture. 

\end{itemize}

\subsection{WP7: Toolchain}

The backlog and the resource plan have been updated.

The first version of the openETCS PDF Handbook is now available \url{https://github.com/openETCS/toolchain/wiki/Simple-Scrum-Process}.

The tool qualification plan ahs been reviewed.

\subsection{WP2: Requirements}

No meeting this week.

\subsection{PMB: Project Management Board}
\begin{itemize}
\item Results of ITEA Review Meeting\\
The review results are available. All presentations and the result are linked to the management wiki. \url{https://github.com/openETCS/management/wiki/ITEA-Review-2014}

\item Status of Change request\\
The change request requesting extension of the project by 6 months has been confirmed by ITEA. To make the change request concrete each cluster has to apply for the extension separately at the local authorities.

\item Proceeding on Scrum of Scrum Acivity\\
It was discussed to enforce the project management efficiency in a  side meeting to the Munich Review Workshop. The action is not yet implemented. \url{https://github.com/openETCS/toolchain/wiki/Simple-Scrum-Process}

\item a.o.b.\\
Leader of the French Cluster is now Jacque Pores (Alstom).

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/Minute_20140627.pdf}. Please, use the issue tracker for findings with the minutes.

\end{itemize}

\end{document}
