
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
Organised by &Klaus-R\"udiger Hase\\
Minutes by & Bernd Hekele\\
When & September, 5th, 2014, 10:15 - 11:45\\
Location & Telco and Goto-Meeting\\
%9:30-10:00 and 
%\hline
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
%10:15 - 10:30 & Nicolas van Landeghem & WP5: Demonstration \\\hline  
10:30 - 11:00 & Marc Behrens & WP4: Verification \& Validation \\\hline  
10:45 - 11:00 & Fausto Cochetti & WP3: Modelling \\\hline  
%10:45 - 11:00 & Peter Mahlmann & WP3: Modelling \\\hline  
11:00 - 11:15 & Michael Jastram & WP7: Toolchain \\\hline
%11:15 - 11:30 & Baseliyos Jacob & WP2: API Requirements \\\hline  
11:15 - 11:45 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
%11:15 - 11:45 & Bernd Hekele & PMB: Project Management Board \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} \\\hline
% Name                  6   5   4   3   7   P
%Alexander Nitsch     & x & x & x & x & x & x \\\hline  
Alexander Stante     &   &   &   &   & x &   \\\hline 
Baseliyos Jacob      & x &   & x & x & x &   \\\hline 
%Bernd Gonska         &   &   & x &   &   &   \\\hline
Bernd Hekele         & x &   & x & x & x & x \\\hline
%Benjamin Beichler    &   &   & x & x & x &   \\\hline
%Cecile Braunstein    &   &   & x & x & x &   \\\hline
%Christian Giraud     &   &   &   &   &   &   \\\hline
%Christian Stahl      &   &   &   & x &   &   \\\hline
%David Mentre         &   &   &   &   &   &   \\\hline
Fausto Cochetti      &   &   &   & x & x &   \\\hline
Hardi Hungar         &   &   &   &   & x &   \\\hline
%Huu-Nghia Nguyen     & x &   & x & x & x &   \\\hline
%Ion I. Uribe         &   &   & x &   &   &   \\\hline
%Izaskun de la Torre  &   &   &   & x & x &   \\\hline
Jan Welte            & x &   & x & x & x & x \\\hline
%Jakob Gaertner       &   &   &   & x & x &   \\\hline
%Jan Welvaarts        &   &   &   & x &   &   \\\hline
Jaime Paniagua       &   &   & x &   &   &   \\\hline
%Jens Gerlach         & x & x & x & x &   &   \\\hline
%Jonas Helming        &   &   &   &   &   &   \\\hline
Jos Holtzer          & x &   &   &   &   &   \\\hline
Karsten Falk         &   &   & x & x &   &   \\\hline
%Klaus-R\"udiger Hase &  & x & x & x & x & x \\\hline
%Laurent Ferier       &   &   &   & x & x & x \\\hline
%Lukasz Fronc         &   &   &   &   & x & x \\\hline
Marc Behrens         &   &   & x & x & x & x \\\hline
Marielle Petit-Doche & x &   & x & x & x & x \\\hline
%Mathilde Arnaud      &   &   &   &   &   &   \\\hline
%Matthieu Perin       &   &   & x & x & x & x \\\hline
Michael Jastram      &   &   & x & x & x & x \\\hline
%Nicolas van Landeghem&   & x &   &   &   &   \\\hline
%Peter Mahlmann       &   & x & x & x & x & x \\\hline
Peyman Farhangi      &   &   &   & x &   &   \\\hline
Pierre-Yves Le Morvan&   &  & x & x & x & x \\\hline
%Silvano dal Zilio    &   &   & x & x & x &  \\\hline
Stefan Rieger        & x &   & x & x & x & x \\\hline
Uwe Steinke          & x &   & x & x & x & x \\\hline
%Veronique Gontier    &   &   & x & x & x & x \\\hline
Vincent Nuhaan       &   &   &   & x &   &   \\\hline
% Name                  6   5   4   3   7   P  \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{WP6: Dissemination}
\begin{itemize}
\item openETCS@Innotrans\\
The openETCS@Innotrans preparation is proceeding as planned. No issues open. The invitation to externals to visit the workshop has been sent. The electronic copy of the flyer is available here: \url{https://github.com/openETCS/Dissemination/blob/master/InnoTrans%202014/InvitationFlyer.pdf?raw=true}\\
A poster is shown e.g., at the ERSA booth.

\item openETCS Publications\\
Please, report your openETCS publications for the upcoming report.

\end{itemize}

\subsection{WP5: Demonstration}
%\begin{itemize}
No meeting.
%\end{itemize}

\subsection{WP4: Validation \& Verification}
\begin{itemize}
\item Review of Calculate Train Position document\\
The verification results to the train positioning design has been done by DLR (Bernd Gonska). It has been uploaded linked to the Issue \url{https://github.com/openETCS/validation/issues/227}.

\item Activities\\
The last week Wednesday the Telco On Testing took place on closing issues of the Backlog to D4.2.x.

The next telco on testing will focus on the WP3 Brussels workshop.

\item The follow-up meeting of the internal assessment with AEbt\\
has been re-scheduled in order to take place after the Innotrans-Event.

Next Wednesday, the 17th a special session on coding rules is planned. Please join \url{https://global.gotomeeting.com/join/334291797}.

\end{itemize}

\subsection{WP3: Modelling}
\begin{itemize}

\item WP3 workshop\\
Last week Tuesday and Wednesday a WP3 workshop took place in Brussels. The results can be found here \url{https://github.com/openETCS/SRS-Analysis/tree/master/Meetings/Team-meeting_Brussels_2014-09-09}.

The API document v1.4 is now available. The document is an update of the API document from Alstom in order to be compliant to Baseline3. Major changes are: \\
For a summary, the main modifications are:
\begin{itemize}
\item DMI interface (telegrams between the EVC and the DMI have been updated).
\item The radio interface (the radio API has been updated).
\end{itemize}
 
\item Convergence Workshops\\
The differences of the various architecture proposals existing in openETCS is proposed to be tackled in a convergence workshop. Details to be planned.

\item Architecture Team by DB\\
DB will take responsibility of the Architecture task. First team meeting scheduled for Monday, 14:00.

\end{itemize}

\subsection{WP7: Toolchain}

\begin{itemize}
\item A WP7 team meeting is planned to take place in Munich: \url{https://github.com/openETCS/toolchain/wiki/WP7-Workshop-Fall-2014}. The agenda is currently under construction.
\end{itemize}

\subsection{PMB: Project Management Board}
\begin{itemize}
\item Scrum Of Scrum\\
Second half of September Peter will start to organize follow-up sessions to continue working on the openETCS backlog.\\

\item \textbf{No PCC Scheduled}\\
Currently, there is no plan to have a PCC in mid October. 

However, we have the option to use the reserved facilities in  Munich for another meeting. Proposals are welcome.

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/Minute_20140912.pdf}. Please, use the issue tracker for findings with the minutes.

\end{itemize}

\end{document}
