
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
Organised by & Bernd Hekele\\
Minutes by & Bernd Hekele\\
When & August, 1st, 2014, 10:00 - 11:45\\
Location & Telco and Goto-Meeting\\
%9:30-10:00 and 
%\hline
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
%10:15 - 10:30 & Nicolas van Landeghem & WP5: Demonstration \\\hline  
10:30 - 10:45 & Marc Behrens & WP4: Verification \& Validation \\\hline  
10:45 - 11:00 & Fausto Cochetti & WP3: Modelling \\\hline  
%10:45 - 11:00 & Bernd Hekele & WP3: Modelling \\\hline  
11:00 - 11:15 & Michael Jastram & WP7: Toolchain \\\hline
%11:15 - 11:30 & Baseliyos Jacob & WP2: API Requirements \\\hline  
11:15 - 11:45 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
%11:15 - 11:45 & Bernd Hekele & PMB: Project Management Board \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} \\\hline
% Name                  6   5   4   3   7   P
%Alexander Nitsch     & x & x & x & x & x & x \\\hline  
%Alexander Stante     &   &   &   &   & x &   \\\hline 
Baseliyos Jacob      & x &   & x & x & x & x \\\hline 
%Bernd Gonska         &   &   & x &   &   &   \\\hline
Bernd Hekele         & x &   & x & x & x & x \\\hline
Cecile Braunstein    &   &   & x & x & x &   \\\hline
%Christian Giraud     &   &   &   &   &   &   \\\hline
Christian Stahl      &   &   & x & x &   &   \\\hline
%David Mentre         &   &   &   &   &   &   \\\hline
Fausto Cochetti      &   &   &   & x &   &   \\\hline
%Hardi Hungar         &   &   & x &   &   &   \\\hline
Jos Holtzer         & x &   &   &   &   &   \\\hline
%Huu-Nghia Nguyen     & x &   & x & x & x &   \\\hline
%Izaskun de la Torre  &   &   &   & x & x &   \\\hline
%Jan Welte            & x & x & x & x & x & x \\\hline
%Jan Welvaarts        & x & x & x & x &   &   \\\hline
%Jens Gerlach         &   &   & x &   &   &   \\\hline
%Jonas Helming        &   &   &   &   &   &   \\\hline
Klaus-R\"udiger Hase & x &   & x & x & x & x \\\hline
%Laurent Ferier       &   &   &   & x & x & x \\\hline
%Lukasz Fronc         &   &   &   &   &   &   \\\hline
Marc Behrens         &   &   & x & x & x & x \\\hline
%Marielle Petit-Doche &   & x & x & x & x & x \\\hline
%Mathilde Arnaud      &   &   &   &   &   &   \\\hline
%Matthieu Perin       &   &   & x & x & x & x \\\hline
Michael Jastram      &   &   &   & x & x & x \\\hline
%Nicolas van Landeghem& x & x & x & x & x & x \\\hline
%Peter Mahlmann       &   & x & x & x & x & x \\\hline
Peyman Farhangi      &   &   & x & x & x & x \\\hline
Pierre-Yves Le Morvan&   & x &   & x & x & x \\\hline
%Silvano dal Zilio    &   &   & x & x & x & x \\\hline
Stefan Rieger        & x &   & x & x & x & x \\\hline
Uwe Steinke          & x &   & x & x & x & x \\\hline
%Veronique Gontier    & x & x & x & x & x & x \\\hline
%Vincent Nuhaan       &   &   &   & x &   &   \\\hline
% Name                  6   5   4   3   7   P  \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{WP6: Dissemination}

\begin{itemize}
\item openETCS@Innotrans: Speakers Corner\\
You find a regular update of the planning of this event in the dissemination Wiki:
\url{https://github.com/openETCS/Dissemination/wiki/INNOTRANS-2014-Planning}.

Jos Holtzer (NS) confirmed NS to step in to host the speakers corner. Klaus-R\"udiger also will plan for a talk. Details are to be planned on next Friday afternoon.

\item openETCS Mid-Term workshop (open event)\\
There are currently no rooms available at the Innotrans event to hold the workshop. Since invitations need to be sent to interested persons soon we need a quick result.

\end{itemize}

\subsection{WP5: Demonstration}
\begin{itemize}
\item Update on Activities\\

No update this week due to technical issues.

\end{itemize}


\subsection{WP4: Validation \& Verification}
\begin{itemize}
\item actual activities\\
The meta-model on testing has been discussed in the weekly meeting. 

A template for the VnV User Story is uploaded by Hardi as a basis for planned VnV Level 2 activities and can be found here: \url{https://github.com/openETCS/validation/blob/master/VerificationAndValidationPlan/V02/VnVUsrStrTmplt-140709-02.pdf?raw=true}. Please fill out the user story documenting and coordinating the VnV Level 2 activities you are involved.\\
The second user story for the VnV Plan was already provided thanks to University of Bremen.
 
\end{itemize}

\subsection{WP3: Modelling}

\begin{itemize}
\item Activities\\

The site and date for next WP3 Workshop are fixed now. The meeting is scheduled for September 9th - 10th in Brussels. Details will follow with the invitation.

If you plan to participate, please make use of this doodle: \url{http://doodle.com/cm3kpzi9smecrpcz}

The document on database by Chrstian Giraud is available on Github: \url{https://github.com/openETCS/SRS-Analysis/blob/master/System%20Analysis/WorkingRepository/Group2/WG3_OpenETCS_Database_V9b.docx} in version 9b.

A discussion of the concept in a wider scope is needed. It is agreed to invite additional stakeholders for a review on the document and a grooming session on the architecture.

Next weeks Tuesday a modelling Scade workshop is planned to take place in Braunschweig (9:00-16:00 at Siemens). Remote participation is planned to be supported (for details see openETCS project calendar).

\end{itemize}

\subsection{WP7: Toolchain}

\begin{itemize}
\item Activities\\
The clarification of requirements and first concepts is being continued. Alexander plans to deliver a first study of a plugin handling profiles to the next toolchain release.

Sprint 16 is being extended.

Progress is updated in the sprint activity backlog.

\end{itemize}

\subsection{WP2: Requirements}

%\begin{itemize}

No meeting this week.

%\end{itemize}

\subsection{PMB: Project Management Board}
\begin{itemize}
\item a.o.b.\\
No issues reported. 

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/Minute_20140801.pdf}. Please, use the issue tracker for findings with the minutes.

\end{itemize}

\end{document}
