
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS Scrum Meeting Minutes\end{center}}
\section{Meeting Organisation}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & Weekly Scrum of Scrums\\
%Organised by &Klaus-R\"udiger Hase\\
Organised by &Bernd Hekele\\
Minutes by & Bernd Hekele\\
When & December, 5th, 2014, 10:00 - 12:00\\
Location & Telco and Goto-Meeting\\
%9:30-10:00 and 
%\hline
\end{supertabular}

\renewcommand{\arraystretch}{1.0}
\section{Meeting:}

\begin{tabular}{|c|l|l|}
\hline
\textbf{Slot} &  \textbf{Called By} & \textbf{Workpackage} \\
\hline  
10:00 - 10:15 & Stefan Rieger & WP6: Dissemination \\\hline  
10:15 - 10:30 & Nicolas van Landeghem & WP5: Demonstration \\\hline  
10:30 - 11:00 & Jan Welte & WP4: Verification \& Validation \\\hline  
%10:30 - 11:00 & Marc Behrens & WP4: Verification \& Validation \\\hline  
%10:45 - 11:00 & Fausto Cochetti & WP3: Modelling \\\hline  
%10:45 - 11:00 & Peter Mahlmann & WP3: Modelling \\\hline  
10:45 - 11:00 & Bernd Hekele & WP3: Modelling \\\hline  
11:00 - 11:15 & Michael Jastram & WP7: Toolchain \\\hline
%11:15 - 11:30 & Baseliyos Jacob & WP2: API Requirements \\\hline  
11:15 - 12:00 & Klaus-R\"udiger Hase & PMB: Project Management Board \\\hline  
%11:15 - 11:45 & Bernd Hekele & PMB: Project Management Board \\\hline  
\end{tabular}

\section{Participants in Meeting:}

\begin{tabular}{|l|c|c|c||c|c|c||c|c|c|}
\hline
\textbf{Participant} & \textbf{WP6} &  \textbf{WP5} & \textbf{WP4}&  \textbf{WP3} & \textbf{WP7}&  \textbf{PMB} \\\hline
% Name                  6   5   4   3   7   P
%Alexander Nitsch     &   &   &   &   &   &   \\\hline  
Alexander Stante     &   &   &   &   & x & x \\\hline 
%Baseliyos Jacob      &   &   & x & x & x &   \\\hline 
%Bernd Gonska         &   &   & x &   &   &   \\\hline
Bernd Hekele         & x & x & x & x & x & x \\\hline
Benjamin Beichler    &   & x & x & x & x &   \\\hline
%Cecile Braunstein    &   &   & x & x & x &   \\\hline
%Christian Giraud     &   &   &   &   &   &   \\\hline
Christian Stahl      &   &   & x & x &   &   \\\hline
%David Mentre         &   &   &   &   &   &   \\\hline
%Fausto Cochetti      &   &   & x & x & x &   \\\hline
%Hardi Hungar         &   &   & x &   & x &   \\\hline
%Huu-Nghia Nguyen     & x &   & x & x & x &   \\\hline
%Ion I. Uribe         &   &   & x &   &   &   \\\hline
Izaskun de la Torre  & x & x & x & x & x & x \\\hline
Jan Welte            & x & x & x & x & x & x \\\hline
Jaime Paniagua       &   &   &   & x &   &   \\\hline
%Jakob Gaertner       &   &   &   & x & x &   \\\hline
Jan Welvaarts        &   &   &   & x &   &   \\\hline
%Jens Gerlach         & x & x & x & x &   &   \\\hline
%Jonas Helming        &   &   &   &   &   &   \\\hline
%Jos Holtzer          & x &   &   &   &   &   \\\hline
%Karsten Falk         &   &   & x & x & x & x \\\hline
Klaus-R\"udiger Hase &   & x & x & x & x & x \\\hline
%Laurent Ferier       &   &   &   & x & x & x \\\hline
%Lukasz Fronc         &   &   &   &   & x & x \\\hline
%Marc Behrens         &   &   & x & x & x & x \\\hline
Marielle Petit-Doche &   &   & x & x & x & x \\\hline
%Mathilde Arnaud      &   &   &   &   &   &   \\\hline
%Matthieu Perin       &   &   &   & x & x &   \\\hline
Michael Jastram      &   &   &   & x & x & x \\\hline
Nicolas van Landeghem&   & x &   &   &   &   \\\hline
Peter Mahlmann       & x & x & x & x & x & x \\\hline
%Peyman Farhangi      &   & x & x & x & x & x \\\hline
Pierre-Yves Le Morvan&   & x & x & x &   & x \\\hline
%Silvano dal Zilio    &   &   & x & x & x &  \\\hline
Stefan Karg          & x & x & x & x & x & x \\\hline
Stefan Rieger        & x & x & x & x & x & x \\\hline
Uwe Steinke          &   & x & x & x & x & x \\\hline
Veronique Gontier    &   & x & x & x & x &   \\\hline
Vincent Nuhaan       &   &   &   & x &   &   \\\hline
% Name                  6   5   4   3   7   P  \\\hline
\end{tabular}

%\line(1,0){440}

\section{Scrum Meetings}

\subsection{WP6: Dissemination}
\begin{itemize}
\item Activities\\
The link to the Itea Co-Summit event is visible in the Wiki:
\url{https://github.com/openETCS/Dissemination/wiki/ITEA-ARTEMIS-Co-Summit-2015}. Please, use the doodle for planning your participation.
\url{http://doodle.com/4wwcndmadvg8vtu3#table} Presentations are under discussion. THe toolschain is an option. Another result needs to come out of the scope of WP3 and WP5.

\end{itemize}

\subsection{WP5: Demonstration}
\begin{itemize}
\item Activities\\
The seperation of interfaces (CORBA based) is progressing. 
For the demonstration of the hw-platform the ERSA DMI implementation is chosen. Publishinmg the interfaces has been discussed. Conformation outstanding.

\end{itemize}

\subsection{WP4: Validation \& Verification}
\begin{itemize}
\item Activities\\
WP3 and WP4 synch meeting is scheduled for December 10th. 
\end{itemize}

\subsection{WP3: Modelling}
\begin{itemize}

\item WP3 Activities\\
Work a first iteration is progressing. The product shall be defivered to WP4. 

\item Scade Training\\
The Scade training is scheduled now for 12th of January - 16th of January.
The date has been confirmed by Esterel.

Individual invitations to participants will follow. The scope of the training has been slightly changed: we still plan to have a basic "newcomer" training as a start. But at the rear of the training (Thursday - Friday) we plan to swith to Q\&A and problems solving coming from more experienced partners.

\end{itemize}

\subsection{WP7: Toolchain}

\begin{itemize}
\item Activities\\
The Reqif transformation tool for the SRS document is progressing. 
\end{itemize}

\subsection{PMB: Project Management Board}
\begin{itemize}

\item Activities\\
The technical review document (TR1.1) has been presented. Review is ongoing and will be finalised Friday, 12th of December.

\item Scrum Of Scrum Proposal\\
Backlog grooming has been continued. You will find the actual state in the product backlog repository.

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/Minutes/\jobname}. Please, use the issue tracker for findings with the minutes.

\end{itemize}

\end{document}
