
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP4 Meeting Minutes\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP3 Weekly Scrum: Modelling\\
Date \& time & 2013-07-19, 10:45h--11:00h\\
Location & Telco and Goto-Meeting\\
Called up by & Pierre-Francois Jauquet\\
Participants &
Benjamin Beichler,
Marc Behrens,
Cecile Braunstein,
Cyril Cornu,
%Sylvain Baro,
Fausto Cochetti,
%Peyman Farhangi,
Jens Gerlach,
%Frank Golatowski,
%Ainhoa Gracia,
Michael Jastram,
Klaus-R\"udiger Hase,
Bernd Hekele,
Jonas Helming,
Hardi Hungar,
%Roberto Kretschmer,
Peter Mahlmann,
Alexander Nitsch,
Marielle Petit-Doche,
Stan Pinte,
Merlin Pokam,
Christophe Ponsard,
Stefan Rieger,
Uwe Steinke,
Pierre Francois Jauquet
%Benjamin Beichler,
%Jo\~ao Santos,
%Izaskun de la Torre
%Jan Welte
%Silvano dal Zilio,
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item Short summary of this week results.
\end{itemize}

\section{Discussion}
\begin{itemize}

\item Initial Meeting\\
This was the initial meeting for WP3. A weekly meeting is planned to take place from now on.
\item Functional Analysis\\
Work by ERTMSSolutions with ERTMSFormalSpec (EFS) has been interrupted. EFS has not been selected in the first primary toolchain decision. Michael pointed out the decision will take place as planned. There is no reason to interrupt ongoing activities.  
\item Start of Modelling\\
Pierre-Francois sees three dependencies before the modelling tasks can be started:
\begin{enumerate}
\item requirements are defined (ok)
\item SSRS is available (started)
\item the tool for modelling is selected (ongoing)
\end{enumerate}
Klaus-R\"udiger pointed out modelling activities can also start based on the Paris decision (Papyrus + SysML). The Paris decision does not stop any other tools from being selected. Especially, there is no hidden vote pro or against EFS hidden in this decision.
\end{itemize}


\section{Notes}
The meeting was heavily disturbed by technical issues with goto-meeting servers.

\end{document}
