
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP3 Meeting Minutes\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP3 Weekly Scrum: Modelling\\
%9:30-10:00 and 
Date \& time & 2014-05-09, 9:30-10:00 and 10:45h--11:00h\\
Location & Telco and Goto-Meeting\\
Called up by & Bernd Hekele\\
Participants &
%Mathilde Arnaud,
%Benjamin Beichler,
Marc Behrens,
Cecile Braunstein,
%Alessandro Cimatti (only 9:30 slot),
Fausto Cochetti,
Peyman Farhangi,
Lukasz Fronc,
%Baseliyos Jacob,
Klaus-R\"udiger Hase,
Bernd Hekele,
%Jonas Helming,
%Hardi Hungar,
Michael Jastram,
Peter Mahlmann,
Alexander Nitsch,
%Huu-Nghia Nguyen,
Vincent Nuhaan,
Matthieu Perin,
%Marielle Petit-Doche,
Alexander Stante,
Stefan Rieger,
%Christian Stahl,
Uwe Steinke,
%Izaskun de la Torre,
%Giovanni Trotta,
Jan Welte,
Jan Welvaarts
Giovanni Zanelli
%Silvano dal Zilio
\\

Minutes by & Bernd Hekele\\
%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item Upcoming Events
\item Update on Modelling tools - Scade System Beta
\item each partner: impediments, progress
\item a.o.b.
\end{itemize}

\section{Discussion}
\begin{itemize}
\item Upcoming Events\\
The \textbf{openETCS API} is scheduled for May 13th in Munich. It is planned as a technical workshop to conclude on the discussion about the structure and open issues in the review.

The next \textbf{WP3 modelling workshop}, now under management of Alstom, is  scheduled to take place on May 26th - May 28th.
Location of the meeting is close to Brussels Midi. The agenda has been discussed and will be distributed to the participants after todays meeting.

\item Update on Modelling tools - Scade System Beta\\
Esterel has released the Beta for Scade System. The update is available via the update mechanismus of Scade Suite. If you need help get in touch with openETCS projectoffice.\\
Peyman started to test the interface\textit{Papyrus - Scade System - Scade Suite} based on the example of the dataDictionary. Alexander supports this activity. As a result of this action we plan to provide a "requirements and wishes" for support by Esterel for openETCS.

\item each partner: impediments, progress\\
Status is updated in SRS-Analysis and in the modelling repository. 

Contributions have been done to the SysML models and in the data dictionary. In addition, comments have been received on the modelling contribution to the "list of methods and techniques (to meet CENELEC 50128") \url{https://github.com/openETCS/governance/issues/88} and "Template for Competence Matrix" \url{https://github.com/openETCS/governance/issues/63}.

\item a.o.b.\\

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/WP3-Modeling/Minute_20140509_WP3.pdf}. Please, use the issue tracker for findings in the minutes.

\end{itemize}


\end{document}
