
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP3 Meeting Minutes\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP3 Weekly Scrum: Modelling\\
Date \& time & 2013-09-27, 10:45h--11:00h\\
Location & Telco and Goto-Meeting\\
Called up by & Stan Pinte\\
Participants &
%Benjamin Beichler,
Marc Behrens,
%Cecile Braunstein,
Cyril Cornu,
%Sylvain Baro,
%Fausto Cochetti,
%Peyman Farhangi,
Laurent Ferrier,
%Jens Gerlach,
%Frank Golatowski,
%Ainhoa Gracia,
Michael Jastram,
%Klaus-R\"udiger Hase,
Bernd Hekele,
%Jonas Helming,
Hardi Hungar,
%Roberto Kretschmer,
Peter Mahlmann,
%Alexander Nitsch,
Marielle Petit-Doche,
Stan Pinte,
Merlin Pokam,
%Christophe Ponsard,
Stefan Rieger,
Uwe Steinke,
%Pierre Francois Jauquet
%Benjamin Beichler,
%Jo\~ao Santos,
%Izaskun de la Torre
Jan Welte
Silvano dal Zilio,
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item Description of Work
\item WP3 Kickoff Meeting
\end{itemize}

\section{Discussion}
\begin{itemize}

\item Description of Work\\
The meeting was called by projectOffice. Description of work for WP3 not yet prepared. Start of this activity requested by projectOffice.\\
Stan will start to work on the Description of Work for Tasks T3.5 and T3.6. (Deadline October 1st). Both are in responsibility of EFS.

\item WP3 Kickoff Meeting\\
The Kickoff Meeting is scheduled for October 8th. Participation from Alstom not yet confirmed. Alstom requested a preparation meeting which is scheduled for October 1st, in order to get a common understanding on the mode of operation (covered by issues \url{https://github.com/openETCS/governance/issues/60} and\\ \url{https://github.com/openETCS/model-evaluation/issues/21}.\\
The Kick-Off Agenda is pending. The strategy for Modelling as a part of openETCS is covered by the decisions in D7.1 and is on the agenda for the PCC (8.10.13).

\end{itemize}


\section{Notes}

\end{document}
