
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP3 Meeting Minutes\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP3 Weekly Scrum: Modelling\\
%9:30-10:00 and 
Date \& time & 2014-05-16, 9:30-10:00 and 10:45h--11:00h\\
Location & Telco and Goto-Meeting\\
Called up by & Bernd Hekele\\
Participants &
%Mathilde Arnaud,
%Benjamin Beichler,
Marc Behrens,
Cecile Braunstein,
%Alessandro Cimatti (only 9:30 slot),
Fausto Cochetti,
%Peyman Farhangi,
%Lukasz Fronc,
Christian Giraud,
%Baseliyos Jacob,
%Klaus-R\"udiger Hase,
Bernd Hekele,
%Jonas Helming,
%Hardi Hungar,
%Michael Jastram,
Peter Mahlmann,
David Mentre,
Alexander Nitsch,
%Huu-Nghia Nguyen,
Vincent Nuhaan,
Matthieu Perin,
Marielle Petit-Doche,
Stefan Rieger,
Christian Stahl,
Alexander Stante,
Uwe Steinke,
%Izaskun de la Torre,
%Giovanni Trotta,
%Jan Welte,
%Jan Welvaarts
Giovanni Zanelli
%Silvano dal Zilio
\\

Minutes by & Bernd Hekele\\
%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item Upcoming Events
\item Update on Modelling tools - Scade System Beta
\item each partner: impediments, progress
\item a.o.b.
\end{itemize}

\section{Discussion}
\begin{itemize}
\item Actual Events\\
The \textbf{openETCS API} review took place in Munich. You can find information about this event on Github: \url{https://github.com/openETCS/requirements/tree/master/D2.7-Technical_Appendix/2014-05-13-Munich-Meeting}. Meeting minutes are currently under review.

For results and further reading, please refer to the minutes.

The next \textbf{WP3 modelling workshop}, now under management by Alstom, is  scheduled to take place on May 26th - May 28th. Agenda and further reading can be found here: \url{https://github.com/openETCS/modeling/tree/master/meetings/Team-Meeting_Brussels-2014-05-26}

\item Update on Modelling tools - Scade System Beta\\
Esterel has released the Beta for Scade System. The openETCS use-case is now under investigation at DB. DB has started a discussion with Esterel on our findings. A workshop should be scheduled for June.

\item openETCS API Requirements\\
We returned to the definition of requirements for an openETCS API. This document can be seen as a guideline for future contracts. The actual version of the document is available here: \url{https://github.com/openETCS/requirements/blob/master/D2.7-Technical_Appendix/2014-05-13-Munich-Meeting/Bullit%20point%20openETCS%20requirements_20140511.pdf}. Baseliyos opened the \url{https://github.com/openETCS/requirements/issues/64} for review contributions. It is currently under clarification how and where the information will be finally located.

\item each partner: impediments, progress\\
Matthieu gave an update on the status for the Papyrus Luna Release.
He gave the recommendation to prepare for a trial of the latest Luna release in the openETCS toolchain. A first test of our model in the new release showed some needs for correction in the models. The follow-up of this issue is part of the WP7 plan.

\item a.o.b.\\

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/WP3-Modeling/Minute_20140516_WP3.pdf}. Please, use the issue tracker for findings with the minutes.

\end{itemize}

\end{document}
