
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP3 Meeting Minutes\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP3 Weekly Scrum: Modelling\\
Date \& time & 2014-02-28, 9:30-10:00 and  10:30h--10:45h\\
Location & Telco and Goto-Meeting\\
Called up by & Bernd Hekele\\
Participants &
Mathilde Arnaud,
%Benjamin Beichler,
%Marc Behrens,
%Cecile Braunstein,
Alessandro Cimatti (only 8:30 slot),
%Baseliyos Jacob,
Klaus-R\"udiger Hase,
Bernd Hekele,
%Hardi Hungar,
Michael Jastram,
Peter Mahlmann,
Alexander Nitsch,
Huu-Nghia Nguyen,
%Vincent Nuhaan,
Matthieu Perin,
%Marielle Petit-Doche,
Alexander Stante,
Stefan Rieger,
Uwe Steinke,
Izaskun de la Torre,
Jan Welte,
%Jan Welvaarts
Giovanni Zanelli
\\

Minutes by & Bernd Hekele\\
%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item Presentation of results of Rina project
\item Status openETCS API Review
\item First Iteration plan
\item Update on Activities
\item Upcoming Events\\
\end{itemize}

\section{Discussion}
\begin{itemize}
\item Presentation of results of Rina project\\
In the first section of the meeting a presentation by Alessandro Cimatti on the results of a previous RINA project was held. The project had some similarities with openETCS modelling task and process. The discussion will be continued. We plan to distribute  some of the results. Projectoffice will take care to have a follow-up of this activity.  
You can find slides to the meeting here: {https://github.com/openETCS/governance/blob/master/scrumMeetings/WP3-Modeling/Presentations/FBK-ES-OpenETCS.pdf}.

\item Status openETCS API Review\\
The API Alstom is located for review in the Requirements repository: \url{https://github.com/openETCS/requirements/tree/master/D2.7-Technical_Appendix}. First comments have been received in the meantime. A meeting on the API is foreseen to take place end of March (organised by Baseliyos).

In order to avoid confusion, we agreed to remove the copy of the API from the modeling repository.

\item First Iteration plan\\
You can find a first milestone plan for the first iteration here:
\url{https://github.com/openETCS/modeling/issues/milestones}. 

\item Update on Activities\\
On Wednesday, the grooming for our first iteration took place. Results are documented in the issue tracker: \url{https://github.com/openETCS/SRS-Analysis/issues/9}

\item Upcoming Events\\
From March 11th til March 13th the modeling getting started event is planned to take place in Munich. If you intend to participate but did not yet manage to announce your participation, please, do not hesitate to send an e-mail to project office. The workshop is on site. We do not plan for goto-meetings.

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/WP3-Modeling/Minute%2020140228%20WP3.pdf}. Please, use the issue tracker for findings in the minutes.
\end{itemize}


\end{document}
