
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP3 Meeting Minutes\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP3 Weekly Scrum: Modelling\\
Date \& time & 2013-11-15, 09:00h--10:00h\\
Location & Telco and Goto-Meeting\\
Called up by & Pierre Francois Jauquet\\
Participants &
Stephane Besure,
Nicolas Boverie,
Christian Giraud,
%Guillaume Durand,
%Yoann Guyot,
%Baseliyos Jacob,
%Klaus-R\"udiger Hase,
Bernd Hekele,
Pierre Francois Jauquet,
Vincent Nuhaan,
Marielle Petit-Doche,
Uwe Steinke,
Jan Welte,
Jan Welvaarts
%Niklas Schaffrath
\\

Minutes by & Bernd Hekele\\
%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
%\item Team 1 Progress
%\item Team 2 Progress
%\item Team 3 Progress
%\item Team 4 Progress
\item Data Dictionary Team Progress
\item Organisational Issues 
\end{itemize}

\section{Discussion}
\begin{itemize}
\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/WP3-Modeling/Minute%2020131115%20WP3.pdf}. Please, use the issue tracker for findings in the minutes.
 
\item The Data Dictionary Team\\
The team Activities were in the focus of the meeting. Since the activities have been started, a number of different formats have been introduced. 

Decision: We switch all activities to work based on the latest xls template: \url{https://github.com/openETCS/SRS-Analysis/blob/master/Templates/Spread-sheet-%20template.xlsx} 

Marielle (Systerel) will take care on already filled forms and convert them to the latest form.

Location for work on the analysis is this directory: \url{https://github.com/openETCS/SRS-Analysis/tree/master/System%20Analysis/WorkingRepository}

The need for a system architecture group was agreed on. A proposal was discussed to define a new team with participants (e.g., the team leader) from each team and the data dictionary team.

You will find information about the datadictionary in this location: \url{https://github.com/openETCS/dataDictionary}

\item Workshop Organisation\\
Berlin is the location for the next workshop (November 26th - November 28th).\\
The datadictionary team will make use of the option to already start in the Monday afternoon. Meeting details are visible in the project calendar.

\item Effort Estimation\\
Pierre-Francois effort estimation for the task is still in internal review at Alstom. The result is planned to be made available to Siemens at beginning of next week. A feedback on the estimation can be discussed in next weeks meeting.

\end{itemize}

\section{Notes}

\end{document}
