
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP3 Meeting Minutes\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP3 Weekly Scrum: Modelling\\
%9:30-10:00 and 
Date \& time & 2014-04-11, 9:30-10:00 and 10:45h--11:00h\\
Location & Telco and Goto-Meeting\\
Called up by & Bernd Hekele\\
Participants &
%Mathilde Arnaud,
Benjamin Beichler,
%Marc Behrens,
Cecile Braunstein,
%Alessandro Cimatti (only 9:30 slot),
Fausto Cochetti,
%Lukasz Fronc,
Baseliyos Jacob,
Klaus-R\"udiger Hase,
Bernd Hekele,
%Jonas Helming,
%Hardi Hungar,
%Michael Jastram,
Peter Mahlmann,
Alexander Nitsch,
%Huu-Nghia Nguyen,
%Vincent Nuhaan,
Matthieu Perin,
Marielle Petit-Doche,
%Alexander Stante,
Stefan Rieger,
Christian Stahl,
Uwe Steinke,
%Izaskun de la Torre,
Giovanni Trotta,
Jan Welte,
%Jan Welvaarts
%Giovanni Zanelli,
Silvano dal Zilio
\\

Minutes by & Bernd Hekele\\
%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item each partner: impediments, progress
\item API Review
\item a.o.b.

\end{itemize}

\section{Discussion}
\begin{itemize}
\item each partner: impediments, progress\\
Status is updated in SRS-Analysis and in the modelling repository. Progress is visible in the dataDictionary and most  of the models of sub-functions (SysML). Start of work in Scade about to start. New project for dataDictionary opened in Scade.  Automatic transfer of interface from SysML to SCADE blocked.

\item API Review\\
The API review meeting took place in Munich. Minutes to the meeting are available here: \url{https://github.com/openETCS/requirements/tree/master/D2.7-Technical_Appendix/2014-04-12-Munich-Meeting}

\item a.o.b.\\
The Scade System version needed for transfering data between Scade System and Scade Suite has a delay. A meeting with Esterel is scheduled for 11.4.2014.

\end{itemize}

\section{Notes}
\begin{itemize}

\item Note: Location of Meeting Minutes\\
You can find these minutes here: \url{https://github.com/openETCS/governance/blob/master/scrumMeetings/WP3-Modeling/Minute_20140411_WP3.pdf}. Please, use the issue tracker for findings in the minutes.

\end{itemize}


\end{document}
