
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}

\begin{document}
{\begin{center}\huge\bf openETCS PMB Meeting Minutes\end{center}}
%{\begin{center}\huge\bf Project Management Board (PMB)\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & PMB Weekly Scrum: Project Management Board\\
Date \& time & 2014-02-28, 11:30h--12:00h\\
Location & Telco and Goto-Meeting\\
%Called up by & Bernd Hekele\\
Called up by & Klaus-R\"udiger Hase\\
Participants &
Mathilde Arnaud,
%Sylvain Baro,
%Marc Behrens,
%Benjamin Beichler,
%Cyril Cornu,
%Klaus-R\"udiger Hase,
Bernd Hekele,
%Baseliyos Jacob,
%Gilles Dalmas,
%Pierre Francois Jauquet,
%Ainhoa Gracia,
%Frank Golatowski,
%Jonas Helming,
Michael Jastram,
%Pierre-Francois Jauquet,
%Roberto Kretschmer,
%Bego\~na Laibarra,
Peter Mahlmann,
Huu-Nghia Nguyen,
Alexander Nitsch,
Matthieu Perin,
%Marielle Petit-Doche,
%Stan Pinte,
Stefan Rieger,
%Alexander Stante,
Uwe Steinke,
%Izaskun de la Torre,
Jan Welte,
%Jan Welvaarts
Giovanni Zanelli
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
%You can find a regular update on this location: \url{https://github.com/openETCS/governance/wiki/Project-Management}

\begin{itemize}

\item Update on Alstom Participation in openETCS
\item openETCS @ Innotrans
\item ITEA 3 call in N\"urnberg
\item openETCS Itea 2 Change Request
\end{itemize}

\section{Discussion}
\begin{itemize}

\item Update on Alstom Participation in openETCS\\
In a meeting of Alstom at DB-Netz Alstom confirmed to rejoin the openETCS community and plans to fulfils its obligations incl. WP3 leadership. Target: complete the transfer before the Itea openETCS project rehearsal in June.

\item openETCS @ Innotrans\\
oenETCS will be present at the DB stand at the Innotrans. openETCS  is planned to be on the official themes list of the fair. Other options like a conference room workshop, speakers corner, having the mid-term workshop  and flyers are to be discussed.\\

\item ITEA 3 call in N\"urnberg\\
Klaus-R\"udiger gave a talk at the ITEA3 kick-off meeting in N\"urnberg about the openETCS follow-up project.

\item openETCS Itea 2 Change Request\\
Projectoffice will start with the preparation of the Itea change request. Target is to have the CR completed by Mid of June to be ready at the project rehearsal. 

\end{itemize}

\section{Notes}

\end{document}
