
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}

\begin{document}
{\begin{center}\huge\bf openETCS PMB Meeting Minutes\end{center}}
%{\begin{center}\huge\bf Project Management Board (PMB)\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & PMB Weekly Scrum: Project Management Board\\
Date \& time & 2013-08-23, 11:30h--12:00h\\
Location & Telco and Goto-Meeting\\
Called up by & Klaus-R\"udiger Hase\\
Participants &
%Sylvain Baro,
Marc Behrens,
%Benjamin Beichler,
%Cyril Cornu,
Klaus-R\"udiger Hase,
Bernd Hekele,
Baseliyos Jacob,
%Gilles Dalmas,
%Pierre Francois Jauquet,
%Ainhoa Gracia,
Frank Golatowski,
%Jonas Helming,
%Michael Jastram,
%Bego\~na Laibarra,
%Peter Mahlmann,
%Alexander Nitsch,
Marielle Petit-Doche,
%Merlin Pokam,
%Christophe Ponsard,
Stefan Rieger,
Uwe Steinke,
%Izaskun de la Torre,
%J\"urgen Weiss,
Jan Welte
%Giovanni Zanelli
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item Report on Eclipse/Polarsys Meetings on Wednesday \& Thursday this week
\item SSRS contributions are low (review team not active)
\item Info from ESTEREL concerning usage and cost of SCADE (cost, licensing, etcs.)
\item Use of Models for verification and validation (impediment)
\item Modeling/Tooling strategy meeting need to be prepared and called for in October 
\item QA Plan f2f Review  Meeting in the week of Sept. 23rd ( e.g. at 26.09.) in BilBao (SQS Facility) ?!
\item Next PCC meeting ==> doodle
\item Next Advisory board meeting ==> doodle
\end{itemize}

\section{Discussion}
\begin{itemize}
\item Report on Eclipse/Polarsys Meetings on Wednesday \& Thursday this week\\
The workshop confirmed our Eclipse/SysML Selection. We can leanr from TOPCASED \& Polarsys   AIRBUS tools strategy. The Long term strategy, recommendations from AIRBUS/POLARSYS:
\begin{itemize}
\item we need to include POLARSYS elements into evaluation
\item What about coordinating our WP7 activities with POLARSYS?
\end{itemize}

\item SSRS contributions are low (review team not active)\\
After 3 sprints we will estimate the most likely completion time for the SSRS 

\item Info from ESTEREL concerning usage and cost of SCADE (cost, licensing, etcs.)
\item Use of Models for verification and validation (impediment)
PMB confirmed to make use of the SCADE model and its C-Code for first verification steps also with the demonstrator provided by ERSA. ERSA needs to be "activated". \\
In addition, the start of WP5 (Kickoff Meeting) is required by project activities. 
\item Modeling/Tooling strategy meeting need to be prepared and called for in October 
\begin{itemize}
\item Preparation Meetings
\item Defining a concept, based on knowledge today to get Modeling group start working asap.
\item Feed back via Questionnaire from all parties who will commit contributions to WP3 and/or WP7 (who will commit what resources on what activity, acceptance of SCADE, e.g.)
\item Decision need to be authorized by PCC meeting
\end{itemize}

\item QA Plan f2f Review  Meeting in the week of Sept. 23rd ( e.g. at 26.09.) in BilBao (SQS Facility) ?!\\
We plan for a review meeting of the QA guide at SQS in Bilbao. The likely date is September 26th. Details to be decided.

\end{itemize}

\section{Notes}

\end{document}
