
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
%width = 210 - 30 - 25 = 155
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}



% Page layout (geometry)
\title{Meeting Minute openETCS Project Management Board (PMB)}
\author{Hekele, Bernd}
\date{2013-03-22}

\begin{document}
\section*{\large{Meeting Minute openETCS Project Management Board (PMB) 2013-03-22}}

\emph{Called up by: \ Dr. Klaus Ruediger Hase.}\\
\emph{Minutes by: \ \  Bernd Hekele.}


\subsection*{Participants:} PMB, 
Klaus-Ruediger Hase, 
Marc Behrens, 
Stephane Callet,
Gilles Dalmas,
%Frank Golatowski, 
Bernd Hekele,
%Jonas Helming,
Baseliyos Jacob,
Michael Jastram, 
Rico Kaseroni, 
Peter Mahlmann, 
Stan Pinte,
Stefan Rieger, 
Jan Welte\\

%Cyril Cornu, 
%Jens Gerlach, 
%Marielle Petit-Doche, 
%Stan Pinte, 
%Merlin Pokam, 

%Baseliyos Jacob, Joao Santos, Uwe Steinke, Roberto, Kretschmer

\subsection*{Meeting Time: from 13:30h \ to: \ 14:30h}

\subsection*{Type of conference: Telco}

\line(1,0){440}
\section*{\underline{Agenda}}
\begin{enumerate}
\item PCC Meeting in April for Schedule Extension
\item Funding of Second Level Support (GIT)
\item Meeting Minutes Security Workshop
\item Workshop FORMAL METHODS 15.4.-17.4 and 22.-23.04.
\item ITEA2 Website Budget + Effort Numbers (WP level) + Excel Sheets (Task
level)


\end{enumerate}
\line(1,0){440}
\section*{\underline{Discussion}}

\begin{enumerate}
\item PCC Meeting in April for Schedule Extension\\
Meeting is scheduled, Meeting agenda distributed for review.

\item Meeting Minutes Security Workshop\\
Minutes are still in work. First version for review available on repository v-v-report and in teamshare. Please, send comments following the contribution rules. The minutes also document priorities to be followed in the project.

\item Funding of Second Level Support (GIT)\\
Topic is still open. Decision delegated to PCC. Will be on agenda of the May meeting.
\end{enumerate}

\line(1,0){440}
\section*{\underline{Notes}}

\end{document}
