
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
%width = 210 - 30 - 25 = 155
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}



% Page layout (geometry)
\title{Meeting Minute openETCS Project Management Board (PMB)}
\author{Hekele, Bernd}
\date{2013-03-20}

\begin{document}
\section*{\large{Meeting Minute openETCS Project Management Board (PMB) 2013-03-15}}

\emph{Called up by: \ Dr. Klaus Ruediger Hase.}\\
\emph{Minutes by: \ \  Bernd Hekele.}


\subsection*{Participants:} PMB, 
Klaus-Ruediger Hase, 
Marc Behrens, 
Gilles Dalmas,
%Frank Golatowski, 
Bernd Hekele,
Jonas Helming,
Michael Jastram, 
Rico Kaseroni, 
%Peter Mahlmann, 
Stefan Rieger, 
Jan Welte\\

%Cyril Cornu, 
%Jens Gerlach, 
%Marielle Petit-Doche, 
%Stan Pinte, 
%Merlin Pokam, 

%Baseliyos Jacob, Joao Santos, Uwe Steinke, Roberto, Kretschmer

\subsection*{Meeting Time: from 13:30h \ to: \ 14:30h}

\subsection*{Type of conference: Telco}

\line(1,0){440}
\section*{\underline{Agenda}}
\begin{enumerate}
\item Feedback from API / Safety Strategy Workshop in Paris (11.-13.3.)
\item PCC Meeting in April for Schedule Extension\\
As discussed during the Paris WorkShop according to schedule needs
\item Workshop FORMAL METHODS 15.4.-17.4 and 22.-23.04.
\item Greenhopper:  First Feedback from Piloting
\item Open Proposals
\item ITEA2 Website Budget + Effort Numbers (WP level) + Excel Sheets (Task
level)

\item Development Service Support Cost\

\end{enumerate}
\line(1,0){440}
\section*{\underline{Discussion}}

\begin{enumerate}
\item Feedback API / Safety Strategy Workshop in Paris (11.-13.3.)\\
Workshop in Paris is seen as a major positive step forward. Meeting minutes are in work (Marc). Complete set of results will be made available on Github as well as Teamshare:\newline
SharePoint ==> openETCS/Shared Dokument/!Meetings/20130311\_SafetyStrategy\_Workshop\_Paris\\
and on Git:\\
%\url{http://openetcs.org}
Major finding: new model for differentiating between different levels of being formal.\\
Discussion on this topic is ongoing.
\item PCC Meeting in April for Schedule Extension\\
Current effort estimation indicates a change of the project (end-date) or content might be needed. To get an agreement on further steps a Project Co-Ordination Meeting is required. The meeting is scheduled for April, 15th, 18:15 - 19:00 (aligned with the formal methods WS)

\item Workshop FORMAL METHODS 15.4.-17.4 and 22.-23.04.
\item Greenhopper:  First Feedback from Piloting
\item Open Proposals
\begin{itemize}
\item ERTMS FORMAL Spec  => Repository\\
We need a place to support tools and methods available for the openETCS project. Proposal after discussion: collect resources under WP1.\\
\end{itemize}
\item ITEA2 Website Budget + Effort Numbers (WP level) + Excel Sheets (Task
level)\\
In order to further proceed with planning Baseliyos is collecting effort information on task level. For furhter information, see:\\
SharePoint => openETCS/Shared Document/WP1 ...7\\
and make sure that your numbers are correct

\item Development Service Support Cost\
The budget for support costs (about 2 man days per Month) is exceeded. If we want to make use of second level support in the area of Git, Second Level Support needs to be ordered. DB has taken these costs for the first half year. Proposal: distribute the costs to major parties involved. Discussion will be continued on next PMB.

\end{enumerate}

\line(1,0){440}
\section*{\underline{Notes}}

\end{document}
