
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}

\begin{document}
{\begin{center}\huge\bf openETCS PMB Meeting Minutes\end{center}}
%{\begin{center}\huge\bf Project Management Board (PMB)\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & PMB Weekly Scrum: Project Management Board\\
Date \& time & 2013-12-13, 11:30h--12:00h\\
Location & Telco and Goto-Meeting\\
%Called up by & Bernd Hekele\\
Called up by & Klaus-R\"udiger Hase\\
Participants &
%Sylvain Baro,
%Marc Behrens,
%Benjamin Beichler,
%Cyril Cornu,
Klaus-R\"udiger Hase,
Bernd Hekele,
Baseliyos Jacob,
%Gilles Dalmas,
%Pierre Francois Jauquet,
%Ainhoa Gracia,
%Frank Golatowski,
%Jonas Helming,
Michael Jastram,
%Pierre-Francois Jauquet,
%Roberto Kretschmer,
%Bego\~na Laibarra,
Peter Mahlmann,
Alexander Nitsch,
Marielle Petit-Doche,
Stan Pinte,
%Merlin Pokam,
%Christophe Ponsard,
Stefan Rieger,
Uwe Steinke,
%Izaskun de la Torre,
Jan Welte,
%Jan Welvaarts
Giovanni Zanelli
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
You can find a regular update on this location: \url{https://github.com/openETCS/governance/wiki/Project-Management}

\begin{itemize}

\item Proposal on openETCS Toolchain Logo
\item Upcoming Events: January Workshop
\item Charta
\end{itemize}

\section{Discussion}
\begin{itemize}

\item Proposal on openETCS Toolchain Logo\\
The proposal on using an own logo (\url{http://openetcs.org/tool/} has been discussed.
An agreement on the new design could not be achieved. The decision has been deferred until January Munich workshop.

\item Upcoming Events: January Workshop\\
The PCC Agenda has been updated with the topic: "Dealing with defaulting parties according to Sect. 10.4, PCA V1".\\

The workshop has been extended with a Polarsys Information session. 

Please, use the doodle to indicate your participation. \url{http://doodle.com/figwdhn5bq99d8yn}

\item Charta

\item Upcoming Events: January Workshop\\
All workpackages are encouraged to organise the meeting agenda for the January Munich meeting before Xmas holidays.

\item Charta\\
The draft for the charta is on Gihub for review.
\url{https://github.com/openETCS/Charta}

\end{itemize}

\section{Notes}

\end{document}
