
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS PMB Meeting Minutes\end{center}}
%{\begin{center}\huge\bf Project Management Board (PMB)\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & PMB Weekly Scrum: Project Management Board\\
Date \& time & 2013-04-26, 13:30h--14:30h\\
Location & Telco and Goto-Meeting\\
Called up by & Klaus-R\"udiger Hase\\
Participants & PMB,
%Benjamin Beichler,
Marc Behrens,
%Cecile Braunstein,
%Stephane Callet,
%Cyril Cornu, 
%Gilles Dalmas,
%Jens Gerlach, 
%Frank Golatowski, 
Klaus-R\"udiger Hase,
Bernd Hekele,
%Jonas Helming,
Baseliyos Jacob,
Michael Jastram, 
%Bego\~na Laibarra,
Peter Mahlmann, 
Jaime Paniagua,
%Marielle Petit-Doche, 
%Stan Pinte,
Stefan Rieger,
%Uwe Steinke,
%Jo\~ao Santos,
Jan Welte,
Giovanni Zanelli\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item Results SSRS Kick-Off meeting
\item Project Proposal
\end{itemize}

\section{Discussion}
\begin{itemize}
\item Results SSRS Kick-Off meeting\\
Results as outcome from the 24th of April the SSRS Kick-off in Paris:
SSRS experts group and SRSS Review Team\\

The minutes to the SRSS Kick-Off meeting are in preparation (Baseliyos). They will be provided on Github for review (29.04.13). 

As an outcome of the workshop the competences are planned to be concentrated in 2 teams:
\begin{itemize}
\item The SRSS Expert Team with the competences from railway suppliers and research 
\item The SRSS review team with the competence of railway operators.
\end {itemize}
Experts for the teams still have to be nominated. It is foreseen to have the expert team working on a single site, e.g., in Munich at DB. Kickoff for the Review Team Kickoff is scheduled for May 15th.

For planning of the expert team, the following doodle is activated:\\
\url{http://doodle.com/k4emwuvart6uukbv}


\item Project Proposal
Currently one proposal waiting for approval: SRSS. Review started. Decision is planned for May 3rd.

\end{itemize}

\line(1,0){440}
\section{\underline{Notes}}

\end{document}
