
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}

\begin{document}
{\begin{center}\huge\bf openETCS PMB Meeting Minutes\end{center}}
%{\begin{center}\huge\bf Project Management Board (PMB)\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & PMB Weekly Scrum: Project Management Board\\
Date \& time & 2014-04-11, 11:30h--12:00h\\
Location & Telco and Goto-Meeting\\
%Called up by & Bernd Hekele\\
Called up by & Klaus-R\"udiger Hase\\
Participants &
%Mathilde Arnaud,
%Sylvain Baro,
%Marc Behrens,
%Benjamin Beichler,
%Ana Cavalli,
Fausto Cocchetti
Klaus-R\"udiger Hase,
Bernd Hekele,
Baseliyos Jacob,
%Pierre Francois Jauquet,
%Ainhoa Gracia,
%Frank Golatowski,
%Jonas Helming,
Michael Jastram,
%Pierre-Francois Jauquet,
%Roberto Kretschmer,
%Bego\~na Laibarra,
Peter Mahlmann,
%Huu-Nghia Nguyen,
%Alexander Nitsch,
Matthieu Perin,
Marielle Petit-Doche,
%Stan Pinte,
Stefan Rieger,
%Alexander Stante,
Uwe Steinke,
%Izaskun de la Torre,
Jan Welte,
%Jan Welvaarts
Giovanni Zanelli
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
%You can find a regular update on this location: \url{https://github.com/openETCS/governance/wiki/Project-Management}

\begin{itemize}
\item Actions for the Change Request
\end{itemize}

\section{Discussion}
\begin{itemize}

\item Actions for the Change Request\\
The project proposal is now in the process to be filed. In addition actions from the partners are needed:
\begin{enumerate}
\item Each Partner has to check the remaining effort and - in case the distribution of efforts has changed - update the plan at Itea.
\item In each country the funding authority has to be informed of the planned change.
\item DB is in charge of the German cluster and takes care of this step.
\item Alstom is in charge of the French Cluster. Fausto takes the action to inform the Alstom France about this need. 
\end{enumerate}

\item Charta\\
Comments to the Charta are still pending. The openETCS Charta will be on the agenda of the next PCC.

\end{itemize}

\section{Notes}

\end{document}
