
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}

\begin{document}
{\begin{center}\huge\bf openETCS PMB Meeting Minutes\end{center}}
%{\begin{center}\huge\bf Project Management Board (PMB)\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & PMB Weekly Scrum: Project Management Board\\
Date \& time & 2013-11-15, 11:30h--12:00h\\
Location & Telco and Goto-Meeting\\
%Called up by & Bernd Hekele\\
Called up by & Klaus-R\"udiger Hase\\
Participants &
%Sylvain Baro,
%Marc Behrens,
%Benjamin Beichler,
%Cyril Cornu,
Klaus-R\"udiger Hase,
Bernd Hekele,
%Baseliyos Jacob,
%Gilles Dalmas,
%Pierre Francois Jauquet,
%Ainhoa Gracia,
%Frank Golatowski,
%Jonas Helming,
Michael Jastram,
%Roberto Kretschmer,
%Bego\~na Laibarra,
Peter Mahlmann,
%Alexander Nitsch,
Marielle Petit-Doche,
Merlin Pokam,
%Christophe Ponsard,
%Stefan Rieger,
Uwe Steinke,
%Izaskun de la Torre,
%J\"urgen Weiss,
Jan Welte,
Jan Welvaarts
%Giovanni Zanelli
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
You can find a regular update on this location: \url{https://github.com/openETCS/governance/wiki/Project-Management}

\begin{itemize}
\item Upcoming Events: January Workshop
\item Project Proposal Data Dictionary
\end{itemize}

\section{Discussion}
\begin{itemize}

\item Now Fixed: SCADE training\\
We have fixed the time and the location for the Esterel's Scade Training: Munich and 7.1. - 9./10.1.2014. 

Duration is depending on the number of participants.
Persons visible on the oroginal doodle have already been invited. The doodle will be continued to be used.

\url{http://doodle.com/dgx7emaatfd6zaqg}

We will collect your wishes and send you an individual invitation for your participation if there is still seats  available. The doodle will be closed end of November.

\item Upcoming Events: January Workshop\\
The plan is on the governance wiki for your update. The workpackages are asked to take care for updating their parts. Please update the wiki accordingly.

See this link: \url{https://github.com/openETCS/governance/wiki/%23-Jan2014-Munich-openETCS-Meetings}

\item openETCS project metrics going public\\
We agreed to move the openETCS metrics: \url{https://github.com/openETCS/management/wiki/State-of-Deliverables} 
from management to governance in order to make them public.

\item Charta Activities\\
We also agreed to make the repository charta public:
\url{https://github.com/openETCS/Charta}

\end{itemize}

\section{Notes}

\end{document}
