
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}

\begin{document}
{\begin{center}\huge\bf openETCS PMB Meeting Minutes\end{center}}
%{\begin{center}\huge\bf Project Management Board (PMB)\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & PMB Weekly Scrum: Project Management Board\\
Date \& time & 2013-09-13, 11:30h--12:00h\\
Location & Telco and Goto-Meeting\\
Called up by & Klaus-R\"udiger Hase\\
Participants &
%Sylvain Baro,
Marc Behrens,
%Benjamin Beichler,
%Cyril Cornu,
%Klaus-R\"udiger Hase,
Bernd Hekele,
%Baseliyos Jacob,
%Gilles Dalmas,
%Pierre Francois Jauquet,
%Ainhoa Gracia,
%Frank Golatowski,
%Jonas Helming,
Michael Jastram,
%Bego\~na Laibarra,
%Peter Mahlmann,
%Alexander Nitsch,
Marielle Petit-Doche,
%Merlin Pokam,
%Christophe Ponsard,
Stefan Rieger,
Uwe Steinke,
%Izaskun de la Torre,
%J\"urgen Weiss,
Jan Welte
%Giovanni Zanelli
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
You can find a regular update on this location: \url{https://github.com/openETCS/governance/wiki/Project-Management}

\begin{itemize}
\item D7.1 Document Status
\item Upcoming Events: Braunschweig Workshop
\end{itemize}

\section{Discussion}
\begin{itemize}
\item D7.1 Document Status
D7.1 Document describes the technical background of the openETCS Primary Toolchain and decisions related to the toolchain.
Current status is:
\begin{itemize}
\item The document is close to be closed. Some minor technical issues are under clarification. Closing of the document review is planned by September, 18th. 
\item There is a management issue open related to the proposed decision in the document, not a technical issue. The issue is planned to be addressed at the upcoming PCC.
\item The D7.1 describes a strategy for an openETCS open toolchain to be developed in parallel to the clarification of the ETCS SRS model.
\item for the modelevaluation SCADE is foreseen to be used as  a robust but closed modelling tool.
\item the transformation of the SCADE model into an open model is part of D7.1 strategy.
\end{itemize}

\item Upcoming Events: Braunschweig Workshop
See this link: \url{https://github.com/openETCS/governance/wiki/Project-Management}

\end{itemize}

\section{Notes}

\end{document}
