
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}


\begin{document}
{\begin{center}\huge\bf openETCS WP3 Meeting Minutes\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP3 Weekly Scrum: Modelling\\
Date \& time & 2013-12-09, 14:00h--15:30h\\
Location & Telco and Goto-Meeting\\
Called up by & Bernd Hekele\\
Participants &
%Stephane Besure,
Benjamin Beichler,
%Nicolas Boverie,
%Christian Giraud,
%Guillaume Durand,
Frank Golatowski,
%Yoann Guyot,
Baseliyos Jacob,
Klaus-R\"udiger Hase,
Bernd Hekele,
Michael Jastram,
Pierre Francois Jauquet,
Alexander Nitsch,
Vincent Nuhaan,
Marielle Petit-Doche,
Stan Pinte,
Stefan Rieger,
Alexander Stante,
Uwe Steinke,
Jan Welte,
Jan Welvaarts
%Niklas Schaffrath
\\

Minutes by & Bernd Hekele\\
%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item Current WP3-Situation
\item Temporary Setup
\item Call for closing resource gap
\end{itemize}

\section{Discussion}
\begin{itemize}
 
\item Current WP3-Situation\\
Pierre-Francois Alstom announced the intention to withdraw its resources with immediate effect and to leave the openETCS project. The decision is a decision by Alstom management. Reasoning will be communicated with DB-management.

The decision covers all Alstom country organisations.

\item Temporary Setup\\
The participants of the meeting agreed on a temporary set-up. The SRS-Analysis work shall continue as agreed on in the Berlin workshop. With the gap in staff in the team lead by Alstom those activities will be continued with low priority. 

In order to fill the gap in WP3 leadership temporary DB (Baseliyos and Bernd) will jointly coordinate WP3 activities. The situation will be discussed in the upcoming openETCS workshop.

The weekly meetings (Friday, 9:00 - 10:00) will be continued in order to give a platform for team planning. 

The proposal to combine the Munich openETCS workshop (14.1. - 16.1.) with the planned Brussel SRS-analysis team workshop (20.1.-22.1.) was rejected because of being too short term.

Details of the SRS-Analysis workshop will be discussed in the Friday telco.

\item Call for closing resource gap\\
The gap in resourcing both, in terms of quantity and competences is too big to continue without replacement. openETCS project will search for ERTMS experts outside the community. Baseliyos will provide a profile for distribution to interested partners.

Please, discuss options with project office.

\end{itemize}

\end{document}
