
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
%width = 210 - 30 - 25 = 155
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}



% Page layout (geometry)
\title{Meeting Minute openETCS Project Management Board (PMB)}
\author{Hekele, Bernd}
\date{2013-03-11}

\begin{document}
\section*{\large{Meeting Minute openETCS Project Management Board (PMB) 2013-03-08}}

\emph{Called up by: \ Dr. Klaus Ruediger Hase.}\\
\emph{Minutes by: \ \  Bernd Hekele.}


\subsection*{Participants:} PMB, 
Klaus-Ruediger Hase, 
Marc Behrens, 
Frank Golatowski, 
Bernd Hekele,
Michael Jastram, 
Rico Kaseroni, 
Peter Mahlmann, 
Stefan Rieger, 
Jan Welte\\

%Cyril Cornu, 
%Jens Gerlach, 
%Marielle Petit-Doche, 
%Stan Pinte, 
%Merlin Pokam, 

%Baseliyos Jacob, Joao Santos, Uwe Steinke, Roberto, Kretschmer

\subsection*{Meeting Time: from 13:30h \ to: \ 14:30h}

\subsection*{Type of conference: Telco}

\line(1,0){440}
\section*{\underline{Agenda}}
\begin{enumerate}
\item Summary and Conclusion proceedings QA plan
\item Project Proposals for Decision
\item getting Scrum into Locations
\item Scrum tooling: Jira and Greenhopper
\end{enumerate}
\line(1,0){440}
\section*{\underline{Discussion}}

\begin{enumerate}

\item Summary and Conclusion proceedings QA plan
A draft version of the QA plan is now available in Git. The document is stil overloaded with some topics - on the other hand, some topics are stil missing. In order to get a major improvement in the quality of the document a meeting took place this morning. The result of the meeting can be seen here: \\
https://github.com/openETCS/ecosystem/tree/master/QAplan/Meeting%20Minutes\\

\item Project Proposals for Decision\\
Project government is accepted. The aspect of m,oving the PCA under this location  ineeds to be clarified with legals.\\
For project "WP3a: ERTMSFormalSpecs Project proposal" the legal aspect is not clear in the meeting. Especially the aspect of showing a product under openETCS which is funded outside the ITEA2 needs clarification. AI to Bernd Hekele to check the options and align openETCS procedure accordingly.

\item getting Scrum into Locations\\
will be taken into next weeks meeting.
\item Scrum tooling: Jira and Greenhopper\\
We got a free and unlimited license from Atlassian to use Jira and Greenhopper in openETCS. The tool will be prototyped for WP1, WP4 and WP7. After the prototyping phase rollout into the openETCS community is planned.

\end{enumerate}

\line(1,0){440}
\section*{\underline{Notes}}

\end{document}
