
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}

\begin{document}
{\begin{center}\huge\bf openETCS PMB Meeting Minutes\end{center}}
%{\begin{center}\huge\bf Project Management Board (PMB)\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & PMB Weekly Scrum: Project Management Board\\
Date \& time & 2013-12-06, 11:30h--12:00h\\
Location & Telco and Goto-Meeting\\
%Called up by & Bernd Hekele\\
Called up by & Klaus-R\"udiger Hase\\
Participants &
%Sylvain Baro,
%Marc Behrens,
%Benjamin Beichler,
Cyril Cornu,
Klaus-R\"udiger Hase,
Bernd Hekele,
Baseliyos Jacob,
%Gilles Dalmas,
%Pierre Francois Jauquet,
%Ainhoa Gracia,
%Frank Golatowski,
%Jonas Helming,
Michael Jastram,
Pierre-Francois Jauquet,
%Roberto Kretschmer,
%Bego\~na Laibarra,
Peter Mahlmann,
Alexander Nitsch,
Marielle Petit-Doche,
Merlin Pokam,
%Christophe Ponsard,
Stefan Rieger,
Uwe Steinke,
%Izaskun de la Torre,
%J\"urgen Weiss,
Jan Welte,
Jan Welvaarts
%Giovanni Zanelli
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
You can find a regular update on this location: \url{https://github.com/openETCS/governance/wiki/Project-Management}

\begin{itemize}

\item Alstom Proposal
\item Upcoming Events: January Workshop
\item Charta
\end{itemize}

\section{Discussion}
\begin{itemize}

\item Alstom Proposal\\
Pierre Francois Jauquet communicated Alstom's announcement of the intention to step out of the openETCS project. The decision is by Alstom Management. Alstom Management will inform DB maangement about reasoning for this step.

The PMB agreed to call for a meeting with WP3 interested partners on Monday to discuss on the impact and the next steps to handle this situation.

Note when writing: Meeting took place on Monday, 14:00. Results of the meeting will be documented in this location.

Pierre Francois confirmed the request to make the SRS-Analysis repository public including the Alstom contributions. 

The PMB expressed to feel sorry about this step, especially with the background of the successful and enthusiastic cooperation at the Berlin workshop.

\item Upcoming Events: January Workshop\\
All workpackages are encouraged to organise the meeting agenda for the January Munich meeting before Xmas holidays.

\item Charta\\
The draft for the charta is on Gihub for review.
\url{https://github.com/openETCS/Charta}

\end{itemize}

\section{Notes}

\end{document}
