
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}

\begin{document}
{\begin{center}\huge\bf openETCS PMB Meeting Minutes\end{center}}
%{\begin{center}\huge\bf Project Management Board (PMB)\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & PMB Weekly Scrum: Project Management Board + Itea Preparation\\
Date \& time & 2014-05-16, 11:15h--12:00h\\
Location & Telco and Goto-Meeting\\
%Called up by & Bernd Hekele\\
Called up by & Klaus-R\"udiger Hase\\
Participants &
%Mathilde Arnaud,
%Sylvain Baro,
Marc Behrens,
%Benjamin Beichler,
%Ana Cavalli,
Fausto Cocchetti
Laurent Ferrier,
Klaus-R\"udiger Hase,
Bernd Hekele,
%Baseliyos Jacob,
%Pierre Francois Jauquet,
%Ainhoa Gracia,
%Frank Golatowski,
%Jonas Helming,
Michael Jastram,
%Pierre-Francois Jauquet,
%Roberto Kretschmer,
%Bego\~na Laibarra,
Peter Mahlmann,
%Huu-Nghia Nguyen,
%Alexander Nitsch,
Matthieu Perin,
Marielle Petit-Doche,
%Stan Pinte,
Stefan Rieger,
%Alexander Stante,
Uwe Steinke
%Izaskun de la Torre,
%Jan Welte,
%Jan Welvaarts
Giovanni Zanelli
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}

\begin{itemize}
\item Approbation of documents
\item Next PCC meeting scheduled aligned with Itea Review
\item Generic API
\item Preparation of the ITEA 2 Review meeting
\end{itemize}

\section{Discussion}
\begin{itemize}
\item Approbation of documents\\
According to Cenelec documents are to be signed by author and other responsible persons. In order to support this requirement the layout for documents has been extended with structures for the signatures. The new has been distributed by projectoffice to persons concerned. So far, negative feedback has been received by WP2 with the information the workpackage is closed.\\
Projectoffice will bring the lacking responsiveness to the next PCC in order to discuss possible solutions.

\item Next PCC meeting scheduled aligned with Itea Review\\
The next PCC has been scheduled for June, 11th. Agenda is under preparation.

\item Generic API\\
On the API Review meeting the proposal of a generic openETCS API has been supported. The confirmation by the WP3 leader is pending. WP3 is now starting with the analysis of the topic. 

\item Preparation of the ITEA 2 Review meeting.\\
Agenda and actions are updated in the following wiki:
\url{https://github.com/openETCS/management/wiki/Timeline-ITEA-Review-2014}

\end{itemize}

\section{Notes}

\end{document}
