
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}

\begin{document}
{\begin{center}\huge\bf openETCS PMB Meeting Minutes\end{center}}
%{\begin{center}\huge\bf Project Management Board (PMB)\end{center}}
\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & PMB Weekly Scrum: Project Management Board\\
Date \& time & 2013-08-02, 11:30h--13:30h\\
Location & Telco and Goto-Meeting\\
Called up by & Klaus-R\"udiger Hase\\
Participants &
%Sylvain Baro,
Marc Behrens,
Benjamin Beichler,
%Cyril Cornu,
%Klaus-R\"udiger Hase,
Bernd Hekele,
Baseliyos Jacob,
%Gilles Dalmas,
%Pierre Francois Jauquet,
%Ainhoa Gracia,
%Frank Golatowski,
Jonas Helming,
Michael Jastram,
%Bego\~na Laibarra,
Peter Mahlmann,
Alexander Nitsch,
%Marielle Petit-Doche,
%Merlin Pokam,
Christophe Ponsard,
Stefan Rieger,
Uwe Steinke,
%Izaskun de la Torre,
%J\"urgen Weiss,
Jan Welte
%Giovanni Zanelli
\\

Minutes by & Bernd Hekele\\

%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}

%\line(1,0){440}

\section{{Agenda}}
\begin{itemize}
\item Itea Review Debriefing Meeting
\item Information from Meetings with ERTMS User's Group
\item Information from Meetings with Esterel
\item Meeting with Itea2 Chairman Rudolf Haggenm\"uller
\item Preparing for Start of WP3 tasks
\item openETCS QA manager and Review of QA-Plan
\end{itemize}

\section{Discussion}
The PMB meeting was started with the Itea Debriefing. After a break the meeting continued as a PMB with smaller attendance.

\begin{itemize}
\item Itea Review Debriefing Meeting\\
In order to have a clear traceability Issues related with the review are linked to the milestone Itea 2nd review in the management repository.
Results of the debriefing are documented in the issues related to this milestone.
\url{https://github.com/openETCS/management/issues?labels=ITEA2&milestone=&page=1&state=open}\\

\item Information from Meetings with ERTMS User's Group\\
Klaus-R\"udiger reported from a meeting held with ERTMS user's Group:
\begin{itemize}

\item This group has a high expectation in our project. 
\item Focus needs to be on the analysis of the system in SRS subset 26. Not only the OBU is in focus, but also the interworking with other parts of the system including trackside.
\item A high quality reference implementation is the expected basis for tests in the lab. \item This implementation eases the way for legal and technical approval of installations on the wayside by the authorities. 
\item This statement goes in line with the conclusion found by the Itea review team.
\url{https://github.com/openETCS/management/issues/57}\\
We plan to meet in strategy workshops in order to discuss impacts on our plan and adjust our strategy according to the new requirements.

\end{itemize}

\item Information from Meetings with Esterel\\
Klaus R\"udiger met Esterel CEO Eric Bant\'egnie in Paris. On details, please refer to Klaus-R\"udigers mail dated 25.7.2013.\\
\item Meeting with Itea2 Chairman Rudolf Haggenm\"uller\\
We had the chance to get direct feedback in a meeting with Itea2 Chairman Rudolf Haggenm\"uller. He emphasized the Itea review boards conclusion and gave feedback on the new strategy focusing quicker on modelling, which was highlighted by Klaus-R\"udiger.

\item Preparing for Start of WP3 tasks\\
With the changed strategy we need to prepare the modelling work planned in WP3 tasks.
\begin{itemize}
\item We decided to open the necessary repositories now. 
\item To get the right traction we set the task leader as initial committer of the repository. 
\item Marc Behrens as a stakeholder agrees to act as domain mentor for all repositories. 
\item Klaus R\"udiger agrees to act as process mentor.
\end{itemize}
The decision was agreed by voting. Yes: 5 partners, NO: no partner.

\item openETCS QA manager and Review of QA-Plan\\
SQS is playing a major role in openETCS Quality Assurance. 
PMB agrees to appoint Izaskun de la Torre as a quality assurance manager for the openETCS project. With this appointment we want to honour her competences and the value added by SQS to the  openETCS community.\\
The review of the QA-Plan is coming more in focus now. We would like to opt for an on site  meeting for the review. Details need to be agreed on.

\end{itemize}

\section{Notes}

\end{document}
